### 2015-10-01 roadmap/doc.tex
roadmap

\documentclass[12pt]{article}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{float}
\usepackage{subfig}
\usepackage[a4paper]{geometry}
\geometry{hscale=0.85,vscale=0.85,centering}

\def\xcolorversion{2.00}
\def\xkeyvalversion{1.8}
\usepackage[version=0.96]{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,snakes,automata,backgrounds,petri}

\usepackage{algpseudocode} 
\usepackage{algorithm}

\hyphenation{op-tical net-works semi-conduc-tor}

\usepackage{titling}

% Make a clickable table of content
\usepackage{hyperref}
\hypersetup{
	colorlinks,
	citecolor=black,
	filecolor=black,
	linkcolor=black,
	urlcolor=black
}

% Put the bibliography in the table of contents
\usepackage[nottoc,notlof,notlot]{tocbibind}

% For multirow tables
\usepackage{multirow}

\setlength{\droptitle}{-4em}   % This is your set screw

\title{Robotic models of learning and development \\of speech and tool use.}

\author{S\'ebastien Forestier}

\begin{document}

\maketitle
\thispagestyle{empty}
%\vspace{1em}
%\textbf{Supervisor:} Pierre-Yves Oudeyer

\vspace{2em}
%\paragraph{Abstract}

	Documentation and roadmap of my Master's internship and the beginning of my PhD thesis.

%

\vspace{2em}

	\begin{figure}[H] 
		\centering 
		\includegraphics[height=10cm]{./include/torso.png}
	\end{figure}

%\paragraph{Declaration of contribution}

	%\begin{itemize}
		%\setlength\itemsep{0em}
		%\item Definition of scientific question: PYO, SF
		%\item Bibliographic research: PYO, SF
		%\item Choice of the general approach to answer the question: PYO, SF
		%\item Choice of methods: PYO, SF
		%\item Methods development, programming: SF
		%\item Data analysis: SF
		%\item Results interpretation: PYO, SF
		%\item Dissertation writing: SF
		%\item Dissertation review and comments: PYO
	%\end{itemize}

%

\newpage
\tableofcontents
\newpage

\section{Introduction}

	\paragraph{}
	During their first years of life, infants progressively learn to make complex arm gestures and finger movements to interact with the objects of the environment.
	At the same time, they also learn to produce physical effects on the world with another mean.
	They discover that some of their
	vocalizations can be used as tools to influence their social peers, as through the action of these social peers they are able to produce physical effects.
	To do so they learn how to use their vocal tract composed of many complex actuators from the larynx to the lips.
	An important scientific question is how these influences are discovered and by which mechanisms the corresponding abilities are developed.

	\paragraph{}%
	Recent work in computational modeling has shown how mechanisms of active curiosity-driven learning, combined with imitation learning, 
	could progressively self-organize
	developmental stages of increasing complexity in vocal skills.
	These developmental stages share many properties with
	the vocal development of infants in the first 6 months of life \cite{moulin-frier_self-organization_2014}.

	\paragraph{}
	Like in other computational models of vocal development \cite{guenther2006neural, howard2011modeling, warlaumont2013prespeech}, 
	the vocal agents in the model of Moulin-Frier et al. do
	not associate sounds to meaning, and do not link vocal production to other forms of action.	
	In other models of language acquisition, one assumes that vocal production is mastered, 
	and	hand code the meta-knowledge that sound should be associated to referents or actions \cite{mangin2012learning}.
	But understanding what kind of mechanisms can explain the smooth transition between the learning of vocal sound
	production and their use as tools to affect the world is still largely an open question.

	\paragraph{}
	In this work, we will extend models of curiosity-driven goal babbling and
	their interaction with social interaction presented in \cite{moulin-frier_self-organization_2014} so as to make
	steps towards addressing this question. 	
	In particular, we will integrate
	additional mechanisms to handle task and action
	spaces where the task spaces initially given to the robot can be encapsulated
	as primitive actions to affect newly learned task spaces.

	\paragraph{}	
	We will first develop simple extensions of the SAGG-RIAC architecture with different sensorimotor models that can be learned in a hierarchical manner.	
	A sensorimotor model is defined as first a task spaces (or sensori space) where tasks (or sensori states to be reached) can be set by a teacher, 
	or self-generated by the learner and also a motor space to be used to solve those tasks.	
	A sensorimotor model is learned well enough when the learner knows how to solve the tasks (or reach sensori goals) for which it has the means to.
	Then, in an action to solve a new task, a new model can reuse that previous model by giving it a sub-task that will be useful to solve the current one.
	We are here describing a hierarchy of models that the agent can learn and extend with new ones.

	\paragraph{}
	Given a simple hierarchy of 2 models, one reusing the other, a straightforward learning mechanism will be to explore the first model 
	and after some time, to explore the second one. 
	We will also study other mechanisms to handle this hierarchy of sensorimotor models that all need to be explored with an certain amount of trials that 
	the agent could estimate.

	\paragraph{}
	In order to evaluate the hierarchical learning mechanisms, we will describe a first task for which a simple hierarchy of 2 sensorimotor models
	with the second reusing the first can be used to learn the task.
	A simulated robot arm will have to explore its motor space in order to understand how to push an object to different locations. 
	The robot will first explore how to make movements with its hand and then use this skill to explore the task of pushing an object.		
	The simulated environment having a high variability due to collisions' unstability, that makes comparisons of architectures difficult.	
	We will thus also implement a more simple environment composed of a simple geometric arm moving in 2 dimensions.
	Then, more complex hierarchies will be tested in an environment with the simple arm where a sequence of 2 movements has combinatorial 
	consequences on the sensors.

	\paragraph{}
	Measuring exploration or learning is not generally equivalent. 
	Exploration is a measure of how well the agent has found diverse outcomes in its task space. 
	It makes no assumptions about the interest of exploring given regions of the task space from the viewpoint of the engineer, 
	neither if we want the robot to learn specific tasks or if we know that certain tasks will be more useful later for the robot.
	However, in unstable parts of the sensorimotor environment, the exploration measured makes no sense for the robot as it might not have the competence to 
	reach again that goal.
	For instance when a robot is trying to throw a ball to given position on a table, 
	even if the robot tries the same motor command, it might never reach again a reached position due to the variability in the generated arm movement, and 
	the collision between the arm and the ball.
	On the other hand, learning measures the competence of the robot on some tasks: how well the robot reaches a set of user-defined 
	goals of the task space. The agent is evaluated on some tasks even if it did not know that it 
	would be evaluated on those tasks. 
	As the agent self-generates goals in the task space, it might not yet have explored that evaluated part of the environment, or in another run, have explored
	it very early, so it is hard to interpret this competence as a general progress.
	We will thus define an intermediate measure that will evaluate how well competent is the robot on the explored part of the task space.

	\paragraph{}
	Then, in order to assess a possible development of language seen as a tool to produce physical effects on an environment, 
	we will develop a multi-modal environment composed of the DIVA vocal synthesizer \cite{guenther2006neural} and the previous 2D arm, in which combinations 
	of sounds and arm movements make combinatorial changes in the environment.

	\paragraph{}
	In the firsts learning algorithms developed, the hierarchy of models to learn is given to the agent as if it already knew the combinations of actions
	to explore in order to learn the successive tasks.
	This is a strong hypothesis as infants have first to discover what types of actions to combine to get a specific outcome.
	For instance, the discovery that pushing on the knees and on the arms with certain coordination for a 6-month-old baby allow to move with an interesting high speed, but it does not need to be taught by parents.
	We will then develop an algorithm to autonomously complexify the sensorimotor contingencies learned by reusing the previously learned actions, with no
	predefined hierarchy of sensorimotor models.
	In this work we did not have time to assess those learning architectures but that will be done in future experiments.

	%We will describe an algorithm that integrates the different interest model of higher models in the hierarchy to guide the exploration of the current model.

	\paragraph{}
	Finally, we will derive a way to integrate those hierarchical learning architectures with social interactive learning 
	from the SGIM-ACTS learning architecture \cite{nguyen2012}. 
	Different implementations will be developed, that could allow imitation of teachers and more generally social guidance in our models.
	The evaluations of those social learning algorithms remains to be done.

	\paragraph{}
	In the next section, related work will be presented on curiosity-driven learning, models of language acquisition, hierarchical representation of actions
	and social interaction.
	In Section 3, the methods of the experiments will be explained and we will present the details of the algorithms.
	In Section 4, the results of the conducted simulations will be presented, and a general discussion will be developed in Section 5.

	%
%

\section{Related work}

	\subsection{Curiosity-driven exploration and developmental trajectories}

		\paragraph{}
		Active curiosity-driven learning is a paradigm in which the robot or learning agent chooses itself what to explore or learn in its environment, 
		based on some sort of internal model of its progress in the task of exploring or learning \cite{cangelosi2010integration}. 
		With an intrinsic motivation to explore and learn in interesting situations, situations where the agent is progressing the most, the expected future progress is thus maximized.
		The agent does not necessarily know exactly what engineers are expecting from it, or on what task it should measure its own progress, 
		but general principles permit to define what is an interesting situation. 
		If the agent builds an internal model of its sensorimotor contingencies (e.g. What happen if I push that button ?), then it can monitor the accuracy of its sensorimotor model
		by experimenting with its environment, and compute the progress of its sensorimotor model, that will lead it to bias its experiments in those regions of the sensorimotor 
		model that have shown a high prediction progress.

		\paragraph{}
		These ideas of curiosity-driven learning have a grounding in infants psychological experimentation \cite{forestierworkshop} that show that infants are seeking, by play,
		situations of intermediate novelty: situations neither too novel, neither fully understood.
		For instance, in order to understand how infants learn about the statistical properties of their sensory environment, 
		Kidd and collaborators \cite{kidd} have tested 
		how 8-month-old infants' attention to their environment is modulated by its statistical complexity.			
		They presented 3 objects popping out of their respective boxes, in a sequence of varying complexity, 
		as measured by its information content or surprise: the negative log probability of an object popping out of a given box.
		The measure of infants' attention is related to the time after which they look away from the object, given by eye-tracking tools.						
		They show that infants have a Goldilocks preference: a preference for sequences neither too simple nor too complex.				
		The explanation of this effect is that this preference gives infants a useful rate of sensory information 
		and to avoid wasting cognitive resources on too complex stimuli.		
		This is defined also in the "Flow" theory \cite{flow} defining a state of pleasure obtained when engaged in activities challenging enough but not too much.

		\paragraph{}%
		In order to model information seeking mechanisms and curiosity-driven learning suggested by behavioral experiments in humans and animals,
		Pierre-Yves Oudeyer uses an embedded setup with developmental robots. Those robots are learning in an open-ended manner: they are not defined to solve any task but rather are designed 
		to be able to adapt to any unpredicted environment.		
		%
		The authors developed computational architectures to handle this curiosity driven learning: including the IAC \cite{oudeyer_intrinsic_2007} 
		and SAGG-RIAC \cite{baranes2010intrinsically} architectures.
		Here an intrinsic motivation to discover the sensorimotor environment is defined as a measure of prediction progress in the motor space (IAC) 
		or competence-progress in the sensory space (SAGG-RIAC).
		%
		The SAGG-RIAC architecture keeps a predictive model of the competence progress of the robot in different explored parts of the sensory space.
		To measure its own competence, the robot is self-generating goals to reach in the sensory space, and see how close to the goal it manages to go.
		The exploration is then biased towards parts of the space which give the highest competence progress, this mechanism ensuring a useful exploration in a space of high dimensionality where random exploration would not enable any learning. 			
		Implementations of these ideas include the Playground Experiment \cite{oudeyer_intrinsic_2007} and self-organization of vocalizations \cite{moulin-frier_self-organization_2014}.

		\paragraph{}%
		In the Playground Experiment, a quadruped robot is placed in an infant play mat, with a responding robot peer next to it. 
		The robot has to learn how to use its motor primitives to interact with its environment (IAC architecture). 
		They observe the self-organization of developmental	trajectories: in different runs with the same parameters, the robot explores objects and actions with 
		different orders.

		\paragraph{}%
		In the self-organization of vocalizations experiments, a simulated agent has to understand how to use a vocal synthesizer with the help of humans' phonetic items. The SAGG-RIAC architecture can generate phonetic goals to reach with the simulated vocal tract, in parts of the sensory space where competence progress is high, or try to imitate humans' phonetic items, choosing the strategy that again shows the best competence progress.
		They conclude that developmental trajectories of increasing complexity are emerging, with regularity and diversity.
		The diversity comes from different mechanisms: random generation in the algorithms, variability in the environment, and the multiples attractors
		of the learning dynamic system.

		\paragraph{}%
		These developmental trajectories are similar to what can be observed during child development, which is an evidence toward
		a general purpose curiosity-driven system in infants' learning \cite{oudeyer2014evolution}. 
		A behavioral and cognitive epigenesis could develop and complexify behavioral and 
		cognitive phenomena by the interaction with the environment. Hence communication skills could be the result of curiosity-driven exploration.
		Thus curiosity-driven learning, as an exaptation mechanism, could develop skills useless at the moment but which can turn to be recruited 
		later for more complex unforeseen competences.			
		This idea leads them to an evolutionary perspective saying that an intrinsic motivation for learning for itself, could have become at some evolutionary point a more efficient mechanism than one for developing specific genetically encoded skills to survive and reproduce \cite{oudeyer2014evolution}.

		\paragraph{}
		In our hierarchical implementations, even if the sensorimotor models will be part of a hierarchy of models, 
		each of them will be explored using the SAGG-RIAC algorithm. 
		Another computational layer will have to choose which model to explore based on their learning progress.

	%

	\subsection{Models of language acquisition}

		\paragraph{}
		In some models of language acquisition, the produced sounds are not related to actions the agent or the caregiver 
		could make on the objects of the environment.
		The DIVA model (Directions Into Velocities of Articulators, \cite{guenther2006neural}) 
		is a neural network that simulates the cortical interactions to produce
		syllables, that provides an account of different production phenomena, from speaking skill acquisition to coarticulations.	
		%
		The Elija model \cite{howard2011modeling} also uses an articulatory synthesizer to pronounce sounds. 
		It first gets a reward for exploration of its vocal outputs, and then 
		is interacting with a modeled caregiver that imitates its sounds like a mother would do: 
		either mimicking the infant's sounds or rather providing an intermediate 
		sound between the infant's one and the adult one. 
		The model learns the associations between its vocal commands and the response of the caregiver.
		The agent can thus learn the name of objects by trying to reproduce caregiver's utterances.		
		%
		In a self-organizing map neural network model of motor prespeech production \cite{warlaumont2013prespeech}, experiments
		show that a reinforcement based on the similarity of the model's output sounds 
		with a given set of vowels can bias the post-learning model's babbling sounds
		towards that reinforced set of vowels.

		\paragraph{}
		In other models of language acquisition, one assumes that vocal production is mastered, and
		hand code the meta-knowledge that sound should be associated to referents or actions.
		For instance, the model from Mangin et al. \cite{mangin2012learning} gets as input dance-like combinations of human movement primitives plus ambiguous 
		labels associated to these movements.
		Using Non-negative Matrix Factorization \cite{paatero1994positive}, the model learns to recognize the movement primitives common to them, 
		and when given new combinations, is able to produce a good set of 
		labels to describe the combination.

		\paragraph{}
		We rather suppose that the agent has to autonomously learn that vocal sounds can be used, as tools, to affect the environment.

	%

	\subsection{Hierarchical representation of actions}

		\paragraph{}
		The study of the control of manipulation actions in humans has revealed a modular representation of actions 
		either in the cerebral cortex and in the spinal 
		cord with compositionality: an infinite number of movements can be expressed through combination of simple primitives, 
		and generalization: certain neurons (higher 
		in the hierarchy) can represent actions independently of the effectors used \cite{cangelosi2010integration}.

		\paragraph{}
		The same idea holds for language expressiveness which is based on syntactic hierarchical combinations 
		on a vocabulary, that open infinite semantic possibilities. 
		Greenfield has also argued that this parallel between manipulation and language compositionality can be found in the human ontegenic development
		with combinatorial steps for manipulation and syntax acquired approximately at the same period and in the same order \cite{green}. 
		Also, the author explains that the development of the neural substrates for language and tool use could be an ontogenic homology as first of all
		the same neural computations for hierarchical combinations and their semantics should take place for both modalities, and furthermore 
		experiments with Broca's and Wernicke's aphasics show that hierarchical organization for language and manipulation is linked. 
		Broca's aphasics, who have less syntactic organization of speech were shown to also have problems of representation of the hierarchical organization
		of constructions with blocks, whereas Wernicke's aphasics, whose syntax is normal but speech semantics is impaired, succeed in representing such objects 
		hierarchies.

		\paragraph{}
		Functional MRI experiments by Higuchi et al. have shown that the human's neural substrates for tool use and language is indeed shared in 
		the dorsal BA44 Broca's area \cite{higuchi}, which gives evidence for the similar neural computations used. 
		They furthermore argue that these results supports the hypothesis that tool use have appeared first in primate evolution in F5 area,
		and then the language has developed in humans reusing part of tool use and manipulation neural substrates in human's Broca area, homolog of primate's F5.

		\paragraph{}
		Like a developing child, a developmental robot will have to incrementally explore skills that add up to the hierarchy of previously learned skills 
		throughout its life, with a constraint being the cost and time of experimentation. 
		We will seek to define curiosity-driven hierarchical learning architectures 
		that could reuse the sensorimotor contingencies previously learned and to combine them 
		to explore more efficiently new complex sensorimotor models.

		\paragraph{}
		Different computational models have the possibility to learn skill hierarchies. 
		In finite environments represented by a factored Markov Decision Process \cite{vig}, an intrinsic motivation towards actions 
		maximizing Dynamic Bayesian Networks' structure has been shown to allow the learning of the environment's structure.

		\paragraph{}
		In continuous environments but with discrete actions, Metzen et al. \cite{metzen2013} use the framework of options \cite{sutton1999between} 
		to learn skill hierarchies. 
		An intrinsic motivation rewards positively the novelty of the states encountered and negatively the prediction error of the learned skill model.

		\paragraph{}
		The model from Fabisch et al. \cite{fabisch2014active} learns in a setting with a discrete task space (called contexts).
		It uses an intrinsic motivation for learning progress, and a Multi-Armed Bandit algorithm (D-UCB) to choose on which context the agent should train for.
		The Upper Confidence Bound algorithm chooses between contexts given their estimated learning progress and the uncertainty of these estimations
		by picking the context with the maximum upper confidence bound.
		In other words, it maximizes the expected reward plus something related to the uncertainty associated with it, selecting either contexts with 
		certain high rewards or ones with uncertain poor reward.
		This algorithm embeds directly a solution the exploration-exploitation trade-off problem as it represents the exploitation 
		of knowledge by the expected progress and the exploration of other solutions by the uncertainty bonus. 
		This algorithm supposes a stationary learning progress on each context so the authors use an adaptation 
		(D-UCB, \cite{kocsis2006discounted}) to encompass non-stationary learning progress.
		% Sliding Window UCB: \cite{garivier2011upper}

		\paragraph{}
		In a fully continuous setting, Mugan et al. \cite{mugan} have developed an algorithm that first learns a qualitative representation of environment states
		and actions in order to then learn the structure of Dynamic Bayesian Networks representing the temporal contingencies of those states and actions.
		In order to choose which action to practice, the authors use the IAC \cite{oudeyer_intrinsic_2007} where the agent 
		is intrinsically motivated to choose actions that are estimated to yield high prediction error progress.

		\paragraph{}
		Here, we will rely more specifically on the SAGG-RIAC architecture \cite{baranes_active_2013}.
		This architecture learns a single mapping between continuous motor and sensori (or task) 
		spaces with a competence-based intrinsic motivation. 
		In our hierarchy of sensorimotor models, each model will be explored using the SAGG-RIAC procedure, but it could be replaced by another one 
		without changing the mechanisms to learn the hierarchy that will be assessed.

	%

	\subsection{Learning from social interaction}

		\paragraph{}
		During their first year of life, infants learn progressively how to use their vocal tract. 
		At birth, they produce immature protophones like squeals, growls or quasi-vowels, and they are able to produce the vowels and speech-like syllables of their native language \cite{fenson1994variability} at one year old.
		Research on prelinguistic infants has been carried out about the way they learn to produce those specific sound, 
		and has shown that they do not explore and learn only by themselves but rather that they spend a great part of their time interacting with their parents and other adults.		
		At the age of 3 to 4 month-old \cite{kuhl1991}, infants have been shown to imitate the vowels produced by an adult speaker,
		and therefore imitation is thought to be one of the important pathways to social and vocal development \cite{meltzoff1999born}.

		\paragraph{}
		Others psychological studies have shown that infants early come to understand that their vocalizations can be used to get social 
		feedback from their caregiver.
		For instance, Franklin et al. experimented how motivated the infant is in learning 
		by this social interaction loop \cite{franklin2014effects} with
		a Face-to-Face/Still-Face/Reunion paradigm with 6 month-old. 
		The mother and her child were in free interaction 
		during the first phase to measure baseline vocalizations number and types. 
		Then the mother was asked to stay looking at the child with no interaction during the second phase, and they were free again in the third phase.
		They show an increase of protophones vocalizations from FF to SF phases in all categories measured: full vowels, quasi-vowels, squeals and growls, 
		and not cry or laugh. 
		They argue that by 6 month of age infants have learned that they can re-engage their parent through speech-like vocalizations, which is a step 
		toward a pragmatic use of the perlocutionary effect of their vocalizations, that will be a component of their later communication abilities.

		\paragraph{}
		An other mechanism allowing efficient learning from social feedback is that infants may attend to engage in social interactions 
		when they are ready to learn and have a high arousal level. 
		This effect has been suggested in different settings: when infants are vocalizing, or pointing to objects. 
		For instance, Goldstein et al. show that when an experimenter responded to infants 
		looking and vocalizing to an object by naming the object, infants showed stronger label-object association than in a yoked condition where the
		experimenter only responded when infants were looking at the object and not vocalizing \cite{goldstein2010learning}. 
		Also, in \cite{begus}, infants were more able to learn from the demonstration by the experimenter 
		of the function of an object when they had pointed to before than 
		when they had pointed to a different object. Vocalizing and pointing to objects, as attempts to get information from adults 
		might thus be linked to a focused attentional ready-to-learn state.

		\paragraph{}
		Thus infants imitate their parents and if this source of learning is not available, 
		they know how to try to re-engage their parents into social interaction
		and, furthermore, they learn better when they engaged the interaction and received a natural response.

		\paragraph{}
		Those mechanisms of social learning have been modeled by different approaches.
		We are interested here in models in which the learning agent can autonomously choose when to learn by social interaction and when to learn without
		interaction, like an infant that sometimes plays alone and sometimes ask parents for interaction, with the hypothesis that the agent knows
		better than teachers what and when to learn.
		In robotics settings, NGuyen et al. have developed a learning architecture that can decide what to imitate, 
		how, and from which teacher \cite{nguyen2012}.
		The architecture called Socially Guided Intrinsic Motivation with Active Choice of Teacher and Strategy (SGIM-ACTS) estimates the learning 
		progress from each strategy. The different strategies are: learning autonomously, or learning in interaction, by mimicry or by emulation.
		In those cases, the agent also learns from who to imitate, provided teachers of different skills are 
		available. This learning architecture is assessed on moving objects tasks.

		\paragraph{}
		Moulin-Frier et al. have used the SGIM-ACTS framework to implement their model which is learning vocalizations by social interaction
		 \cite{moulin-frier_self-organization_2014}.
		At each exploration step, their agent has to first choose either to autonomously explore the sounds produced by its vocal tract, 
		or to engage in social interaction, based on the learning progress estimated for each strategy.
		If the exploring strategy is chosen, the agent uses the SAGG-RIAC architecture to self-generate goals to try to reach in the sensori space
		composed of the two first formants of the produced sound.
		Otherwise, the agent engages in social interaction and receives one of the predifined adult's sounds as demonstration, 
		and tries to imitate that sound.

		\paragraph{}
		We will extend our models of hierarchical skill learning to integrate the mechanisms of evaluation of the interest of social guidance of SGIM-ACTS
		that allow to learn efficiently from different channels of social guidance.

	%

%

\newpage

\section{Methods}

	\subsection{Exploration architectures}

		\paragraph{}
		In this section we first give details about models and how they are learned, then 
		define the learning architectures developed in this work, and the control architectures to compare with.
		We use and extend the Explauto library \cite{moulin-frier_explauto:_2014} which purpose is to study autonomous exploration in developmental robotics.

		\subsubsection{Learning a model}

			\paragraph{}
			In the Explauto framework, a sensorimotor model mapping a motor space to a goal space is learned 
			together with an interest function over the goal space. 
			These 2 functions are considered as slots that can be instanciated by any algorithms, 
			without changing the considered architecture.

			\paragraph{}
			In our experiments, the mapping between the motor space and the sensori space will be done by storing all the sensorimotor 
			experience (list of tuples $(m, s)$), and computing nearest neighbors on that dataset.
			For instance, to predict the outcome of a given motor command $m$, we look for the nearest neighbors of $m$ in the motor part of the 
			dataset, and output the corresponding $s$. 
			On the other hand, to find the motor command that would allow to reach a given sensori experience $s$, 
			we look for the nearest neighbors of $s$ in the sensori part of the 
			dataset, and output the corresponding $m$. 
			The nearest neighbor function is the simplest regression algorithm and makes no hypothesis on the mapping, 
			but more complex algorithms could be used like Locally Weighted Regression \cite{lwr}, that supposes a locally linear mapping.

			\paragraph{}
			The interest function evaluates how much interesting exploring a given part of the goal space is.
			In the motor and goal babbling algorithms, we do not use such a interest function. 
			A motor babbling agent just randomly draw motor commands to execute and stores its sensori input.
			A goal babbling agent have a constant interest function: it randomly selects goals to be explored.

			\paragraph{}
			An iteration of the learning of a model is as follows: 
			the robot selects a point in its goal space according to the interest function and infers parameters 
			to get close to that goal based on the past sensorimotor experience.
			It also adds some exploration noise to discover new motor configurations near the ones already known.
			Then it executes the motor trajectory corresponding to the parameters, and observes the consequences in the goal space.

			\paragraph{}
			More elaborated interest functions include the SAGG-RIAC procedure \cite{baranes2010intrinsically}
			that splits the goal space in a binary tree and infers the interest to explore on each leaf of the tree.
			A leaf is splitted when a maximum number of points is reached ($100$ in our experiments), and the 
			split value is chosen successively on each dimension of the goal space. 
			The value is chosen to maximize the difference of interest in the 2 sub-regions of the leaf:

			$$split\_value = argmax\big(N_1\times N_2 \times |interest(R_1) - interest(R_2)|\big),$$
			where $N_i$ is the number of points in the subregion $i$ and $interest(R_i)$ the interest of exploring subregion $i$.

			\paragraph{}
			The interest is computed as the absolute value of the competence progress, as a decreasing competence means 
			that something has changed in the corresponding region (e.g. a motor has crashed so unexpected sensori experience happens), that also become interesting.			
			The competence on the task $s$ is then the distance between $s$ and the actually reached sensori experience $s'$ when trying to get as close to 
			$s$ as possible.
			In our experiments, the interest of a region of the tree is measured as the difference of competence between the firsts and lasts experiments: 
			$$interest(R_i) = \Bigg|~ \frac{\sum\limits_{i=3n/4}^{i=n}competence(i) - \sum\limits_{i=1}^{i=n/4}competence(i)}{n/4}~\Bigg|$$

		%

		\subsubsection{Control architectures}

			\paragraph{}
			We compare our architectures to the control one where the robot learns directly a mapping between $M$ and $S$, 
			either with a competence-based intrinsic motivation (Algorithm~\ref{algofgs}) or a fully random motor babbling (Algorithm~\ref{algofmb}).

			\begin{algorithm}
				\caption{Motor Babbling Flat Architecture}
				\label{algofmb}
				\begin{algorithmic}[1]
					\Require Motor space $M = \{m_1, ...~ m_m\}$
					\Require Sensor space $S$
					\State \texttt{sm\_model} $\gets$ SMModel($M,~S$)
					\Comment{Initializes the sensorimotor model}
					\Loop
						\State $m$ $\gets$ Random($M$)
						\Comment{Draws a random motor command}
						\State $s$~ $\gets$ Environment($m$)
						\Comment{Applies it and observes the effect on the environment}
						\State Update \texttt{sm\_model} with (m,s)
					\EndLoop
				\end{algorithmic}
			\end{algorithm}

			\begin{algorithm}
				\caption{Goal-Space Flat Architecture}
				\label{algofgs}
				\begin{algorithmic}[1]
					\Require Motor space $M = \{m_1, ...~ m_m\}$
					\Require Sensor space $S$
					\State \texttt{sm\_model} $\gets$ SMModel($M,~S$)
					\State \texttt{im\_model} $\gets$ IMModel($S$)
					\Loop
						\State $s_g$ $\gets$ Choose(\texttt{im\_model})
						\Comment{The interest model generates a goal in $S$}
						\State $m$ $\gets$ Infer(\texttt{sm\_model}, $s_g$)
						\Comment{The sensorimotor model infers a command to reach this goal}
						\State $s$~ $\gets$ Environment($m$)
						\State Update \texttt{sm\_model} with $(m,~s)$
						\State Update \texttt{im\_model} with $(s,~s_g)$
					\EndLoop
				\end{algorithmic}
			\end{algorithm}

		%

		\subsubsection{Simple hierarchical architecture}

			\paragraph{}
			In the case of 2 sensorimotor models, with reusing the other, we can define a simple hierarchical architecture
			that explores first the first model and then the second.
			The agent explores first the mapping between $M$ and $S_1$ and then a mapping between $S_1$ and $S_2$. 
			When exploring the second one, the agent chooses a point in $S_1$ to produce and uses the first mapping 
			to select the best motor configuration to obtain this subtask.

			\paragraph{}
			We define the Motor Babbling Simplest First Hierarchical Architecture (Algorithm~\ref{algombh}) as a control to compare with the
			Goal-Space Simplest First Hierarchical Architecture (Algorithm~\ref{algogsh}), in which an interest model, possibly a random goal 
			babbling or the SAGG-RIAC-like tree, chooses the goals to explore.

			\begin{algorithm}
				\caption{Motor Babbling Simplest First Hierarchical Architecture}
				\label{algombh}
				\begin{algorithmic}[1]
					\Require Motor space $M = \{m_1, ...~ m_m\}$
					\Require Sensor spaces $S_1,~S_2$
					\Require Total number of iterations $n$

					\State \texttt{sm\_model1} $\gets$ SMModel($M,~S_1$)
					\State \texttt{sm\_model2} $\gets$ SMModel($S_h,~S_2$)
					\For{$n/2$ iterations}
						\State $m$ $\gets$ Random(M)
						\State $s_1,~s_2$~ $\gets$ Environment($m$)
						\State Update \texttt{sm\_model1} with $(m,~s_1)$
						\State Update \texttt{sm\_model2} with $(s_1,~s_2)$
					\EndFor
					\For{$n/2$ iterations}
						\State $s_1$ $\gets$ Random($S_1$)
						\Comment{Draws a random hand movement}
						\State $m$ $\gets$ Infer(\texttt{sm\_model}, $s_1$)
						\State $s'_1,~s_2$~ $\gets$ Environment($m$)
						\State Update \texttt{sm\_model1} with $(m,~s'_1)$
						\State Update \texttt{sm\_model2} with $(s'_h,~s_2)$
					\EndFor
				\end{algorithmic}
			\end{algorithm}

			\begin{algorithm}
				\caption{Goal-Space Simplest First Hierarchical Architecture}
				\label{algogsh}
				\begin{algorithmic}[1]
					\Require Motor space $M = \{m_1, ...~ m_m\}$
					\Require Sensor spaces $S_1,~S_2$
					\Require Total number of iterations $n$

					\State \texttt{sm\_model1} $\gets$ SMModel($M,~S_1$)
					\State \texttt{sm\_model2} $\gets$ SMModel($S_1,~S_2$)
					\State \texttt{im\_model1} $\gets$ IMModel($S_1$)
					\Comment{Initializes the interest models}
					\State \texttt{im\_model2} $\gets$ IMModel($S_2$)
					\For{$n/2$ iterations}
						\State $s_1$ $\gets$ Choose(\texttt{im\_model1})
						\Comment{The first interest model generates a goal in $S_1$}
						\State $m$ $\gets$ Infer(\texttt{sm\_model1}, $s_1$)
						\Comment{The first sm infers a command to reach this goal}
						\State $s'_1,~s_2$~ $\gets$ Environment($m$)
						\State Update \texttt{sm\_model1} with $(m,~s'_1)$
						\State Update \texttt{sm\_model2} with $(s'_1,~s_2)$
						\State Update \texttt{im\_model1} with $(s'_1,~s_1)$
					\EndFor
					\For{$n/2$ iterations}
						\State $s_2$ $\gets$ Choose(\texttt{im\_model2})
						\Comment{The second interest model generates a goal in $S_2$}
						\State $s_1$ $\gets$ Infer(\texttt{sm\_model2}, $s_2$)
						\Comment{The second sm model infers a hand movement}
						\State $m$ $\gets$ Infer(\texttt{sm\_model1}, $s_1$)
						\Comment{The first sm model infers a command}
						\State $s'_1,~s_2$~ $\gets$ Environment($m$)
						\State Update \texttt{sm\_model1} with $(m,~s'_1)$
						\State Update \texttt{sm\_model2} with $(s'_1,~s'_2)$
						\State Update \texttt{im\_model2} with $(s'_2,~s_2)$
					\EndFor
				\end{algorithmic}
			\end{algorithm}

		\subsubsection{Strategic choice}

			As the switch between the exploration of the two models might be difficult to set by hand, 
			another approach is to let the agent choose at each iteration to explore the model that yields the highest competence progress 
			(Algorithm~\ref{algostrat}). 
			This strategic learning approach has first been proposed to allow an agent to choose between 
			different learning modalities \cite{nguyen2012}.

			\begin{algorithm}
				\caption{Goal-Space Strategic Choice Hierarchical Architecture}
				\label{algostrat}
				\begin{algorithmic}[1]
					\Require Motor space $M = \{m_1, ...~ m_m\}$
					\Require Sensor spaces $S_1,~S_2$

					\State \texttt{sm\_model1} $\gets$ SMModel($M,~S_1$)
					\State \texttt{sm\_model2} $\gets$ SMModel($S_1,~S_2$)
					\State \texttt{im\_model1} $\gets$ IMModel($S_1$)
					\State \texttt{im\_model2} $\gets$ IMModel($S_2$)
					\State \texttt{models\_interest} $\gets$ MAB(\texttt{im\_model1}, \texttt{im\_model2})
					\Comment{Initializes a Multi-Armed Bandit on models}
					\Loop
						\State \texttt{model\_to\_train} $\gets$ Choose(\texttt{models\_interest})
						\If{\texttt{model\_to\_train} $=$ \texttt{im\_model1}}
							\State $s_1$ $\gets$ Choose(\texttt{im\_model1})
							\State $m$ $\gets$ Infer(\texttt{sm\_model1}, $s_1$)
							\State $s'_1,~s_2$~ $\gets$ Environment($m$)
							\State Update \texttt{sm\_model1} with $(m,~s'_1)$
							\State Update \texttt{sm\_model2} with $(s'_1,~s_2)$
							\State Update \texttt{im\_model1} with $(s'_1,~s_1)$
							\State Update \texttt{models\_interest} with Interest(\texttt{im\_model1})
							\Comment{The MAB is updated with the current interest of the first interest model}

						\ElsIf{\texttt{model\_to\_train} $=$ \texttt{im\_model2}}

							\State $s_2$ $\gets$ Choose(\texttt{im\_model2})
							\State $s_1$ $\gets$ Infer(\texttt{sm\_model2}, $s_2$)
							\State $m$ $\gets$ Infer(\texttt{sm\_model1}, $s_1$)
							\State $s'_1,~s_2$~ $\gets$ Environment($m$)
							\State Update \texttt{sm\_model1} with $(m,~s'_1)$
							\State Update \texttt{sm\_model2} with $(s'_1,~s'_2)$
							\State Update \texttt{im\_model2} with $(s'_2,~s_2)$
							\State Update \texttt{models\_interest} with Interest(\texttt{im\_model2})
							\Comment{The MAB is updated with the current interest of the second interest model}
						\EndIf
					\EndLoop
				\end{algorithmic}
			\end{algorithm}

			Those first algorithms are defined in the case of the learning of 2 sensorimotor models, but the extension to an arbitrary hierarchy of 
			sensorimotor models is straghtforward: we explore the models from the lower layer to the higher.
		%

		\subsubsection{Interacting models in hierarchy}
		\label{sec:interacting}
			\paragraph{}
			The previous hierarchical learning architectures considered models as independents building blocks that each explores a mapping with
			its own policy. 
			However, optimally exploring the different models of the hierarchy does not imply that we are optimally exploring the overall hierarchy, 
			as parts of the sensori space of an intermediate model might be of no relevance to the complex skills being learned, and others might be
			of critical importance. 
			For instance, if a first model learns how to move the hand of the robot at different positions, and a second model 
			learns the consequencies of pushing on certain buttons in front of the robot, then learning to acurately to put hand of the robot behind 
			it for the first model is not useful to refine the other models. On the other hand, being able to robustly reach the different buttons is of 
			major interest for the second model and so could be more explored by the first model.
			We thus define here 2 types of architectures where the models do not learn independently but communicate information what seems 
			useful for them to learn.

			\paragraph{Top-Down Drive}~\\

			Here, we let the highest model in the hierarchy draw goals in $S_2$, then infer an interesting hand's movement 
			in $S_1$ to try in order to reach that goal (Algorithm~\ref{algotdd}).
			The lowest model in the hierarchy is now given a certain amount of iterations to try motor configurations to obtain this hand's movement. 
			It can do so either by sampling around its best already known motor configuration for that hand's movement, 
			or with a more sophisticated black-box optimization technique like the Covariance Matrix Adaptation Evolution Strategy \cite{cma}.

			\begin{algorithm}[H]
				\caption{Goal-Space Top-Down Drive Hierarchical Architecture}
				\label{algotdd}
				\begin{algorithmic}[1]
					\Require Motor space $M = \{m_1, ...~ m_m\}$
					\Require Sensor spaces $S_1,~S_2$

					\State \texttt{sm\_model1} $\gets$ SMModel($M,~S_1$)
					\State \texttt{sm\_model2} $\gets$ SMModel($S_1,~S_2$)
					\State \texttt{im\_model1} $\gets$ IMModel($S_1$)
					\State \texttt{im\_model2} $\gets$ IMModel($S_2$)
					\Loop
						\State $s_2$ $\gets$ Choose(\texttt{im\_model2})
						\State $s_1$ $\gets$ Infer(\texttt{sm\_model2}, $s_2$)
						\State Explore\_Around(\texttt{sm\_model1}, $s_1$)
						\Comment{The first model can explore for a few iterations in order to reach $s_1$}
						\State $m$ $\gets$ Infer(\texttt{sm\_model1}, $s_1$)
						\Comment{Now the best motor command is chosen}
						\State $s'_1,~s_2$~ $\gets$ Environment($m$)
						\State Update \texttt{sm\_model1} with $(m,~s'_1)$
						\State Update \texttt{sm\_model2} with $(s'_1,~s'_2)$
						\State Update \texttt{im\_model2} with $(s'_2,~s_2)$
					\EndLoop
				\end{algorithmic}
			\end{algorithm}

			We also explicit an exemple with 2 lower models and 1 higher model in the hierarchy (Algorithm~\ref{algotdd21}).
			This algorithm can be extended to a tree hierarchy i.e. a hierarchy where each model is connected to at most 1 higher level model.
			If a model $mod$ is connected to 2 higher level models, each giving $mod$ a goal to explore, then the choice of the goal to explore for $mod$ is not straightforward.
			A possibility to extend this algorithm to other hierarchies (where only one model is not reused) is derived in the next paragraph.

			\begin{algorithm}[H]
				\caption{Goal-Space Top-Down Drive 2-low/1-high Hierarchical Architecture}
				\label{algotdd21}
				\begin{algorithmic}[1]
					\Require Motor spaces $M_1,~M_2$
					\Require Sensor spaces $S_1,~S_2,~S_3$

					\State \texttt{sm\_model1} $\gets$ SMModel($M_1,~S_1$)
					\State \texttt{sm\_model2} $\gets$ SMModel($M_2,~S_2$)
					\State \texttt{sm\_model3} $\gets$ SMModel($S_1S_2,~S_3$)
					\State \texttt{im\_model1} $\gets$ IMModel($S_1$)
					\State \texttt{im\_model2} $\gets$ IMModel($S_2$)
					\State \texttt{im\_model3} $\gets$ IMModel($S_3$)
					\Loop
						\State $s_3$ $\gets$ Choose(\texttt{im\_model3})
						\State $s_1,~s_2$ $\gets$ Infer(\texttt{sm\_model3}, $s_3$)
						\State Explore\_Around(\texttt{sm\_model1}, $s_1$)
						\Comment{The first model can explore for a few iterations in order to reach $s_1$}
						\State Explore\_Around(\texttt{sm\_model2}, $s_2$)
						\Comment{The second model can explore for a few iterations in order to reach $s_2$}
						\State $m_1$ $\gets$ Infer(\texttt{sm\_model1}, $s_1$)
						\State $m_2$ $\gets$ Infer(\texttt{sm\_model1}, $s_2$)
						\State $s'_1,~s'_2,~s'_3$~ $\gets$ Environment($m_1m_2$)
						\State Update \texttt{sm\_model1} with $(m_1,~s'_1)$
						\State Update \texttt{sm\_model2} with $(m_2,~s'_2)$
						\State Update \texttt{sm\_model3} with $(s'_1s'_2,~s'_3)$
						\State Update \texttt{im\_model3} with $(s'_3,~s_3)$
					\EndLoop
				\end{algorithmic}
			\end{algorithm}

			~\\
			\paragraph{Merging interest models for hierarchy}~\\
			\paragraph{}
			Another possibility for a higher model to guide the exploration of a lower is to compute the interest of the second model
			in its motor space $S_1$ as the inverse of the interest distribution (the distribution of goals to be chosen in $S_2$, by the sensorimotor mapping function). 
			The inverse of the distribution can be computed through Monte-Carlo sampling.
			The lower model then gets a guided interest distribution in its sensori space $S_1$, and merges this distribution with its own interest 
			distribution when it has to generate goals in $S_1$. 
			If a model is connected to more than 1 higher models, it has to merge its own interest distribution with each of the guided output distributions from the higher models that are connected to it.
			If a model is connected to more than 1 lower model, it outputs one distribution for each connected lower model, computed by the same inversion mechanism.
			This algorithm has not yet been implemented.

			\begin{figure}[H] 
				\centering 
				\includegraphics[width=12cm]{./include/tddriveext.png}
				\caption{Top-Down Drive to guide exploration of lower level models}
				\label{tddrive}
			\end{figure}

		%

		\subsubsection{Exploration of sensorimotor models of increasing complexity}
		\label{sec:increasing}

			\paragraph{}
			In the previous learning algorithms developed, 
			the hierarchy of models to learn is given to the agent as if it already knew the combinations of actions
			to explore in order to learn the successive tasks.
			We describe here an algorithm (Algorithm~\ref{algomult}) that autonomously generates different hierarchies of sensorimotor models and decides which of them to explore.
			To explore a hierarchy, it then uses the previously described algorithms that explore in a fixed hierarchy (e.g. Top-Down Drive, Sec. \ref{sec:interacting}).

			\paragraph{}
			Let $O = \{O_1, ...~ O_p\}$ be a set of operators allowed to combine the actions to reuse, for instance the sequence operator, that
			takes 2 actions and return the action that executes those 2 actions in sequence.
			Also, the parallel operator
			takes 2 actions and return the action that executes those 2 actions in parallel, when possible, and if the 2 actions take different values on 
			some motor, one of them is randomly chosen.

			\paragraph{}
			Given a set of motor spaces and sensori spaces (for instance vocal and arm motor spaces, visual and audio sensori spaces), the algorithm
			explores first the simplest sensorimotor models (e.g. $M_1S_1$, $M_1S_2$, $M_2S_1$, $M_2S_2$), and when making too small progress on those models
			complexifies the hierarchy of models.
			It then combine known models with the allowed operators to form a new more complex one (e.g. a sequence of an action in $S_1$ with the $M_1S_1$ 
			model and an action in $M2$, with $S_1$ as sensorimotor model).
			The algorithm increases the complexity of the hierarchies step by step, the complexity being the number of sensorimotor models 
			reused plus the number of sensori spaces used.

			\paragraph{}
			To decide which hierarchy to explore at each learning time step, a Multi-Armed Bandit algorithm monitors interest to explore (e.g. the competence progress) on each of them.
			The interest of a hierarchy is computed as the competence progress over the last experiments 
			on the models of that hierarchy (with a sliding window).

			\paragraph{}
			Each model can be used by several hierarchies that do not duplicate it but share it. Exploring a given hierarchy can thus benefits the other hierarchies.			
			This algorithm has not yet been implemented.

			\begin{algorithm}[H]
				\caption{Exploration of Sensorimotor Models of Increasing Complexity}
				\label{algomult}
				\begin{algorithmic}[1]
					\Require Motor spaces $M = \{M_1, ...~ M_m\}$
					\Require Sensor spaces $S = \{S_1, ...~ S_n\}$
					\Require Operators $O = \{O_1, ...~ O_p\}$
					\State \texttt{models\_MAB} $\gets$ MAB(list of models $(M_iS_j)$ with $i \leq m$ and $j \leq n$)~~~
					\Comment{Initialize a Multi-Armed Bandit with models of complexity $0$}
					\Loop
						\If{all models in \texttt{current\_models} are not interesting}

							\State \texttt{actions} $\gets M~\cup $ \texttt{models\_MAB}
							\State \texttt{combined\_actions} $\gets$ O(\texttt{actions} $\times$ \texttt{actions})
							\State \texttt{possible\_models} $\gets$ (\texttt{actions}$ ~\cup~ $\texttt{combined\_actions})$ \times P(S)$
							\State $c \gets$ max\_complexity(\texttt{current\_models})
							\If{some model of \texttt{models\_MAB}, has complexity $c$}
								\State \texttt{new\_model} $\gets$ a model of complexity $c$ from \texttt{possible\_models}
							\Else
								\State \texttt{new\_model} $\gets$ a model of complexity $c+1$ from \texttt{possible\_models}
							\EndIf
							\State add \texttt{new\_model} to \texttt{models\_MAB}
						\Else
							\State \texttt{model} $\gets$ Choose(\texttt{models\_MAB})
							\State Train(\texttt{model})
							\State Update \texttt{models\_MAB} with Interest(\texttt{model})
						\EndIf
					\EndLoop
				\end{algorithmic}
			\end{algorithm}

		%

		\subsubsection{Formulation as a Directed Acyclic Graph}
		\label{sec:dag}

			\paragraph{}
			The hierarchies of models can be formalized more efficiently, with a directed acyclic graph (DAG) that links motor and sensori domains and
			intermediate and top-level models (the models that are not reused by higher level models).
			Each model could then receive top-down drive from all the models from different hierarchies that reuse it, which would be more efficient that exploring independently the 
			hierarchies with the Top-Down Drive algorithm. See Fig. \ref{exemple} for an exemple of such hierarchies.
			In order to choose which model to explore, a tradeoff can be done for each model between autonomous interest and top-down drive and social guidance interests.
			The model to explore would then be the one with max tradeoff interest.

			\begin{figure}[H] 
				\centering 
				\begin{tikzpicture}[node distance=2.5cm,>=stealth',bend angle=45,auto]

					\tikzstyle{dom}   = [ellipse, thick, draw=black!75, fill=blue!20,  minimum height=10mm, minimum width=20mm]
					\tikzstyle{prim dom}   = [dom,  minimum height=15mm, minimum width=30mm,  fill=green!20]
					\tikzstyle{model} = [rectangle, thick, draw=black!75, fill=black!20, minimum size=15mm]
					\tikzstyle{top model} = [model, fill=red!20]

					\begin{scope}
						\node [prim dom] (pd1) {$M_1$};
						\node [prim dom] (pd2) [xshift=5cm] {$M_2$};

						\node [model] (m1) [above of=pd1] {$mod_1$}
						edge [pre]                  (pd1);

						\node [dom] (d1) [above of=m1] {$S_1$}
						edge [pre]                (m1);

						\node [model] (m2) [above of=pd2] {$mod_2$}
						edge [pre]                  (pd2);

						\node [dom] (d2) [above of=m2] {$S_2$}
						edge [pre]                (m2);

						\node [model] (m3) [above of=d1, label={[label distance=0.05cm]280:$O_1$}] {$mod_3$}
						edge [pre]                  (d1)
						edge [pre, bend right=20]                  (d2);

						\node [dom] (d3) [above of=m3] {$S_3$}
						edge [pre]                (m3);

						\node [top model] (m4) [above of=d2, label={[label distance=0.05cm]265:$O_2$}] {$mod_4$}
						edge [pre, bend left=20]                  (d1)
						edge [pre]                  (d2);

						\node [dom] (d4) [above of=m4] {$S_4$}
						edge [pre]                (m4);

						\node [top model] (m5) [above of=d3, xshift=1cm, label={[label distance=0.05cm]270:$O_2$}] {$mod_5$}
						edge [pre]                  (d3)
						edge [pre, bend right=10]                  (d2);

						\node [dom] (d5) [above of=m5] {$S_5$}
						edge [pre]                (m5);

					\end{scope}

					\begin{pgfonlayer}{background}
						\filldraw [line width=4mm,join=round,black!10]
						(d5.north  -| pd2.east)  rectangle (pd1.south  -| pd1.west);
					\end{pgfonlayer}
				\end{tikzpicture}

				\caption{Exemple of 2 hierarchies sharing models.
				Ellipses represent domains. Green ellipses: motor domains. Blue ellipses: sensori domains. Squares represent models. Gray squares: intermediate models. Red squares: top-level domains.	First hierarchy is composed of intermediate models $mod_1$, $mod_2$, $mod_3$, and top-level model $mod_5$.  Second hierarchy is composed of intermediate models $mod_1$, $mod_2$, and top-level model $mod_4$.
				}
				\label{exemple}
			\end{figure}

		%

		\subsubsection{Integrating social interaction}
			\label{sec:social}
			\paragraph{}
			We describe here different ways to integrate social interaction to those hierarchical learning architectures.				
			The following one is inspired from the SGIM-ACTS learning architecture \cite{nguyen2012}. 
			In SGIM-ACTS, the learning progress from each strategy are estimated. 
			The agent can learn autonomously, or learn in interaction.	
			When learning by interaction, the agent also learns from who to imitate, if teachers of different skills are available. 			
			For each model, we could thus estimate the interest of asking for teacher input (sensori tasks) on that model. 
			When the agent explores a given model, it then first chooses by which strategy to explore it: self-generation of goals, or teacher input, 
			and from which teacher to get the input that will serve as socially guided goal to imitate.

			\paragraph{}
			Another possibility is to merge the input from social peers with the interest distribution of the models.
			When generating a goal to explore for a given model, the interest distribution of the model is merged with the top-down drive interest distributions from higher models
			plus social interest given as a another distribution.

			\paragraph{}
			Also, if the social input is not specified at the goal spaces level, but more abstract, it could be integrated at the level of the choice of model or choice of hierarchy. 
			When choosing which hierarchy (in Algo. \ref{algomult} in the Multi-Armed-Bandit) or which model (in Algo. of Section \ref{sec:dag}) to explore, the agent could merge the interest with a social
			value or reinforcement for those hierarchies or models. 
			The implementation and evaluation of those different algorithms remains to be done.

		%

	%

	\subsection{Measures}

		\subsubsection{Exploration}

			\paragraph{}
			Exploration is a measure of how well the agent has found diverse outcomes in its task space. 
			It makes no assumptions about the interest of exploring given regions of the task space from the viewpoint of the engineer, 
			neither if we want the robot to learn specific tasks or if we know that certain tasks will be more useful later for the robot.
			To compute the quantity of exploration we consider the task space as a grid with small cells and count the number of cells that have been reached.

		%

		\subsubsection{Competence}
			\label{sec:competence}
			\paragraph{}
			Given a task region where we want to evaluate the competence of the agent, we draw random goals in that region and measure the distance of
			the point reached from that goal.

		%

		\subsubsection{Competent exploration}

			\paragraph{}
			As the agent self-generates goals in the task space, it might not yet have explored that evaluated part of the environment, 
			or in another run, have explored
			it very early, so it is hard to interpret this competence as a general progress.
			We thus define an intermediate measure that evaluates how well competent is the robot on the explored part of the task space.
			The competent exploration is thus the number of cells explored (as in the exploration measure) but that the robot can reach again,
			with some margin, when asked for it.

		%

		\begin{figure}[H] 
			\centering 
			\subfloat[]{\includegraphics[height=7cm]{./include/measure_explo.png}}
			\hfil
			\subfloat[]{\includegraphics[height=7cm]{./include/measure_comp.png}}
			\hfil
			\subfloat[]{\includegraphics[height=7cm]{./include/measure_explocomp.png}}
			\caption{Measures of exploration. Blue points are 2D sensori points reached during exploration.
			(a) Exploration measures approximately the reached area (approx. the blue areas). 
			(b) Competence measures the ability to reach random goals in a task area (green rectangle) e.g. the green point is a goal, the red point is the reached position, leading to a high error for that goal. 
			(c) Competent exploration measures the ability to reach goals in the explored area (approx. green areas).}
		\end{figure}  	
	%

	\subsection{Environments}

		\subsubsection{V-rep simulated physical arm}

			\paragraph{}
			The experimental setup is composed of a robotic arm with $4$ degrees of freedom from the Poppy robot \cite{poppy} simulated with the V-REP simulator 
			based on the Bullet physics engine. 
			We use Dynamical Movement Primitive \cite{ijspeert_dynamical_2013} to control the arm's movement as this framework permits the production of a diversity of arm's trajectories with few parameters.
			Each arm's degree of freedom (DOF) is controlled by a DMP with a starting and a goal position equal to the rest position of the motor.
			Each DMP is parameterized by one weight on each of $5$ basis functions whose centers are distributed homogeneously throughout the movement of duration $4s$.
			The weights are bounded in the interval [-400,400] which allow each motor to cover its standard angle interval [-1,1] during the movement.
			Each DMP outputs a series of angle positions that represents a sampling of the trajectory of one motor during the movement.
			A block is placed near the robot's hand and can be moved in two dimensions in different complex ways, e.g. with the hand pushing on the top of the block or on a side, in one or two steps.
			We voluntarily kept the number of basis functions small for the agent to learn more easily the trajectory space but still being able to move the object in different complex ways.

			\paragraph{}
			Let $M$ be the $20D$ space of the motor parameters and $S_h$ the $9D$ space representing the movement of the hand encoded by the projection of the $3D$ movement of the hand on DMPs with $3$ basis functions. 
			$S_o$ is the $2D$ space representing the position of the object at the end of the simulation.
			As we are interested in how an architecture has explored the different locations where the object can be pushed to, we define $S_o$ as the goal space where exploration will be evaluated.
			Thus, to evaluate the exploration of an architecture we compute the number of reached cells in a grid of $2cm$ width.
			And to measure the competent exploration, we draw one sample in each explored cell of the object space and use its sensorimotor model to infer a motor configuration that leads the object close to the given object goal position. We then run the movement in the simulator and check if the object has been moved less than $2cm$ away from the goal.

			\begin{figure}[H]
				\centering
				\subfloat[]{\includegraphics[width=12cm]{./include/torso.png}}\\
				\subfloat[]{\includegraphics[width=12cm]{./include/scheme.png}}
				\caption{(a) Poppy Torso in the V-Rep simulator moving a block. (b) Top: Hierarchical architecture. Bottom: Control architecture.}
				\label{fig_sim}
			\end{figure}

		%

		\subsubsection{Simple geometric arm}

			\paragraph{}
			A simple geometric arm is defined as a $3$ DOF arm with a total length of $1$ unit, and the first part of length $4/7$ units, the second $2/7$
			and the last $1/7$. The sensori space has $2$ dimensions being the X and Y position of the end of the arm.

			\paragraph{}
			We also define new sensori objects in this environment as sliders that output a linear value between 0 and 1 if the end of the arm is close to the slider,
			and 0 if it is at a distance greater than $0.15$. For instance, in Fig. \ref{arms}, in (a) the 2 sliders output 0, and in (b), the first 
			slider outputs 0 and the second outputs $0.8$.

			\paragraph{}
			This environment will also be used in a sequence of 2 arm positions, with a new sensori value $s_3$ depending on $s_1$ and $s_2$ at the 2 timesteps:
			$$r1 = (s_1\_1 + s_2\_1)/2$$
			$$r2 = (s_1\_2 + s_2\_2)/2$$
			$$s3 = (r1+r2)/2 ~if ~r1 > 0 ~and~ r2 > 0 ~else ~0$$
			The new value $s_3$ then outputs a strictly positive value only if the arm has touched the 2 sliders in sequence.

			\begin{figure}[H]
				\centering
				\subfloat[]{\includegraphics[height=2.62in]{./include/armseq1.png}}
				\subfloat[]{\includegraphics[height=2.62in]{./include/armseq2.png}}
				\caption{2 positions of the simple arm and corresponding values on the 2 sliders.}
				\label{arms}
			\end{figure}

		%

		\subsubsection{The DIVA synthesizer}

			\paragraph{}
			The DIVA synthesizer is a vocal synthesizer that outputs the formants of the sounds produced given the positions on $13$ motor values.
			As in \cite{moulin-frier_self-organization_2014}, we use only the first $7$ articulators, set the articulators 8 to 10 to 1 to ensure phonation,
			and articulators 11 to 13 to 0. We keep only the first and second formants as sensori output as they encode relatively well the vowels produces.

			\paragraph{}
			We also add a slider as in the arm environment, as a third output value, between the sounds /o/ and /y/ with margin $0.3$ octave.

			\paragraph{}
			A combined environment is also defined where the arm with one slider $s_1$ and the vocal synthesizer with one slider $s_2$ are put together.
			A third output value is then computed as 
			$$s_3 = 4 \times (s_1 - 0.5) \times (s_2 - 0.5) ~if~ s_1 > 0.5 ~and~ s_2 > 0.5~ else~ 0$$

		%

		\subsubsection{Combination of arm and vocal movements}

			\begin{figure}[H]
				\centering
				\includegraphics[width=10cm]{./include/multimodal.png}
				\caption{Multi-modal environment}
			\end{figure}

		%

	%

	\subsection{Experiments}

		\subsubsection{V-rep arm pushing a block}

			\paragraph{}
			In order to compare the first hierarchical architecture implemented, we test them on a simple hierarchical task where the robot arm simulated
			in V-rep has to push the block to different locations.
			We compare here the flat control architectures, the Simplest First, and the Top-Down guiding architectures, with goal babbling and SAGG-RIAC-like
			interest models. We measure the exploration and the competent exploration with a grid size of $0.02m$.

		%

		\subsubsection{Sequence of actions}

			\paragraph{}
			In order to compare the hierarchical architecture in a more complex hierarchical task with 2 lower models to learn before learning the high one, 
			we use simple arm environment with a sequence of 2 actions and the new output value $s_3$ depending on the value of the 2 sliders in the 2 actions.
			In hierarchical architectures, the first model learns a mapping between the first 3D $M$ action and the value on the first slider touched, the
			 second model learns a mapping between the second 3D $M$ action and the value on the second slider touched, and the high third model learns a 
			 mapping between the 2 sliders touched values and the $s_3$ new value.
			Flat architectures learn a mapping between the 2 3D actions and the 2 sliders and the new value, so a model of $M^2S_1S_2S_3$.
			We compare here the flat control architectures, the Simplest First, and the Top-Down guiding architectures, with goal babbling and SAGG-RIAC-like
			interest models. We measure the exploration on $S_3$ with a grid size of $0.001m$.

		%

		\subsubsection{Combination of arm and vocal movements}

			\paragraph{}
			In a similar mathematical problem but with a multi-modal combination of actions, we use the environment composed of a simple arm and a slider plus
			the DIVA synthesizer plus its slider.
			In hierarchical architectures, the first model learns a mapping between the first 3D $M$ action and the value on the slider, the
			 second model learns a mapping between the DIVA motor space and the value on the slider in formant space, and the high third model learns a 
			 mapping between those 2 sliders values and the $s_3$ new value.
			Flat architectures learn a mapping between the multi-modal 10D action and the 2 sliders and the new value, so a model of $M_1M_2S_1S_2S_3$.
			We compare here the flat control architectures, the Simplest First, and the Top-Down guiding architectures, with goal babbling and SAGG-RIAC-like
			interest models. We measure the exploration on $S_3$ with a grid size of $0.001m$.

		%

	%

\section{Results}

	\subsection{V-rep arm pushing a block}
	\label{result:tdd}
		\paragraph{}
		Preliminary results show comparable amounts of exploration for hierarchical and flat architectures 
		with the same SAGG-RIAC interest models (Fig. \ref{explo_vrep}).
		MS1 means that one single model learns the mapping between M and $S_h$. MS2 means that one single model learns the mapping between M and $S_o$ (flat control architecture).
		S1S2 means that one single model learns the mapping between $S_h$ and $S_o$. SEQ means that a model learns $MS_h$ in the first half and an other learns $S_hS_o$ 
		in the second half of the iterations (Simplest first strategy). TOP-DOWN-CMA means that the CMA evolution strategy is used in the model $MS_h$ to try to reach a hand movement 
		$s_h$ chosen by the model $S_hS_o$. TOP-DOWN-RANDOM means that around the $s_h$ chosen by $S_hS_o$, the first model makes 5 random explorations (taken into account in the 10,000 iterations).

		%\begin{figure}[H]
			%\centering
			%\subfloat[]{\includegraphics[height=4in]{./include/explo-2015-04-11_12-08-52_cube.png}}
			%\hfil
			%\subfloat[]{\includegraphics[height=4in]{./include/explo-2015-04-18_02-19-01-explaupoppydiva-riac-cube.png}}
			%\caption{Exploration in the object's space $S_o$. (a) SAGG-RANDOM exploration mechanism within models. (b) SAGG-RIAC.
					 %MS1: one single model learns the mapping between M and $S_h$. MS2: one single model learns the mapping between M and $S_o$.
					 %S1S2: one single model learns the mapping between $S_h$ and $S_o$. SEQ: a model learns $MS_h$ in the first half and an other learns $S_hS_o$ 
					 %in the second half of the iterations (Simplest first strategy). TOP-DOWN-CMA: the CMA evolution strategy is used in the model $MS_h$ to try to reach a hand movement 
					 %$s_h$ chosen by the model $S_hS_o$. TOP-DOWN-RANDOM: random exploration for $MS_h$ around the $s_h$ chosen by $S_hS_o$.}
			%\label{explo_vrep}
		%\end{figure}

		\begin{figure}[h]
			\centering
			\includegraphics[height=4in]{./include/explo-2015-04-18_02-19-01-explaupoppydiva-riac-cube.png}
			\caption{Exploration in the object's space $S_o$ using the SAGG-RIAC interest model.
			Mann-Whitney U tests at the end of the experiments show that the exploration measures in the MS2, SEQ and TOP-DOWN conditions
			are significatively greater ($p<0.05$) than in the MOTOR-BABBLING, MS1 and S1S2 conditions.			
		}
			\label{explo_vrep}
		\end{figure}

		\paragraph{}
		As a very high variability results of the collision between the hand and the object, only a few explored cells, were in fact competent, in other words
		when we ask the robot to go to those cells,it succeeds in only a few.
		We measured the exploration together with the competent exploration in another run with a grid of size $0.1$ (Fig. \ref{explo_comp}).
		The competent measure is the number of cells where the robot succeeds in putting again the block at that place.

		\paragraph{}
		Mann-Whitney U tests at the end of the experiments show that the exploration measures in the CONTROL-GOAL-BABBLING and TOP-DOWN-GUIDANCE conditions
		are significatively greater ($p<0.5$) than in the SEQ condition, where it is significatively greater than in the CONTROL-MOTOR-BABBLING condition.
		On the other hand, tests on the competent exploration measure show that it is significatively greater in the TOP-DOWN-GUIDANCE condition than in 
		the SEQ condition where it is significatively greater than in the CONTROL conditions.

		\begin{figure}[H]
			\centering
			\subfloat[]{\includegraphics[width=3.5in]{./include/exploration_comparison.png}}
			\subfloat[]{\includegraphics[width=3.5in]{./include/explocomp_comparison.png}}
			\caption{(a) Exploration. (b) Competent exploration. CONTROL-MOTOR-BABBLING: random motor parameters in $M$ are explored for all iterations. CONTROL-GOAL-BABBLING: one single model learns the mapping between $M$ and $S_o$. SEQ: a model learns $MS_h$ in the first half and an other learns $S_hS_o$ 
					 in the second half of the iterations (Simplest first strategy). TOP-DOWN-GUIDANCE: the CMA evolution strategy is used in the model $MS_h$ to try to reach a hand movement 
					 $s_h$ chosen by the model $S_hS_o$.}
			\label{explo_comp}
		\end{figure}

		\paragraph{}
		Results show comparable amounts of exploration for the top-down guidance and the control (goal babbling) conditions, whereas the competent exploration
		measure shows that the architectures learning an intermediate hand's movement representation allow the agent to put again the object on much more diverse
		locations. The intuition for this result is that when exploring around given motor parameters, the control architecture will modify some motor's angle trajectories and will produce more unstable interactions with the object than a hierarchical architecture that modify directly hand's Cartesian trajectory.
		A posssibilty to test this hypothesis is to choose an explored object's position $s_o$ in the condition TOP-DOWN-GUIDANCE, then infer a hand movement
		$s_h$ and then a motor set of parameters $m$ that should lead close to $s_o$. If the hypothesis is true, then given a variation $m'$ of $m$, and 
		an infered $m''$ of a variation $s_h'$ of $s_h$, the variance of the reached object position when repeating $m'$ should be higher than when 
		repeating $m''$.

		\paragraph{}
		Fig. \ref{diversity} shows the diversity of explored block position for the same experiment but several independant trials.
		This illustrates why measuring the competence (Section \ref{sec:competence}) does not make sense on a fixed subregion of the goal space as different runs
		do not explore the same parts of the space.

		\begin{figure}[H]
			\centering
			\subfloat[]{\includegraphics[height=2.4in]{./include/log1-scatter2D.png}}
			\subfloat[]{\includegraphics[height=2.4in]{./include/log2-scatter2D.png}}
			\subfloat[]{\includegraphics[height=2.4in]{./include/log3-scatter2D.png}}
			\subfloat[]{\includegraphics[height=2.4in]{./include/log4-scatter2D.png}}
			\caption{Variability in exploration in 2D space for several trials of condition TOP-DOWN-CMA-tree (SAGG-RIAC). Red square: initial position of the block.}
			\label{diversity}
		\end{figure}

	%

	\subsection{Sequence of actions}

		\paragraph{}
		Fig. \ref{explo_armseq} shows the results of the second experiment, with a sequence of 2 arm movements.
		Results show that the hierarchical Simplest First architecture explores better than the hierarchical Top-Down approach, which explores better
		than the flat architectures, either with goal babbling or SAGG-RIAC interest models.
		The motor babbling Simplest First hierarchical architecture explores also better than flat architectures.

	%

	\subsection{Combination of arm and vocal movements}

		\paragraph{}
		Fig. \ref{explo_armdiva} shows the exploration in the multi-modal arm plus vocal synthesizer environment.
		Results show that the hierarchical Simplest First architecture explores better than the flat architectures, 
		either with goal babbling or SAGG-RIAC interest models.
		The motor babbling Simplest First hierarchical architecture explores less than flat architectures.

		\begin{figure}[H]
			\centering
			\subfloat[]{\includegraphics[height=3in]{./include/explo-2015-05-30_16-11-48-Test-Arm-Seq-GB.png}}\\
			\subfloat[]{\includegraphics[height=3in]{./include/explo-2015-05-30_16-11-48-Test-Arm-Seq-Tr.png}}
			\caption{Exploration. (a) Goal Babbling versus Motor Babbling. (b) SAGG-RIAC versus Motor Babbling. GB: goal babbling is used to explore models. MB: motor babbling is used. Tr: SAGG-RIAC interest model. F: flat architecture with 1 model. 
					 H: hierarchical architecture with the Simplest First strategy with 3 models. GB-H-TD: GB is used to explore the high model, and TOP-DOWN-RANDOM to guide the 2 lower models. Tr-H-TD: SAGG-RIAC is used to explore the high model, and TOP-DOWN-RANDOM to guide the 2 lower models.
					 Mann-Whitney U tests at the end of the experiments show that the exploration measures in the GB-H and Tr-H conditions
			are significatively greater ($p<0.001$) than in the GB-H-TD condition where it is significatively greater ($p<0.01$) than in the Tr-H-TD condition, 
			where it is significatively greater ($p<0.001$) than in the MB-H condition, 
			where it is significatively greater ($p<0.01$) than in the Tr-F and GB-F conditions, 
			where it is significatively greater ($p<0.001$) than in the MB-F condition.}
			\label{explo_armseq}
		\end{figure}

		\begin{figure}[H]
			\centering
			\includegraphics[height=4in]{./include/explo-2015-05-27_11-51-43-ARM-DIVA.png}
			\caption{Exploration in the multi-modal environment. GB: goal babbling is used to explore models. MB: motor babbling is used. Tr: SAGG-RIAC interest model. F: flat architecture with 1 model. 
			H: hierarchical architecture with the Simplest First strategy with 3 models.					 
			Mann-Whitney U tests at the end of the experiments show that the exploration measures in the Tr-H and GB-H conditions
			are significatively greater ($p<0.05$) than in the GB-F and Tr-F conditions,
			where it is significatively greater ($p<0.01$) than in the MB-H condition,
			where it is significatively greater ($p<0.001$) than in the MB-F condition.
					 }
			\label{explo_armdiva}
		\end{figure}

	%

%

\section{Discussion}

	\paragraph{}
	The hierarchical architectures composed of 2 models tested in the V-rep simulator show equivalent exploration results but better competent exploration than flat architectures.
	%This might first be due to the fact that in this case, the hierarchy does not help that much because it just allows the expression of the movement in 
	%an intermediate representation (the 9D projection of the hand movement) and is used only by one higher model. 
	%The picture should be different if several models were using the same intermediate learned representation.
	%Also, the benefits of an intermediate low dimensional hand movement space $S_h$ might not outweigh the downside of a too simple representation of the 
	%movement by the projection on sensory DMPs.

	\paragraph{}
	The results on the environment composed of a sequence of 2 simple arm commands and the multi-modal environment with an arm and a vocal synthesizer
	show that our exploration architectures get more useful as the hierarchy of sensorimotor models gets more complex.

	\paragraph{}
	The development of a parallel combination operator that allows to run different actions at the same time is not straightforward as a motor could receive two commands at the same time. 
	In that case,  a first idea is to randomly choose one of the commands.
	An interesting approach could make use of Probabilistic Movement Primitives \cite{paraschos2013probabilistic} that represent distributions of probabilities of movements on the different articulators.
	PMPs are shown to handle easily sequence and parallel combinations of movements as operations on distributions of probabilities, for instance the product of probability distributions for the parallel operator.
	%\paragraph{}%Stochasticité
	%In unstable environments,

	\paragraph{}
	In the architectures developed (e.g. Section \ref{sec:increasing}), the sensori spaces represent environmental states that are received as input to the agent at the end of the executed actions.
	%Thus if several actions are combined in sequence, e.g. an action of model $mod_4$ in Fig. \ref{exemple} as a sequence $O_2(S_1, S_2)$ of an action of $mod_1$ and then an 
	%action of $mod_2$, the sensori state $s_1$ received by $mod_1$ could have been modified by the second action, leading to a wrong update of $mod_1$.
	In order to handle environments with hidden states, where sequences of actions have combinatorial effects, it should be beneficial to take the context of the action into 
	account, thus having contextual sensorimotor models relating an action $A$ in a sensori context $S$ to the next sensori state $S'$.
	The dimensionalities would then be much higher, which might require dimensionality reduction techniques.

	%

%

%\section*{Acknowledgment}

	%\paragraph{}
	%First of all I wish to express my sincere thanks to Pierre-Yves Oudeyer for his scientific guidance and his encouragements during this internship.
	%I am scientifically and personally pleased to be going to continue to work under his supervision for the more complex PhD task.
	%I would like to thank Jonathan Grizou and Fabien Benureau who gave me valuable advices and useful references.
	%I am also grateful to Pierre Rouanet who so kindly assisted me for all the technical questions.
	%Finally, I am grateful to William Schueller who gave me useful comments on previous versions of this manuscript and saved me crucial time.

%

%\newpage

	%

\section{Graph implementation}

	I'm trying to implement a first version of a graph representation of multiple hierarchies' learning.
	Before that, I have to be sure about the behavior of the SAGG-RIAC algorithm and its parameters 
	as it will be used as a sub-component in the multi-level graph representation.

	\subsection{SAGG-RIAC}

		Here I want to study the important parameters of the SAGG-RIAC implementation 
		(from Explauto, with my implementation of RIAC in explauto.interest\_model.tree) and test them first on very simple environments.
		The goal is to get a sound progress output, that could be compared with other models' progresses.

		\paragraph{Parameters}
		\begin{itemize}
			\item sensorimotor model (KNN -default-, WNN, LWLR)
			\item exploration noise (gaussian noise amplitude -default $1/30$-)
			\item competence measure ($-distance$ or $exp(-distance)$, distance min -default=0.01-)
			\item progress measure (initial progress value, progress time-scale)
			\item leaf sampling mode (greedy, eps-greedy, softmax -default-), weighting by volume, no multi-scale sampling here
			\item constaints on tree: depth -default=6-, max number of points per region -default=100-
			\item split mode (middle -default-, median, best interest difference)

		\end{itemize}

		\paragraph{Questions}
		\begin{itemize}

			\item how does the progress measure evolve for very simple forward models ? (constant, piece-wise, linear, random)
			\item does progress change when split occurs ? (weighting by volume ?)

		\end{itemize}

		\paragraph{First Tests}
		\begin{itemize}

			\item \textbf{Constant forward model}. We have one motor dimension $m \in [0,1]$ and one sensory dimension always equal to $0~(\in [0,1])$.
				With default RIAC settings, the progress measure does not converge to 0, even if the distance min of the competence measure is not 0 (typically 0.01, which means that if the competence is better than 0.01 in the region, that region will become non-interesting).
				The reason seems to be that given a region not containing $0$ (e.g. $s \in [0.5-0.75]$), all the drawn goals will have a low competence 
				but varying between the competence of distances $0.5$ to $0.75$, with no amelioration with time.
				One idea to fix this problem is to set a maximum goal-to-reached distance (e.g. the size of the region) corresponding to a minimum competence, which will be the always obtained competence in our example, with no fluctuating progress.
				This idea works in this example, and is beneficial for the same reasons in the case of a \textbf{Random forward model}.
				However, in the case of a non-stationary forward model, a new kinematics too far from the learned one might not be computed as interesting (it might be at the beginning due to the time window).
				EDIT: That does not prevent adaptation to new forward models (See Fig. \ref{kmeans}).

			\item \textbf{Linear forward model}. We have one motor dimension $m \in [0,1]$ and one sensory dimension  $s = m$.
				The progress fluctuates between $0.1$ and $1$ for some hundreds iterations (learning phase) and then fluctuates at very low values ($10^{-2~to~-5}$)
				(stochastic changes).
				Setting a minimal distance in the competence measure (e.g. $0.01$) makes the progress go to stricly $0$ instead.

			\item Does progress change when split occurs ? 
				In order to have progress outputs comparable as possible between learning modules, 
				we should have a progress value that depends only on the new incoming data and not on a change in data representation.
				In the SAGG-RIAC algorithm, a split is decided when a region has too much points ($>100$ here).
				The progress of the 2 sub-regions is then recomputed with the competences of the 2 sub-sets of the points, separately.
				Assuming that the 2 sub-regions and the parent one have similar progresses, we have now 2 leaves with the same progress.
				In the sampling process, when we choose the leaf from which to sample a point with a softmax function applied to the interests, then 
				the 2 leaves will weigh 2 times more than the parent one, while representing the same region. 
				It might be interesting to explore more in splitted regions that need resampling, but that leads to a focuse on such regions that will thus be resplitted and so on, with too deep trees. I thus included a possibility to weight the interest of regions by their volume, which allow
				a more stable sampling process.

		\end{itemize}

	%

	\subsection{Hierarchical exploration}

		I implemented the hierarchical exploration of models with a model-first sampling (instead of a hierarchy-first).
		That mean I consider all the models to learn, see their learning progress, and sample one model with high progress 
		(with a softmax of relatively low temperature -$0.5$-). 
		Then that model goal babbles, chooses a motor configuration to try (add random noise), which can be in the sensory space of a lower-model level, 
		and execute the motor command (if no lower-level dependency) or give that goal to lower-level models to be executed now (with no exploration iterations budget, but allowing motor noise in lower-level models).
		A motor command $m$ is finally executed, and a sensory input $s$ observed.
		Each model is then updated with the dimensions of $ms$ it is concerned with, which can be different from what it asked to lower-level models.
		I also implemented the possibility to add an exploration budget around the top-down guided point, but I don't use it here as results are not clear.

		\paragraph{Parameters}
		\begin{itemize}
			\item model sampling (greedy, softmax -default-)
			\item sampling models (-default-) or first sampling the hierarchy to train (root of the DAG) and then the model in the hierarchy.
			\item add top-down guided exploration budget
		\end{itemize}

		\paragraph{Questions}
		\begin{itemize}

			\item In a simple hierarchy, do we see expected exploration behaviors ? e.g. if a model is harder to learn, is it babbling more often ?
					If a model is reusing another one, does a learning schedule autonomously emerge with the higher-level model explored significantly after ?
			\item For non-stationary forward models, the sensorimotor model does not forget old points. Should we weight also by time ?

		\end{itemize}

		\paragraph{First Tests}~\\
		I use here identity function as forward models.
		There are 2 low-level models (mod1 and mod2) and one higher level that only rely upon mod1.
		Thus $s1=m1, s2=m2, s3=s1$.
		In a second condition, the forward model of mod3 is changed at 5000 iterations with $s3=s1^2$.

		\begin{figure}[H]
			\centering
			\includegraphics[width=8cm]{./include/Test_DAG_3mods_f=id-_1000.png}
			\includegraphics[width=8cm]{./include/Test_DAG_3mods_f=id_change_500-_1000.png}
			\caption{Exploration }
		\end{figure}

		\paragraph{Remarks}
		\begin{itemize}
			\item In the first condition, the 3 modules learn quickly their function, and then alternate. 
					In tests with more complex functions including random noise, the results are less clear (depend on max distance).
			\item In the second condition, at 5000, the 3rd module is seeing an increase in its progress but is not learning the change in its forward model.
					This is due to the problem described before, of non forgetting old sensorimotor points.
			\item In tests with a more complex hierarchy (7 models with some of them reusing several others), and a change in a given forward model, the results are similar.
			\item The progress or interest of a SAGG-RIAC tree is here computed as the progress on the last k (here $k=10$) babbling points on the overall tree, taking the points of all leaves into account (default).
					Another way to compute the progress is to get the maximum of the progress of each leaf. This does not change qualitatively the results.
		\end{itemize}

	%

	\subsection{More on Non-Stationary Forward Models}
	\label{NSLWLR}

		\paragraph{}
		To cope with non-stationary forward models, with have to somehow forget old points and consider more the newest ones.
		The linear regression in LWLR is weighted by the distance of the points in the dataset. We can also weight them according to their timestamps (iterations at which the points were added).
		Given $x$, we want to compute $f(x)$, using data points $\{x_i, y_i\}$.
		First idea: we compute the weights of the Locally-Weighted Linear Regression with:

		$$ w_i = K_g(dist(x_i, x), \sigma^2) * ((iteration(i) - min\_iteration +1)/max\_iteration)^2$$
		where $K_g$ is a gaussian kernel with $\sigma = 0.05$.

		The results (Fig. \ref{NS1}) do not show a stabilization of the progress towards $0$ after the change in forward model at iteration $500$ for module $3$.

		\begin{figure}[H]
			\centering
			\includegraphics[width=8cm]{./include/NSLWLR-k=05.png}
			\includegraphics[width=8cm]{./include/NSLWLR-k=20.png}
			\caption{Progress of the 3 modules. The weights of the LWLR regression are weight with iterations' timestamps. Left: k=5 points used in regression, Right: k=20 points. Progress is measured as the max of the progress of each leaf.}
			\label{NS1}
		\end{figure}

		\paragraph{}
		Second idea: we use a gaussian kernel also for time weighting (see Fig. \ref{gt}, left).
		$$ w_i = K_g(dist(x_i, x), \sigma^2) * K_g(current\_iteration - iteration(i),~\sigma_t^2)$$
		with $\sigma_t = 100$ iterations.

		The result is shown in Fig. \ref{gt} left.
		That was neither a fast adaptation so I closer looked into the progress depending on the leaves. 
		I saw that the non-zero progress was due to the initial guess point of the inverse optimization (with algo L-BFGS-B) that was set as the $x$ corresponding to the nearest neighbor of the goal $y_g$ in the dataset.
		After the change in forward model, the guess point is often corresponding to the old forward model, and the optimization starting with that points is often failing, returning uncertain or 0 values giving a not real progress to the leaf.
		I changed the number of initial guess points (goal's nearest neighbors) to try with inverse optimization to $k=10$ (Fig. \ref{gt} right).
		Now, if points corresponding to the new forward model do exist near the goal, they are tested and optimization fail much seldom.
		However, the computation time gets too long.

		\begin{figure}[H]
			\centering
			\includegraphics[width=8cm]{./include/NSLWLR-opt_k-initial=1.png}
			\includegraphics[width=8cm]{./include/NSLWLR-opt_k-initial=10.png}
			\caption{Progress of the 3 modules. The weights of the LWLR regression are weight with a gaussian time kernel. Left: 1 point is used as initial guess. Right: 10 points are used. Progress is measured as the progress on the last points of the global tree.}
			\label{gt}
		\end{figure}

		\paragraph{}
		An idea is to try only different points (ideally one old point and one new point) from the dataset as initial guess to the inverse optimization.
		I did that with a k-means clustering of the $50$ nearest neighbors of the goal in the dataset, to get 2 clusters. The inverse optimization is feeded with the 2 clusters' centroids as initial guess.
		The results (Fig. \ref{kmeans}) show the same adaptation as the $k=10$ guess points (Fig. \ref{gt} right) but is much faster.

		\begin{figure}[H]
			\centering
			\includegraphics[width=8cm]{./include/NSLWLR-kmeans2-k=50_max_prog.png}
			\includegraphics[width=8cm]{./include/NSLWLR-kmeans2-k=50_all_prog.png}
			\caption{K-means clustering of 50 initial guesses in 2 clusters to try inverse optimization. Left: Progress is measured as the progress on the last points of the global tree. Right: Progress is measured as the max of the progress of each leaf.}
			\label{kmeans}
		\end{figure}

		There is still some noise due to BFGS failed optimizations that sometimes sticks to the domain bounds, which gives competence noise in the SAGG-RIAC tree's lowest leaf (e.g. with bounds [0-0.125] -tree max depth is $3$ here).
		The adaptation is satisfying, given that the time kernel size is of $100$ iterations. In Fig. \ref{gt20}, the gaussian time kernel has size $20$ iterations, and different forward model's transitions are tested.
		The transition from a harder to a simpler forward model seems to need longer adaptation, but it might not be significant.

		\begin{figure}[H]
			\centering
			\includegraphics[width=8cm]{./include/NSLWLR_gt20_hard-easy.png}
			\includegraphics[width=8cm]{./include/NSLWLR_gt20_easy-hard.png}
			\caption{Progress on the 3 modules. LWLR weighted with a gaussian time kernel of size $20$ iterations. Left: forward model of module $3$ moves from $x\rightarrow x^2$ to $x\rightarrow x$.
			Right: forward model of module $3$ moves from $x\rightarrow x$ to $x\rightarrow x^2$.}
			\label{gt20}
		\end{figure}

		When one module see a change in its forward model, all the models that reuse it will not have their sensorimotor model modified, but will have their interest model perturbated.
		For instance, let's say module $1$ learns the mapping from $m_1$ to $s_1$ and becomes wrong, and module $2$ learns a mapping from $s_1$ to $s_2$ and reuses module $1$.
		Then when module $2$ is babbling, it wants to produce $s_2$ so infers a $s_1$ to try, and feeds it to module $1$ that fails at producing $s_1$ but produces instead $s'_1$ that leads to $s'_2$ far from $s_2$. 
		Thus both modules see a decrease in competence and thus an increase in interest.

		\paragraph{}
		As all models reusing the perturbated one gets a perturbated interest (interest that do not actually correspond to a change in the competence of the model's mapping), thus a lot of exploration iterations might be wasted
		on those models while they do not necessarily need training.
		With 4 models in a linear hierarchy where model $i+1$ reuses model $i$, Fig. \ref{f10} left shows the results after a change in the forward model of module $1$ at iteration $200$.
		Indeed, the $4$ modules have a non-zero interest and are sampled, from iterations $200$ to $300$, whereas only module $1$ needs sampling.
		An idea to avoid this waste of exploration is to weight the interest of each module (before a softmax choice) depending on the level of modules in the hierarchy.
		I used the following weights in Fig. \ref{f10} right:

		$$ w_{mod_i} = p_i * f^{max\_level - level(i)}$$

		where $p_i$ is the progress of module $i$, $f$ a power factor, $level(i)$ is the level of module $i$ in the hierarchy: from $0$ for module $1$ to $3$ for module $4$.

		We can see in Fig. \ref{f10} right that even if modules $3$ and $4$ have sampled a few points between iterations $225$ and $400$, most of the babbling is done by module $1$ that corrects its own sensorimotor model.
		This idea to first train on more basic skills seems ecological and can be applied to more complex hierarchies, and can also be combined with other mechanisms to choose modules to train.

		\begin{figure}[H]
			\centering
			\includegraphics[width=8cm]{./include/NSLWLR-f=0.png}
			\includegraphics[width=8cm]{./include/NSLWLR-f=10.png}
			\caption{Progress on the 4 modules of a linear hierarchy. Left: $f=0$. Right: $f=10$.}
			\label{f10}
		\end{figure}

	\subsection{Creation of modules/tasks}

		\paragraph{}
		Here we allow the creation of modules when all the progresses of current modules are below a threshold (e.g. 1e-2).

		\paragraph{Module creation}
		An operator is randomly chosen among the concurrence and sequence operators.
		Then, 2 input connexions are chosen among the output of other modules plus primitive motor spaces.
		A sensory space is randomly chosen as a subset of all possible sensory spaces.
		In case of the concurrence operator, there are constraints on the input and output spaces: that the 2 input's set of controled variables must have a void intersection, 
		and that the motor spaces can't be in the sensory spaces.
		We could remove the constraints and let the agent understand that this module might be useless, but it could be a waste of iterations.

		\paragraph{}
		In the following experiments (see Fig. \ref{pc}), we use the previous linear hierarchy as initial models (from module 1 to module 4), and we use the constraints above for the concurrence operator.
		As we have only one motor space, the concurrence operator constraints can't be fulfilled, so the sequence operator only will be chosen.

		\begin{figure}[H]
			\centering
			\includegraphics[width=8cm]{./include/autocreate_progresses.png}
			\includegraphics[width=8cm]{./include/autocreate_competences.png}
			\caption{Left: Progress of modules. Right: IM Competence of modules: competence to reach self-generated goals, which depends on the sensorimotor competences of involved modules.}
			\label{pc}
		\end{figure}

	%

	\subsection{More on Top-Down Drive}
	\label{tddkdtree}
		\paragraph{}
		The idea of Top-Down Drive is that higher modules in the hieararchy have relevant information about the utility of the exploration of the different regions of the common representation space.
		Different ideas might allow to take this information into account.
		In the experiments with the V-rep arm pushing a block (\ref{result:tdd}), I suggested 2 possibilities (See Section \ref{sec:interacting}).
		One is that each module asked to reach a goal, explores with a small budget of experiments around that goal before infering a motor command to reach that goal.
		A problem with that approach is that in a complex hierarchy, it would take to much time to infer a motor command for a goal containing a lot of nested sub-goals, 
		furthermore as each module could receive multiple goals.
		The second approach, not implemented was thus to feedback a top-down interest model in the common space to lower models that will have to balance 
		the self-computed interest map with Top-Down interest map (and even social interest map).
		The drawback now is that a lot of maps represented for instance with GMMs have to be handled, recomputed, multiplicated and sampled.

		\paragraph{}
		An other approach in-between would be to store, for each module, all the goals that have been asked from higher models in a specific KDTree 
		(different from the SM model that contains all points, and from IM model that contains the self-generated points).
		The information of interest to explore a point would be retrieved as the density of points in the kdtree around the given point.
		This could be computed with sklearn.neighbors.KDTree.kernel\_density that takes the bandwidth of a gaussian kernel as input.

		In order to balance self-computed interest with Top-Down interest, we could include the Top-Down information into the softmax choice of a leaf of the interest model's tree (in SAGG-RIAC) to explore.
		Up to now, the weights of the leaves are the competence progress on the points of each leaf.
		The idea is to also weight the interest of the leaves by the density of the Top-Down points around the center of each leaf.
		The bandwidth of the gaussian kernel could be proportional to the leaf's size as that is the relevant scale to smooth density information.

		In the case where we do not use SAGG-RIAC but SAGG-Random, instead of sampling random goals, we could directly sample the density map (implemented in sklearn) most of the time, and randomly sample sometime.

	%

%

\section{Summary}

	\paragraph{}%Résumé
	We have implemented and tested some of the described hierarchical exploration architectures in different environments (See Table \ref{recap}).

	\begin{table}[H]
		\centering
		\begin{tabular}{|l|l|l|c|}
		\hline
		\multicolumn{1}{|c|}{{\bf Problem}}                                                                  & \multicolumn{1}{c|}{{\bf Algorithm}}                                                        & \multicolumn{1}{c|}{{\bf Specificities}} & {\bf Implem. ?}   \\ \hline
		\multirow{4}{*}{\begin{tabular}[c]{@{}l@{}}Exploring autonomously \\ a fixed hierarchy\end{tabular}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Exploring models \\ in a hierarchy\end{tabular}} & Fixed learning cv                        & Yes                 \\ \cline{3-4} 
																											 &                                                                                             & Dynamic learning cv                      & Yes                 \\ \cline{2-4} 
																											 & \multirow{2}{*}{Top-Down Drive}                                                             & \begin{tabular}[c]{@{}l@{}}Models used by \\ max 1 model\end{tabular}               & Yes                 \\ \cline{3-4} 
																											 &                                                                                             & Other hierarchies                  & No                  \\ \hline
		\begin{tabular}[c]{@{}l@{}}Exploring tasks of \\increasing complexity\end{tabular}                                                                      & Creating modules   & Given M, S, O                            & Some                  \\ \hline
		\multicolumn{1}{|c|}{\multirow{3}{*}{Learning with Social Guidance}}                                 & \multirow{3}{*}{\begin{tabular}[c]{@{}l@{}}Integration of \\ Social Guidance\end{tabular}}  & Task-space level                         & \multirow{3}{*}{No} \\ \cline{3-3}
		\multicolumn{1}{|c|}{}                                                                               &                                                                                             & Model level                              &                     \\ \cline{3-3}
		\multicolumn{1}{|c|}{}                                                                               &                                                                                             & Hierarchy level                          &                     \\ \hline
		\end{tabular}
		\caption{Summary of developed algorithms}
		\label{recap}
	\end{table}

%

\section{Roadmap}

	%\paragraph{}%Missing Results = next steps	
	%In the learning algorithms tested, the hierarchy of models to learn is given to the agent as if it already knew the combinations of actions
	%to explore in order to learn the successive tasks.
	%This is a strong hypothesis as infants have first to discover what types of actions to combine to get a specific outcome.
	%The next step of this work is the implementation of the algorithm described in Section \ref{sec:increasing} that autonomously learns to progressively complexify 
	%the hierarchy of sensorimotor models.
	%Also, sensori contexts in models might simplify the use of sequencial actions and the design of sensori spaces.

	\paragraph{}%Future Studies
	The next important steps are to properly formulate, analyze and illustrate the different questions of this report, first in abstract settings before real experimental setups.
	The first question is how to explore a given, fixed hierarchy of tasks, and how the different algorithms behave (Section \ref{study1}).
	In those algorithms, the hierarchy of models to learn is given to the agent as if it already knew the combinations of actions to explore in order to learn the successive tasks.
	This is a strong hypothesis as infants have first to discover what types of actions to combine to get a specific outcome.	
	The second question is thus how and when to autonomously combine the previously learned actions in a relevant hierarchy of skills (Section \ref{study2}).	
	Then, we will study the integration of social guidance into those algorithms (Section \ref{study3}).

	\paragraph{}%Future Work:
	In future work, we also plan to make an experiment in which a robot has to autonomously 
	discover that sounds can influence a social peer (for example making him
	manipulate objects in the environment), using the extensions of our hierarchical exploration architectures that integrate social interaction (Section \ref{sec:social}). 
	Experiments will be conducted both through simulation of robotic environments and real robot
	experiments, in particular using the open-source humanoid platform Poppy.
	Then, we will work to allow for
	hierarchical reinforcement learning techniques in the model \cite{botvinick2012hierarchical}, in particular option
	theory \cite{sutton1999between}). 
	Also, we will study how techniques
	of multi-modal deep learning \cite{ngiam2011multimodal} can be used to select useful manifold in high-dimensional sensorimotor flows 
	(i.e. find useful lower dimensional abstractions of the flows) on which
	skill acquisition techniques can be applied.

%

\newpage

\section{Study 1: Exploration of a given hierarchy of skills}
\label{study1}

	\subsection{Motivation}

		Explain related work: \cite{vig, ugur2014, ugur2015}.

	%

	\subsection{Methods}

		\subsubsection{Algorithms}

			\paragraph{}
			Different possibilities to handle exploration in the hierarchy:
			\begin{itemize}
				\item MAB on all modules (implemented: greedy, softmax),
				\item MAB biaised on lower modules (implemented),
				\item ZPDES (to check with Benjamin).
			\end{itemize}

			\paragraph{}
			Different types of Top-Down Drive:
			\begin{itemize}
				\item Nothing,
				\item Exploration budget around goals asked by higher models,
				\item Balance self-computed interest with Top-Down interest (See Section \ref{tddkdtree}).
			\end{itemize}

			\paragraph{}
			Different types of Sensorimotor models:
			\begin{itemize}
				\item NN,
				\item LLWR,
				\item NSLWLR to handle non stationary forward models (See Section \ref{NSLWLR}).
			\end{itemize}

			\paragraph{}
			Different module implementations (implemented):
			\begin{itemize}
				\item Motor Babbling,
				\item SAGG-Random,
				\item SAGG-RIAC.
			\end{itemize}

		%

		\subsubsection{Environment}

			\paragraph{}
			Abstract environment with forward models defined by mathematical functions. 
			It should be interesting to use some sort of benchmark to control the complexity of functions.

			\paragraph{}
			Different variables to test:
			\begin{itemize}
				\item Motor and Sensory dimensionalities,
				\item Complexity of hierarchies (with a measure of it),
				\item Perturbations of forward models at different hierarchy levels.
			\end{itemize}

		%

		\subsubsection{Measures}

			\begin{itemize}
				\item Exploration of each module,
				\item Exploration of top spaces,
				\item Competence of each sensorimotor model,
				\item Competence and Progress in each Interest Model,
				\item Developmental trajectories.
			\end{itemize}

		%

	%

%

\section{Study 2: Curiosity-driven combination of skills}
\label{study2}

%

\section{Study 3: Socially-guided combination of skills}
\label{study3}

%

\bibliographystyle{apalike}
% argument is your BibTeX string definitions and bibliography database(s)
\small
\bibliography{./include/bibliography}

% that's all folks
\end{document}

### 2015-10-02 roadmap/doc.tex
TDD

@@
 	\end{figure}
-
-%\paragraph{Declaration of contribution}
-
-	%\begin{itemize}
-		%\setlength\itemsep{0em}
-		%\item Definition of scientific question: PYO, SF
-		%\item Bibliographic research: PYO, SF
-		%\item Choice of the general approach to answer the question: PYO, SF
-		%\item Choice of methods: PYO, SF
-		%\item Methods development, programming: SF
-		%\item Data analysis: SF
-		%\item Results interpretation: PYO, SF
-		%\item Dissertation writing: SF
-		%\item Dissertation review and comments: PYO
-	%\end{itemize}
-
-%
 
@@
 	\label{tddkdtree}
+
 		\paragraph{}
@@
 
-		\paragraph{}
+		\paragraph{Weighting by the density of Top-Down goals.}
 		An other approach in-between would be to store, for each module, all the goals that have been asked from higher models in a specific KDTree 
@@
 		In the case where we do not use SAGG-RIAC but SAGG-Random, instead of sampling random goals, we could directly sample the density map (implemented in sklearn) most of the time, and randomly sample sometime.
+
+		\paragraph{Taking into account the information of the error between desired and actual motor command.}
+		With the previous algorithm based on the density on Top-Down asked goals, there still exists information not handled but which might be useful.
+		Indeed, when a module asks for a desired motor command $m_d$, if lower modules do not reach that goal but a $m_r$ potentially far from $m_d$, 
+		then the distance $e_m = ||m_r - m_d||$ represents the error of lower models and might be useful to drive their exploration.
+		The density idea already uses the information of the point $m_d$, but not the associated $e_m$ which could lead to a quantity of progress if derived.
+		This learning progress is exactly the learning progress computed in a leaf of the interest model of lower modules, but there it is updated only when that sub-module has babbled, 
+		not when a higher module has asked for a goal.
+If we were to update also the interest models when modules have not babbled, I guess that would mess up the competence derivative computation, leading to wrong estimates.
+		So I don't know if we can use this supplementary information.
+
+		\paragraph{Taking into account the progress in the leaf of the remote module that has been babbled.}
+		In the density algorithm above, when a higher module has asked for a goal $s_g$, that point is added to the density map of Top-Down goals, 
+		saying that this point is an interesting location to further explore around.
+		But overall, some of those asked goals will lead to a progress in a leaf of the remote module that has babbled, and some of them will not.
+		Thus it might be useful to use that information to add or remove interest in the given region of the map of Top-Down goals depending on the progress that has been remotely elicited.
+		To this purpose, we could inspire from the framework of RL and particularly the $TD(\lambda)$ algorithm that makes use of eligibility traces that stores the influence of each state on the future reward.
+		We could see the progress computed in the leaf that has babbled as a reward which will be added to the Top-Down interest of the leaves that have been used in the given command 
+		(with accumulating or replacing eligibility traces).
+
+		This idea is also inspired by the RiARiT algorithm that stores a table of competence levels required by each activity on each knowledge component.
+		Each knowledge component thus knows the influence it has on each activity.
+		In our setting, knowledge components are themselves activities, and that table would be estimated on-the-fly and at the leaf scale.
+
+		The implementation would use the mean of (possibly time-decaying) rewards in each leaf as a weight to be balanced with self-computed leaves' interests before a leaf softmax choice.
 

### 2015-10-07 roadmap/doc.tex
module choices

@@
 	\subsection{SAGG-RIAC}
-
+	\label{sec:saggriac}
 		Here I want to study the important parameters of the SAGG-RIAC implementation 
@@
 		The implementation would use the mean of (possibly time-decaying) rewards in each leaf as a weight to be balanced with self-computed leaves' interests before a leaf softmax choice.
+
+	%
+
+	\subsection{Implementation of multiple options to explore a given sensori space}
+	\label{choices}
+
+		\paragraph{}
+		I have implemented the possibility to have different modules that learn a mapping towards the same sensori space.
+		A higher module that uses that space as a motor space will choose which lower module to use to explore a point in that space with the goal to maximize the competence around that point.
+		I have tested that idea using SAGG-Random modules instead of SAGG-RIAC ones.
+		I compute the progresses (to choose the module that will babble) as the derivative of the competence of last goal babbled points.
+		The competence around a point (to choose the module that will reach the goal with the maximum precision) is computed as the mean of the competences of the $k=20$ nearest neighbors.
+
+		\paragraph{}
+		The hierarchy used is the following: mod1 learns from $m1$ to $s1$, mod2 learns from $m2$ to $s1$, and mod3 learns from $s1$ to $s2$.
+		Mod3 can thus reuse either mod1 or mod2. All spaces are 1-dimensional with range $[0-1]$. Here are the forward models:
+
+		$$s1 = \frac{2*m1 + m2}{3}$$
+		$$s2 = s1^2$$
+
+		Thus, if mod3 reuses mod1, it will reach a wider range of outputs than with mod2. Fig. \ref{fchoices} shows the results of 2000 iterations with this setup.
+		Mod3 quickly (100 iterations) gets to use mod1 (around 90\% of babbling iterations) instead of mod2.
+		In the computation of competences, I also cut the competences to a minimal competence value (or maximal error distance of $0.1$) in order to avoid big random fluctuations of interest (absolute value of progress)
+		when a module wants to explore a far unreachable point, which entails a very high interest (see Sec. \ref{sec:saggriac}).
+
+		\begin{figure}[H]
+			\centering
+			\includegraphics[width=8cm]{./include/choice_test_choices.png}
+			\includegraphics[width=8cm]{./include/choice_test_competences.png}
+			%\includegraphics[width=8cm]{./include/choice_test_progresses.png}
+			\caption{Progress on the 3 modules of a hierarchy with 2 choices of sub-modules for module 3.
+Left: Proportion of choices of module 3 (with a sliding window).
+Right: Competences (with a sliding window) babbled points of each modules.}
+			\label{fchoices}
+		\end{figure}
 

### 2015-10-08 roadmap/doc.tex
different hierarchies
experiments

@@
 
-	\subsection{Motivation}
+	\subsection{Introduction}
 
 		Explain related work: \cite{vig, ugur2014, ugur2015}.
+
+	%
+
+	\subsection{Questions}
+
+		\begin{itemize}
+			\item Exploring in a structured hierarchy is more efficient than directly from $M$ to $S$.
+			\item Which task should I explore now ?
+			\item How to choose between different means to explore a given space ? 
+			\item How can high-level tasks guide the exploration of lower-level ones ?
+			\item How can the system cope with perturbations on some of the forward models ?		
+		\end{itemize}
 
@@
 
+		\subsubsection{Hierarchies}
+
+			\begin{figure}[H] 
+				\subfloat[]{\input{include/H1.tikz}}
+				\subfloat[]{\input{include/H2.tikz}}
+				\subfloat[]{\input{include/H3.tikz}}
+				\subfloat[]{\input{include/H4.tikz}}
+				\caption{Exemple of hierarchies.}
+				\label{H}					
+			\end{figure}
+		%
+
 		\subsubsection{Environment}
-
-			\paragraph{}
-			Abstract environment with forward models defined by mathematical functions. 
-			It should be interesting to use some sort of benchmark to control the complexity of functions.
 
@@
 				\item Motor and Sensory dimensionalities,
-				\item Complexity of hierarchies (with a measure of it),
-				\item Perturbations of forward models at different hierarchy levels.
+				\item Type of functions: linear, cosine, geometric arm, non-continuous interaction with objects.
+				\item Noise
 			\end{itemize}
@@
 
+		\subsubsection{Experiments}
+
+				\paragraph{Experiment 1: Exploring in a structured hierarchy is more efficient than directly from $M$ to $S$.}
+				\paragraph{}
+				The idea is to compare our simplest algorithm (explore the module with higher progress) in a realistic setting (Hierarchy (a) of Fig.
+\ref{H}) to the control condition where a sensorimotor model is learned
+				directly from the whole motor space $M$ to the whole sensori space $S$.
+
+				\paragraph{Experiment 2: Which task should I explore now ?}
+				\paragraph{}
+				Here we compare the different possibilities to choose the module to explore in the hierarchy: maximizing the progress, maximizing with a bias towards lower-level modules, or use ZPDES,
+				with the same hierarchy (a) of Fig. \ref{H}.
+
+				\paragraph{Experiment 3: How to choose between different means to explore a given space ?}
+				\paragraph{}
+				Here we explain that we can choose between different means (e.g. different tools) using the one with the maximal competence.
+				We can use the hierarchy (b) of Fig. \ref{H}.
+
+				\paragraph{Experiment 4: How can high-level tasks guide the exploration of lower-level ones ?}
+				\paragraph{}
+				We compare different possibilities of Top-Down Guidance, 
+				with hierarchy (c) of Fig. \ref{H}.
+
+				\paragraph{Experiment 5: How can the system cope with perturbations on some of the forward models ?}
+				\paragraph{}
+				We apply perturbations to one of the possible forward models, either blocking, shifting or randomizing one dimension. 
+				We can use the hierarchy (d) of Fig. \ref{H}.
+
+		%
 		\subsubsection{Measures}

### 2015-10-09 roadmap/doc.tex
experiments

@@
 Left: Proportion of choices of module 3 (with a sliding window).
-Right: Competences (with a sliding window) babbled points of each modules.}
+Right: Competences (with a sliding window) of babbled points of each modules.}
 			\label{fchoices}
@@
 			\paragraph{}
+			Different module implementations (implemented):
+			\begin{itemize}
+				\item Motor Babbling,
+				\item SAGG-Random.
+			\end{itemize}
+
+			\paragraph{}
+			Different types of Sensorimotor models (implemented):
+			\begin{itemize}
+				\item NN or LWLR,
+				\item NSLWLR to handle non stationary forward models (See Section \ref{NSLWLR}), or NSNN as NN plus a weighting by time.
+			\end{itemize}
+
+			\paragraph{}
 			Different possibilities to handle exploration in the hierarchy:
@@
 			\begin{itemize}
-				\item Nothing,
-				\item Exploration budget around goals asked by higher models,
-				\item Balance self-computed interest with Top-Down interest (See Section \ref{tddkdtree}).
-			\end{itemize}
-
-			\paragraph{}
-			Different types of Sensorimotor models:
-			\begin{itemize}
-				\item NN,
-				\item LLWR,
-				\item NSLWLR to handle non stationary forward models (See Section \ref{NSLWLR}).
-			\end{itemize}
-
-			\paragraph{}
-			Different module implementations (implemented):
-			\begin{itemize}
-				\item Motor Babbling,
-				\item SAGG-Random,
-				\item SAGG-RIAC.
+				\item Just add noise to motor command of each module (pb: interferes with competence and progress estimation)  (implemented),
+				\item Exploration budget around goals asked by higher models (explonential in $levels^{n+1}$ so even $n=1$ is not feasible in general but maybe in practice)  (implemented),
+				\item Exploration budget only for the modules one layer below the babbling module (not implemented).
+				\item Balance self-computed interest with Top-Down interest (See Section \ref{tddkdtree}, not implemented).
 			\end{itemize}
@@
 			\paragraph{}
-			Different variables to test:
+			Different variables to test: motor and sensory dimensionalities, type of functions (linear, cosine, geometric arm, non-continuous interaction with objects), noise.
+
+			\paragraph{Possible arm models:}
 			\begin{itemize}
-				\item Motor and Sensory dimensionalities,
-				\item Type of functions: linear, cosine, geometric arm, non-continuous interaction with objects.
-				\item Noise
+				\item $n$ DOFs 2D geometric arm
 			\end{itemize}
 
+			\paragraph{Possible tool models:}
+			\begin{itemize}
+				\item static piano
+				\item stick 
+			\end{itemize}
+
+			\paragraph{Possible object models:}
+			\begin{itemize}
+				\item static object with features depending on the piano
+				\item dynamic object
+			\end{itemize}
+
 		%
@@
 
+				% Experiment 1
 				\paragraph{Experiment 1: Exploring in a structured hierarchy is more efficient than directly from $M$ to $S$.}				
-				\paragraph{}
-				The idea is to compare our simplest algorithm (explore the module with higher progress) in a realistic setting (Hierarchy (a) of Fig.
+				\begin{itemize}
+					\item Idea: to compare our simplest algorithm (explore the module with higher progress) in a realistic setting (Hierarchy (a) of Fig.
 \ref{H}) to the control condition where a sensorimotor model is learned
@@
 
+					\item Conditions: Hierarchy (a) vs $M \rightarrow S$, Motor Babbling vs SAGG-Random
+
+					\item Features: MAB on all modules, NN, No TDD.
+
+					\item Measures: exploration of intermediate spaces (hands, tools), exploration of top spaces (objects). Competence to reach random goals in reachable parts of intermediate and top spaces. 
+							Statistics on multiple runs to see regularity/diversity in developmental trajectories.
+				\end{itemize}
+
+				% Experiment 2
 				\paragraph{Experiment 2: Which task should I explore now ?}
-				\paragraph{}
-				Here we compare the different possibilities to choose the module to explore in the hierarchy: maximizing the progress, maximizing with a bias towards lower-level modules, or use ZPDES,
+				\begin{itemize}
+					\item Idea: to compare the different possibilities to choose the module to explore in the hierarchy: maximizing the progress, maximizing with a bias towards lower-level modules, or use ZPDES,
 							with the same hierarchy (a) of Fig. \ref{H}.
 
+					\item Conditions: Random module, MAB on all modules, MAB with bias, ZPDES.
+
+					\item Features: Hierarchy (a), SAGG-Random, NN, No TDD.
+
+					\item Measures: exploration of intermediate spaces (hands, tools), exploration of top spaces (objects). Competence to reach random goals in reachable parts of intermediate and top spaces. 
+							Statistics on multiple runs to see regularity/diversity in developmental trajectories.
+				\end{itemize}
+
+				% Experiment 3
 				\paragraph{Experiment 3: How to choose between different means to explore a given space ?}
-				\paragraph{}
-				Here we explain that we can choose between different means (e.g. different tools) using the one with the maximal competence.
-				We can use the hierarchy (b) of Fig. \ref{H}.
-
+				\begin{itemize}
+					\item Idea: to explain how we can choose between different means (e.g. different tools) using the one with the maximal competence, or maximal progress.
+							We can use the hierarchy (b) of Fig. \ref{H}, in order to have 2 different tools to move the object.
+
+					\item Conditions: maximize competence vs progress, noise on each tool, reachability (e.g. size) of each tool.
+
+					\item Features: Hierarchy (b), MAB on all modules, SAGG-Random, NN, No TDD.
+
+					\item Measures: exploration of intermediate spaces (hand, tools), exploration of top spaces (object). Competence to reach random goals in reachable parts of intermediate and top spaces. 
+							Statistics on multiple runs to see regularity/diversity in developmental trajectories.
+				\end{itemize}
+
+				% Experiment 4
 				\paragraph{Experiment 4: How can high-level tasks guide the exploration of lower-level ones ?}
-				\paragraph{}
-				We compare different possibilities of Top-Down Guidance, 
-				with hierarchy (c) of Fig. \ref{H}.
-
+				\begin{itemize}
+					\item Idea: tocompare different possibilities of Top-Down Guidance, with hierarchy (c) of Fig. \ref{H} in order to have TD guidance at different levels: 
+							arm with one higher model, hand with 2 higher models, tool1 with one higher model, or tool2 with 2 higher models.
+
+					\item Conditions: No TDD, Just add noise to motor command of each module (pb: interferes with competence estimation) 
+							vs explore $n$ points and returns the best (warning: exponential)
+							vs only one layer below the babbling module explores $n$ points.
+
+					\item Features: Hierarchy (c), MAB on all modules with bias (or no bias?), SAGG-Random, NN.
+
+					\item Measures: exploration of intermediate spaces (hands, tools), exploration of top spaces (objects). Competence to reach random goals in reachable parts of intermediate and top spaces. 
+							Statistics on multiple runs to see regularity/diversity in developmental trajectories.
+				\end{itemize}
+
+				% Experiment 5
 				\paragraph{Experiment 5: How can the system cope with perturbations on some of the forward models ?}
-				\paragraph{}
-				We apply perturbations to one of the possible forward models, either blocking, shifting or randomizing one dimension. 
-				We can use the hierarchy (d) of Fig. \ref{H}.
-
-		%
-		\subsubsection{Measures}
-
 				\begin{itemize}
-				\item Exploration of each module,
-				\item Exploration of top spaces,
-				\item Competence of each sensorimotor model,
-				\item Competence and Progress in each Interest Model,
-				\item Developmental trajectories.
+					\item Idea: to apply perturbations to one of the possible forward models, either blocking, shifting or randomizing one dimension. 
+							We can use the hierarchy (d) of Fig.
+\ref{H} in order to see an adaptation at 2 levels: the use of one hand to use one tool, the use of both tools to move the object even if only one is perturbated.
+
+					\item Conditions: No perturbations, which model is perturbated (arm, tool), type of perturbation (blocking, shifting, random).
+
+					\item Features: Hierarchy (d), MAB on all modules, SAGG-Random, NN, best TDD.
+
+					\item Measures: exploration of intermediate spaces (hands, tools) and top spaces (objects) before and after perturbations. 
+							Competence to reach random goals in reachable parts of intermediate and top spaces before and after perturbations. 
+							Statistics on multiple runs to see regularity/diversity in developmental trajectories.
 				\end{itemize}

### 2015-10-09 roadmap/doc.tex
ZPDES

@@
 
+	\subsection{ZPDES}
+	\label{zpdes}
+
+		I've tested Benjamin's code of the ZPDES algorithm \cite{clement2014online} to choose which module to explore at each iterations.
+		The algorithm has mainly 4 parameters:
+		\begin{itemize}
+			\item The rate $\alpha$ of integration of new information about average reward of bandits: $bandit\_value = (1 - \alpha) * old\_bandit\_value + \alpha * reward$. I used $\alpha = 0.5$.
+			\item The activation threshold: if the mean (recent) competence of activated modules exceeds that threshold, then a new module will be activated. I used $0.5$.
+			\item The deactivation threshold: if one module have its mean recent competence exceeding that threshold, it will be deactivated. I used $0.6$ here.
+			\item A window size to compute the means of recent competences and progress: I used $20$ iterations.
+		\end{itemize}
+
+		See Fig. \ref{zpdesfig} for an exemple of execution of ZPDES in my setup. There are 3 modules with the same mathematical functions as forward models as in the previous section.
+		We can see that module 1 gets deactivated early when its mean competence exceeds $0.6$.
+		Module 3 only gets activated when the mean competence of modules 1 and 2 exceeds $0.5$ around $200$ iterations.
+
+		\begin{figure}[H]
+			\centering
+			\includegraphics[width=8cm]{./include/ZPDES_competences.png}
+			\includegraphics[width=8cm]{./include/ZPDES_progresses.png}
+			\caption{Competences and progresses using ZPDES.}
+			\label{zpdesfig}
+		\end{figure}
+
+		\paragraph{Remarks}
+
+		The activation threshold allows to avoid spending useless trials on too complex tasks, provided the algorithm knows a sequence of modules sorted by increasing complexity or level in the hierarchy.		
+		Also, the deactivation threshold allows to stop sampling tasks that are already mastered.
+		However, if a task can't be mastered, for instance if a large part of the sensori space is not reachable (which is often the case), 
+		then its competence might never exceed the deactivation threshold, which is not really a problem, and might even not exceed the activation threshold, at least if we use random goal babbling that might often
+		set unreachable goals. That could be a problem as only non progressing modules might be activated.
+		One could lower the activation threshold but its benefit will be lower also.
+		If SAGG-RIAC is used, the apparent competence will be the one on sampled points in progressing subregions of the tree, thus mostly in reachable parts, so that might not be an issue.
+
+	%
+
 %
@@
 			\paragraph{}
-			Different possibilities to handle exploration in the hierarchy:
+			Different possibilities to handle exploration in the hierarchy (implemented):
 			\begin{itemize}
-				\item MAB on all modules (implemented: greedy, softmax),
-				\item MAB biaised on lower modules (implemented),
-				\item ZPDES (to check with Benjamin).
+				\item MAB on all modules (greedy, softmax),
+				\item MAB biaised on lower modules (see Sec. \ref{NSLWLR}),
+				\item ZPDES (see Sec. \ref{zpdes}).
 			\end{itemize}
@@
 				\begin{itemize}
-					\item Idea: tocompare different possibilities of Top-Down Guidance, with hierarchy (c) of Fig. \ref{H} in order to have TD guidance at different levels: 
+					\item Idea: to compare different possibilities of Top-Down Guidance, with hierarchy (c) of Fig. \ref{H} in order to have TD guidance at different levels: 
 							arm with one higher model, hand with 2 higher models, tool1 with one higher model, or tool2 with 2 higher models.

### 2015-10-16 paper1/paper.tex
added paper1

%% bare_conf.tex
%% V1.3
%% 2007/01/11
%% by Michael Shell
%% See:
%% http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.7 or later) with an IEEE conference paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%
%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. IEEE's font choices can trigger bugs that do  ***
% *** not appear when using other class files.                            ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[conference]{include/IEEEtran}
% Add the compsoc option for Computer Society conferences.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference]{../sty/IEEEtran}

\usepackage{cite}
\usepackage[pdftex]{graphicx}

\def\xcolorversion{2.00}
\def\xkeyvalversion{1.8}
\usepackage[version=0.96]{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,snakes,automata,backgrounds,petri}

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
% There is also a support site at:
% http://algorithms.berlios.de/index.html
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/

\usepackage[caption=false,font=footnotesize]{subfig}

% *** FLOAT PACKAGES ***
%
\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure. The latest version and documentation can be found at:
% http://www.ctan.org/tex-archive/macros/latex/base/

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/misc/
% Read the url.sty source comments for usage information. Basically,
% \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{}

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Curiosity-driven Exploration of Skill Hierarchies}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{S\'ebastien Forestier}
\IEEEauthorblockA{INRIA Bordeaux Sud-Ouest\\
Bordeaux, France\\
Email: sebastien.forestier@inria.fr}
\and
\IEEEauthorblockN{Pierre-Yves Oudeyer}
\IEEEauthorblockA{INRIA Bordeaux Sud-Ouest\\
Bordeaux, France\\
Email: pierre-yves.oudeyer@inria.fr}}

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
%Homer Simpson\IEEEauthorrefmark{2},
%James Kirk\IEEEauthorrefmark{3}, 
%Montgomery Scott\IEEEauthorrefmark{3} and
%Eldon Tyrell\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
%Georgia Institute of Technology,
%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
%Email: homer@thesimpsons.com}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

\begin{abstract}
%\boldmath
The abstract goes here.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

% no keywords

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}

	The study of the control of manipulation actions in humans has revealed a modular representation of actions 
	either in the cerebral cortex and in the spinal 
	cord with compositionality: an infinite number of movements can be expressed through combination of simple primitives, 
	and generalization: certain neurons (higher 
	in the hierarchy) can represent actions independently of the effectors used \cite{cangelosi2010integration}.

	The same idea holds for language expressiveness which is based on syntactic hierarchical combinations 
	on a vocabulary, that open infinite semantic possibilities. 
	Greenfield has also argued that this parallel between manipulation and language compositionality can be found in the human ontegenic development
	with combinatorial steps for manipulation and syntax acquired approximately at the same period and in the same order \cite{green}. 
	Also, the author explains that the development of the neural substrates for language and tool use could be an ontogenic homology as first of all
	the same neural computations for hierarchical combinations and their semantics should take place for both modalities, and furthermore 
	experiments with Broca's and Wernicke's aphasics show that hierarchical organization for language and manipulation is linked. 
	Broca's aphasics, who have less syntactic organization of speech were shown to also have problems of representation of the hierarchical organization
	of constructions with blocks, whereas Wernicke's aphasics, whose syntax is normal but speech semantics is impaired, succeed in representing such objects 
	hierarchies.

	Functional MRI experiments by Higuchi et al. have shown that the human's neural substrates for tool use and language is indeed shared in 
	the dorsal BA44 Broca's area \cite{higuchi}, which gives evidence for the similar neural computations used. 
	They furthermore argue that these results supports the hypothesis that tool use have appeared first in primate evolution in F5 area,
	and then the language has developed in humans reusing part of tool use and manipulation neural substrates in human's Broca area, homolog of primate's F5.

	Like a developing child, a developmental robot will have to incrementally explore skills that add up to the hierarchy of previously learned skills 
	throughout its life, with a constraint being the cost and time of experimentation. 
	We will seek to define curiosity-driven hierarchical learning architectures 
	that could reuse the sensorimotor contingencies previously learned and to combine them 
	to explore more efficiently new complex sensorimotor models.

	\subsection{Goal of the study}

		\begin{itemize}
			\item Exploring in a structured hierarchy is more efficient than directly from $M$ to $S$.
			\item Which task should I explore now ?
			\item How to choose between different means to explore a given space ? 
			\item How can high-level tasks guide the exploration of lower-level ones ?
			\item How can the system cope with perturbations on some of the forward models ?		
		\end{itemize}

	%

	\subsection{Related work}
		\cite{ugur2014, ugur2015}.

		Different computational models have the possibility to learn skill hierarchies. 
		In finite environments represented by a factored Markov Decision Process \cite{vig}, an intrinsic motivation towards actions 
		maximizing Dynamic Bayesian Networks' structure has been shown to allow the learning of the environment's structure.

		In continuous environments but with discrete actions, Metzen et al. \cite{metzen2013} use the framework of options \cite{sutton1999between} 
		to learn skill hierarchies. 
		An intrinsic motivation rewards positively the novelty of the states encountered and negatively the prediction error of the learned skill model.

		The model from Fabisch et al. \cite{fabisch2014active} learns in a setting with a discrete task space (called contexts).
		It uses an intrinsic motivation for learning progress, and a Multi-Armed Bandit algorithm (D-UCB) to choose on which context the agent should train for.
		The Upper Confidence Bound algorithm chooses between contexts given their estimated learning progress and the uncertainty of these estimations
		by picking the context with the maximum upper confidence bound.
		In other words, it maximizes the expected reward plus something related to the uncertainty associated with it, selecting either contexts with 
		certain high rewards or ones with uncertain poor reward.
		This algorithm embeds directly a solution the exploration-exploitation trade-off problem as it represents the exploitation 
		of knowledge by the expected progress and the exploration of other solutions by the uncertainty bonus. 
		This algorithm supposes a stationary learning progress on each context so the authors use an adaptation 
		(D-UCB, \cite{kocsis2006discounted}) to encompass non-stationary learning progress.
		% Sliding Window UCB: \cite{garivier2011upper}

		In a fully continuous setting, Mugan et al. \cite{mugan} have developed an algorithm that first learns a qualitative representation of environment states
		and actions in order to then learn the structure of Dynamic Bayesian Networks representing the temporal contingencies of those states and actions.
		In order to choose which action to practice, the authors use the IAC \cite{oudeyer_intrinsic_2007} where the agent 
		is intrinsically motivated to choose actions that are estimated to yield high prediction error progress.

		Here, we will rely more specifically on the SAGG-RIAC architecture \cite{baranes_active_2013}.
		This architecture learns a single mapping between continuous motor and sensori (or task) 
		spaces with a competence-based intrinsic motivation. 
		In our hierarchy of sensorimotor models, each model will be explored using the SAGG-RIAC procedure, but it could be replaced by another one 
		without changing the mechanisms to learn the hierarchy that will be assessed.

	%
%

\section{Methods}

	\subsection{Algorithms}

		\paragraph{}
		Different module implementations (implemented):
		\begin{itemize}
			\item Motor Babbling,
			\item SAGG-Random.
		\end{itemize}

		\paragraph{}
		Different types of Sensorimotor models (implemented):
		\begin{itemize}
			\item NN or LWLR,
			\item NSLWLR to handle non stationary forward models (See Section \ref{NSLWLR}), or NSNN as NN with max gaussian\_kernel(distance) * gaussian\_kernel(time\_distance).
		\end{itemize}

		\paragraph{}
		Different possibilities to handle exploration in the hierarchy (implemented):
		\begin{itemize}
			\item MAB on all modules (greedy, softmax),
			\item MAB biaised on lower modules (see Sec. \ref{NSLWLR}),
			\item ZPDES (see Sec. \ref{zpdes}).
		\end{itemize}

		\paragraph{}
		Different types of Top-Down Drive:
		\begin{itemize}
			\item Just add noise to motor command of each module (pb: interferes with competence and progress estimation)  (implemented),
			\item Exploration budget around goals asked by higher models (explonential in $levels^{n+1}$ so even $n=1$ is not feasible in general but maybe in practice)  (implemented),
			\item Exploration budget only for the modules one layer below the babbling module (not implemented).
			\item Balance self-computed interest with Top-Down interest (implemented, based on the density of top-down goals).
		\end{itemize}

	%

	\subsection{Hierarchies}

		See Fig. \ref{Hierarchies} for exemples of hierarchies.

		\begin{figure*}[!t]
			\centerline{\subfloat[]{\input{include/H1.tikz}}
			\subfloat[]{\input{include/H2.tikz}}
			\subfloat[]{\input{include/H3.tikz}}
			\subfloat[]{\input{include/H4.tikz}}}
			\caption{Exemple of hierarchies.}
			\label{Hierarchies}					
		\end{figure*}
	%

	\subsection{Environment}

		\paragraph{}
		Different variables to test: motor and sensory dimensionalities, type of functions (linear, cosine, geometric arm, non-continuous interaction with objects), noise.

		\paragraph{Possible arm models}
		\begin{itemize}
			\item $n$ DOFs 2D geometric arm
		\end{itemize}

		\paragraph{Possible tool models}
		\begin{itemize}
			\item static piano
			\item stick 
		\end{itemize}

		\paragraph{Possible object models}
		\begin{itemize}
			\item static object with features depending on the piano
			\item dynamic object
		\end{itemize}

	%

	\subsection{Experiments}

			% Experiment 1
			\paragraph{Experiment 1: Exploring in a structured hierarchy is more efficient than directly from $M$ to $S$.}				
			\begin{itemize}
				\item Idea: to compare our simplest algorithm (explore the module with higher progress) in a realistic setting (Hierarchy (a) of Fig. \ref{Hierarchies}) to the control condition where a sensorimotor model is learned
						directly from the whole motor space $M$ to the whole sensori space $S$.

				\item Conditions: Hierarchy (a) vs $M \rightarrow S$, Motor Babbling vs SAGG-Random

				\item Features: MAB on all modules, NN, No TDD.

				\item Measures: exploration of intermediate spaces (hands, tools), exploration of top spaces (objects). Competence to reach random goals in reachable parts of intermediate and top spaces. 
						Statistics on multiple runs to see regularity/diversity in developmental trajectories.
			\end{itemize}

			% Experiment 2
			\paragraph{Experiment 2: Which task should I explore now ?}
			\begin{itemize}
				\item Idea: to compare the different possibilities to choose the module to explore in the hierarchy: maximizing the progress, maximizing with a bias towards lower-level modules, or use ZPDES,
						with the same hierarchy (a) of Fig. \ref{Hierarchies}.

				\item Conditions: Random module, MAB on all modules, MAB with bias, ZPDES.

				\item Features: Hierarchy (a), SAGG-Random, NN, No TDD.

				\item Measures: exploration of intermediate spaces (hands, tools), exploration of top spaces (objects). Competence to reach random goals in reachable parts of intermediate and top spaces. 
						Statistics on multiple runs to see regularity/diversity in developmental trajectories.
			\end{itemize}

			% Experiment 3
			\paragraph{Experiment 3: How to choose between different means to explore a given space ?}
			\begin{itemize}
				\item Idea: to explain how we can choose between different means (e.g. different tools) using the one with the maximal competence, or maximal progress.
						We can use the hierarchy (b) of Fig. \ref{Hierarchies}, in order to have 2 different tools to move the object.

				\item Conditions: maximize competence vs progress, noise on each tool, reachability (e.g. size) of each tool.

				\item Features: Hierarchy (b), MAB on all modules, SAGG-Random, NN, No TDD.

				\item Measures: exploration of intermediate spaces (hand, tools), exploration of top spaces (object). Competence to reach random goals in reachable parts of intermediate and top spaces. 
						Statistics on multiple runs to see regularity/diversity in developmental trajectories.
			\end{itemize}

			% Experiment 4
			\paragraph{Experiment 4: How can high-level tasks guide the exploration of lower-level ones ?}
			\begin{itemize}
				\item Idea: to compare different possibilities of Top-Down Guidance, with hierarchy (c) of Fig. \ref{Hierarchies} in order to have TD guidance at different levels: 
						arm with one higher model, hand with 2 higher models, tool1 with one higher model, or tool2 with 2 higher models.

				\item Conditions: No TDD, Just add noise to motor command of each module (pb: interferes with competence estimation) 
						vs explore $n$ points and returns the best (warning: exponential)
						vs only one layer below the babbling module explores $n$ points.

				\item Features: Hierarchy (c), MAB on all modules with bias (or no bias?), SAGG-Random, NN.

				\item Measures: exploration of intermediate spaces (hands, tools), exploration of top spaces (objects). Competence to reach random goals in reachable parts of intermediate and top spaces. 
						Statistics on multiple runs to see regularity/diversity in developmental trajectories.
			\end{itemize}

			% Experiment 5
			\paragraph{Experiment 5: How can the system cope with perturbations on some of the forward models ?}
			\begin{itemize}
				\item Idea: to apply perturbations to one of the possible forward models, either blocking, shifting or randomizing one dimension. 
						We can use the hierarchy (d) of Fig. \ref{Hierarchies} in order to see an adaptation at 2 levels: the use of one hand to use one tool, the use of both tools to move the object even if only one is perturbated.

				\item Conditions: No perturbations, which model is perturbated (arm, tool), type of perturbation (blocking, shifting, random).

				\item Features: Hierarchy (d), MAB on all modules, SAGG-Random, NN, best TDD.

				\item Measures: exploration of intermediate spaces (hands, tools) and top spaces (objects) before and after perturbations. 
						Competence to reach random goals in reachable parts of intermediate and top spaces before and after perturbations. 
						Statistics on multiple runs to see regularity/diversity in developmental trajectories.
			\end{itemize}

%

\section{Results}

%

\section{Discussion}

%

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation Results}
%\label{fig_sim}
%\end{figure}

% Note that IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command, the
% \label for the overall figure must come after \caption.
% \hfil must be used as a separator to get equal spacing.
% The subfigure.sty package works much the same way, except \subfigure is
% used instead of \subfloat.
%
%\begin{figure*}[!t]
%\centerline{\subfloat[Case I]\includegraphics[width=2.5in]{subfigcase1}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{subfigcase2}%
%\label{fig_second_case}}}
%\caption{Simulation results}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.

% An example of a floating table. Note that, for IEEE style tables, the 
% \caption command should come BEFORE the table. Table text will default to
% \footnotesize as IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that IEEE does not put floats in the very first column - or typically
% anywhere on the first page for that matter. Also, in-text middle ("here")
% positioning is not used. Most IEEE journals/conferences use top floats
% exclusively. Note that, LaTeX2e, unlike IEEE journals/conferences, places
% footnotes above bottom floats. This can be corrected via the \fnbelowfloat
% command of the stfloats package.

\section{Conclusion}
The conclusion goes here.

% conference papers do not normally have an appendix

% use section* for acknowledgement
\section*{Acknowledgment}

The authors would like to thank...

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
\bibliographystyle{include/IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)

%\begin{thebibliography}{1}

%\bibitem{IEEEhowto:kopka}
%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  %0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

%\end{thebibliography}

\bibliography{./include/bibliography}

% that's all folks
\end{document}

### 2015-10-16 roadmap/doc.tex
added paper1

@@
 		The information of interest to explore a point would be retrieved as the density of points in the kdtree around the given point.
-		This could be computed with sklearn.neighbors.KDTree.kernel\_density that takes the bandwidth of a gaussian kernel as input.
-
-		In order to balance self-computed interest with Top-Down interest, we could include the Top-Down information into the softmax choice of a leaf of the interest model's tree (in SAGG-RIAC) to explore.
-		Up to now, the weights of the leaves are the competence progress on the points of each leaf.
-		The idea is to also weight the interest of the leaves by the density of the Top-Down points around the center of each leaf.
-		The bandwidth of the gaussian kernel could be proportional to the leaf's size as that is the relevant scale to smooth density information.
-
-		In the case where we do not use SAGG-RIAC but SAGG-Random, instead of sampling random goals, we could directly sample the density map (implemented in sklearn) most of the time, and randomly sample sometime.
+
+		If we use SAGG-Random, instead of sampling random goals, we could directly sample the density map most of the time (one parameter from $0$ to $1$), and randomly sample sometime.
+
+		Fig. \ref{TDD} shows the results of the exploration of a 1D space with a 2-modules hierarchy: first modules learns $s1 = m1$ and second module learns $s2 = 2 * s1$ with $m1, s1, s2 \in [0-1]$.
+		The idea is that for the second module to progress, only half of the motor space ($m1\in [0-0.5]$) is useful to explore.
+The Top-Down guidance of module 2 on module 1 thus makes it focus more on that part.
+		The results show that the larger the TD weight, the larger the exploration of $S2=[0-1]$ (divided into 500 small parts). 
+		Also, other tests show as expected that the smaller the useful area of M1 for module 2, the larger the benefit of
+		Top-Down guidance on the exploration of S2.
+
+		\begin{figure}[H]
+			\centering
+			\subfloat[]{\includegraphics[width=6cm]{./include/TDD0.png}}
+			\subfloat[]{\includegraphics[width=6cm]{./include/TDD0-5.png}}
+			\subfloat[]{\includegraphics[width=6cm]{./include/TDD1.png}}
+			\caption{(a) no Top-Down Guidance. (b) Top-Down Guidance with weight $0.5$. (c) Top-Down Guidance with weight $1$.}
+			\label{TDD}
+		\end{figure}
+
+		In the case we use SAGG-RIAC, and in order to balance self-computed interest with Top-Down interest, 
+		we could include the Top-Down information into the softmax choice of a leaf of the interest model's tree to explore.
+		By default, the weights of the leaves are the competence progress on the points of each leaf.
+		An idea is to also weight the interest of the leaves by the number of TD goals in that leaf.
+		I've also implemented that algorithm, which shows also a benefit from SAGG-RIAC.
 
@@
 
-		\paragraph{Taking into account the progress in the leaf of the remote module that has been babbled.}
+		\paragraph{Taking into account the progress in the leaf of the remote module that has babbled.}
 		In the density algorithm above, when a higher module has asked for a goal $s_g$, that point is added to the density map of Top-Down goals, 
@@
 	The next important steps are to properly formulate, analyze and illustrate the different questions of this report, first in abstract settings before real experimental setups.
-	The first question is how to explore a given, fixed hierarchy of tasks, and how the different algorithms behave (Section \ref{study1}).
+	The first question is how to explore a given, fixed hierarchy of tasks, and how the different algorithms behave.
 	In those algorithms, the hierarchy of models to learn is given to the agent as if it already knew the combinations of actions to explore in order to learn the successive tasks.
 	This is a strong hypothesis as infants have first to discover what types of actions to combine to get a specific outcome.	
-	The second question is thus how and when to autonomously combine the previously learned actions in a relevant hierarchy of skills (Section \ref{study2}).	
-	Then, we will study the integration of social guidance into those algorithms (Section \ref{study3}).
+	The second question is thus how and when to autonomously combine the previously learned actions in a relevant hierarchy of skills.	
+	Then, we will study the integration of social guidance into those algorithms.
 
@@
 
-\newpage
-
-\section{Study 1: Exploration of a given hierarchy of skills}
-\label{study1}
-
-	\subsection{Introduction}
-
-		Explain related work: \cite{vig, ugur2014, ugur2015}.
-
-	%
-
-	\subsection{Questions}
-
-		\begin{itemize}
-			\item Exploring in a structured hierarchy is more efficient than directly from $M$ to $S$.
-			\item Which task should I explore now ?
-			\item How to choose between different means to explore a given space ? 
-			\item How can high-level tasks guide the exploration of lower-level ones ?
-			\item How can the system cope with perturbations on some of the forward models ?		
-		\end{itemize}
-
-	%
-
-	\subsection{Methods}
-
-		\subsubsection{Algorithms}
-
-			\paragraph{}
-			Different module implementations (implemented):
-			\begin{itemize}
-				\item Motor Babbling,
-				\item SAGG-Random.
-			\end{itemize}
-
-			\paragraph{}
-			Different types of Sensorimotor models (implemented):
-			\begin{itemize}
-				\item NN or LWLR,
-				\item NSLWLR to handle non stationary forward models (See Section \ref{NSLWLR}), or NSNN as NN plus a weighting by time.
-			\end{itemize}
-
-			\paragraph{}
-			Different possibilities to handle exploration in the hierarchy (implemented):
-			\begin{itemize}
-				\item MAB on all modules (greedy, softmax),
-				\item MAB biaised on lower modules (see Sec. \ref{NSLWLR}),
-				\item ZPDES (see Sec. \ref{zpdes}).
-			\end{itemize}
-
-			\paragraph{}
-			Different types of Top-Down Drive:
-			\begin{itemize}
-				\item Just add noise to motor command of each module (pb: interferes with competence and progress estimation)  (implemented),
-				\item Exploration budget around goals asked by higher models (explonential in $levels^{n+1}$ so even $n=1$ is not feasible in general but maybe in practice)  (implemented),
-				\item Exploration budget only for the modules one layer below the babbling module (not implemented).
-				\item Balance self-computed interest with Top-Down interest (See Section \ref{tddkdtree}, not implemented).
-			\end{itemize}
-
-		%
-
-		\subsubsection{Hierarchies}
-
-			\begin{figure}[H] 
-				\subfloat[]{\input{include/H1.tikz}}
-				\subfloat[]{\input{include/H2.tikz}}
-				\subfloat[]{\input{include/H3.tikz}}
-				\subfloat[]{\input{include/H4.tikz}}
-				\caption{Exemple of hierarchies.}
-				\label{H}					
-			\end{figure}
-		%
-
-		\subsubsection{Environment}
-
-			\paragraph{}
-			Different variables to test: motor and sensory dimensionalities, type of functions (linear, cosine, geometric arm, non-continuous interaction with objects), noise.
-
-			\paragraph{Possible arm models:}
-			\begin{itemize}
-				\item $n$ DOFs 2D geometric arm
-			\end{itemize}
-
-			\paragraph{Possible tool models:}
-			\begin{itemize}
-				\item static piano
-				\item stick 
-			\end{itemize}
-
-			\paragraph{Possible object models:}
-			\begin{itemize}
-				\item static object with features depending on the piano
-				\item dynamic object
-			\end{itemize}
-
-		%
-
-		\subsubsection{Experiments}
-
-				% Experiment 1
-				\paragraph{Experiment 1: Exploring in a structured hierarchy is more efficient than directly from $M$ to $S$.}				
-				\begin{itemize}
-					\item Idea: to compare our simplest algorithm (explore the module with higher progress) in a realistic setting (Hierarchy (a) of Fig.
-\ref{H}) to the control condition where a sensorimotor model is learned
-							directly from the whole motor space $M$ to the whole sensori space $S$.
-
-					\item Conditions: Hierarchy (a) vs $M \rightarrow S$, Motor Babbling vs SAGG-Random
-
-					\item Features: MAB on all modules, NN, No TDD.
-
-					\item Measures: exploration of intermediate spaces (hands, tools), exploration of top spaces (objects). Competence to reach random goals in reachable parts of intermediate and top spaces. 
-							Statistics on multiple runs to see regularity/diversity in developmental trajectories.
-				\end{itemize}
-
-				% Experiment 2
-				\paragraph{Experiment 2: Which task should I explore now ?}
-				\begin{itemize}
-					\item Idea: to compare the different possibilities to choose the module to explore in the hierarchy: maximizing the progress, maximizing with a bias towards lower-level modules, or use ZPDES,
-							with the same hierarchy (a) of Fig. \ref{H}.
-
-					\item Conditions: Random module, MAB on all modules, MAB with bias, ZPDES.
-
-					\item Features: Hierarchy (a), SAGG-Random, NN, No TDD.
-
-					\item Measures: exploration of intermediate spaces (hands, tools), exploration of top spaces (objects). Competence to reach random goals in reachable parts of intermediate and top spaces. 
-							Statistics on multiple runs to see regularity/diversity in developmental trajectories.
-				\end{itemize}
-
-				% Experiment 3
-				\paragraph{Experiment 3: How to choose between different means to explore a given space ?}
-				\begin{itemize}
-					\item Idea: to explain how we can choose between different means (e.g. different tools) using the one with the maximal competence, or maximal progress.
-							We can use the hierarchy (b) of Fig. \ref{H}, in order to have 2 different tools to move the object.
-
-					\item Conditions: maximize competence vs progress, noise on each tool, reachability (e.g. size) of each tool.
-
-					\item Features: Hierarchy (b), MAB on all modules, SAGG-Random, NN, No TDD.
-
-					\item Measures: exploration of intermediate spaces (hand, tools), exploration of top spaces (object). Competence to reach random goals in reachable parts of intermediate and top spaces. 
-							Statistics on multiple runs to see regularity/diversity in developmental trajectories.
-				\end{itemize}
-
-				% Experiment 4
-				\paragraph{Experiment 4: How can high-level tasks guide the exploration of lower-level ones ?}
-				\begin{itemize}
-					\item Idea: to compare different possibilities of Top-Down Guidance, with hierarchy (c) of Fig. \ref{H} in order to have TD guidance at different levels: 
-							arm with one higher model, hand with 2 higher models, tool1 with one higher model, or tool2 with 2 higher models.
-
-					\item Conditions: No TDD, Just add noise to motor command of each module (pb: interferes with competence estimation) 
-							vs explore $n$ points and returns the best (warning: exponential)
-							vs only one layer below the babbling module explores $n$ points.
-
-					\item Features: Hierarchy (c), MAB on all modules with bias (or no bias?), SAGG-Random, NN.
-
-					\item Measures: exploration of intermediate spaces (hands, tools), exploration of top spaces (objects). Competence to reach random goals in reachable parts of intermediate and top spaces. 
-							Statistics on multiple runs to see regularity/diversity in developmental trajectories.
-				\end{itemize}
-
-				% Experiment 5
-				\paragraph{Experiment 5: How can the system cope with perturbations on some of the forward models ?}
-				\begin{itemize}
-					\item Idea: to apply perturbations to one of the possible forward models, either blocking, shifting or randomizing one dimension. 
-							We can use the hierarchy (d) of Fig.
-\ref{H} in order to see an adaptation at 2 levels: the use of one hand to use one tool, the use of both tools to move the object even if only one is perturbated.
-
-					\item Conditions: No perturbations, which model is perturbated (arm, tool), type of perturbation (blocking, shifting, random).
-
-					\item Features: Hierarchy (d), MAB on all modules, SAGG-Random, NN, best TDD.
-
-					\item Measures: exploration of intermediate spaces (hands, tools) and top spaces (objects) before and after perturbations. 
-							Competence to reach random goals in reachable parts of intermediate and top spaces before and after perturbations. 
-							Statistics on multiple runs to see regularity/diversity in developmental trajectories.
-				\end{itemize}
-
-		%
-
-	%
-
-%
-
-\section{Study 2: Curiosity-driven combination of skills}
-\label{study2}
-
-%
-
-\section{Study 3: Socially-guided combination of skills}
-\label{study3}
-
-%
-
 \bibliographystyle{apalike}

### 2015-11-05 paper1/paper.tex
hierarchies
xp1 xp2

@@
 
-\section{Methods}
+\section{Environment}
 
-	\subsection{Algorithms}
+	\begin{figure}[!t]
+		\centering
+		\includegraphics[width=8cm]{./include/tools.png}
+		\caption{Play Environment}
+		\label{env}
+	\end{figure}
 
-		\paragraph{}
-		Different module implementations (implemented):
-		\begin{itemize}
-			\item Motor Babbling,
-			\item SAGG-Random.
-		\end{itemize}
-
-		\paragraph{}
-		Different types of Sensorimotor models (implemented):
-		\begin{itemize}
-			\item NN or LWLR,
-			\item NSLWLR to handle non stationary forward models (See Section \ref{NSLWLR}), or NSNN as NN with max gaussian\_kernel(distance) * gaussian\_kernel(time\_distance).
-		\end{itemize}
-
-		\paragraph{}
-		Different possibilities to handle exploration in the hierarchy (implemented):
-		\begin{itemize}
-			\item MAB on all modules (greedy, softmax),
-			\item MAB biaised on lower modules (see Sec. \ref{NSLWLR}),
-			\item ZPDES (see Sec. \ref{zpdes}).
-		\end{itemize}
-
-		\paragraph{}
-		Different types of Top-Down Drive:
-		\begin{itemize}
-			\item Just add noise to motor command of each module (pb: interferes with competence and progress estimation)  (implemented),
-			\item Exploration budget around goals asked by higher models (explonential in $levels^{n+1}$ so even $n=1$ is not feasible in general but maybe in practice)  (implemented),
-			\item Exploration budget only for the modules one layer below the babbling module (not implemented).
-			\item Balance self-computed interest with Top-Down interest (implemented, based on the density of top-down goals).
-		\end{itemize}
+	See Fig. \ref{env} for the initial state of the environment.
 
@@
 
-	\subsection{Hierarchies}
-
-		See Fig. \ref{Hierarchies} for exemples of hierarchies.
-
-		\begin{figure*}[!t]
-			\centerline{\subfloat[]{\input{include/H1.tikz}}
-			\subfloat[]{\input{include/H2.tikz}}
-			\subfloat[]{\input{include/H3.tikz}}
-			\subfloat[]{\input{include/H4.tikz}}}
-			\caption{Exemple of hierarchies.}
-			\label{Hierarchies}					
-		\end{figure*}
-	%
-
-	\subsection{Environment}
-
-		\paragraph{}
-		Different variables to test: motor and sensory dimensionalities, type of functions (linear, cosine, geometric arm, non-continuous interaction with objects), noise.
-
-		\paragraph{Possible arm models}
-		\begin{itemize}
-			\item $n$ DOFs 2D geometric arm
-		\end{itemize}
-
-		\paragraph{Possible tool models}
-		\begin{itemize}
-			\item static piano
-			\item stick 
-		\end{itemize}
-
-		\paragraph{Possible object models}
-		\begin{itemize}
-			\item static object with features depending on the piano
-			\item dynamic object
-		\end{itemize}
+\section{Random Goal Babbling}
 
@@
 
-	\subsection{Experiments}
+\section{Hierarchically structured exploration}
+
+	\begin{figure}[!t]
+		\center
+		\input{include/H1.tikz}
+		\caption{H1}
+		\label{H1}					
+	\end{figure}
 
 	% Experiment 1
-			\paragraph{Experiment 1: Exploring in a structured hierarchy is more efficient than directly from $M$ to $S$.}				
+	\subsection{Experiment 1: Methods}
+
 		\begin{itemize}
@@
 
+	%
+
+	\subsection{Experiment 1: Results}
+
+		\begin{figure*}[!t]
+			\centering
+			\subfloat[Competences]{\includegraphics[width=6cm]{./include/H0-GB-log6-competences.png}}
+			\subfloat[Interests]{\includegraphics[width=6cm]{./include/H0-GB-log6-interests.png}}
+			\subfloat[Events]{\includegraphics[width=6cm]{./include/H0-GB-log6-events.png}}
+			\caption{Competences, interests and events using H0 with Random Goal Babbling}
+			\label{resH0GB}
+		\end{figure*}
+
+		\begin{figure*}[!t]
+			\centering
+			\subfloat[Competences]{\includegraphics[width=6cm]{./include/H1-GB-log5-competences.png}}
+			\subfloat[Interests]{\includegraphics[width=6cm]{./include/H1-GB-log5-interests.png}}
+			\subfloat[Events]{\includegraphics[width=6cm]{./include/H1-GB-log5-events.png}}
+			\caption{Competences, interests and events using H1 with Random Goal Babbling}
+			\label{resH1GB}
+		\end{figure*}
+
+		\begin{figure*}[!t]
+			\centering
+			\subfloat[Tool]{\includegraphics[width=6cm]{./include/xp1-n_tool_1.png}}
+			\subfloat[Object]{\includegraphics[width=6cm]{./include/xp1-n_obj.png}}
+			\subfloat[Box 1]{\includegraphics[width=6cm]{./include/xp1-n_box_1.png}}\\
+			\subfloat[Box 2]{\includegraphics[width=6cm]{./include/xp1-n_box_2.png}}
+			\subfloat[Box 3]{\includegraphics[width=6cm]{./include/xp1-n_box_3.png}}
+			\caption{Number of touch of tool, object and boxes for each 100 iterations' bin.}
+			\label{res_xp1_events}
+		\end{figure*}
+
+		See Fig. \ref{resH0GB}, \ref{resH1GB} and \ref{res_xp1_events}.
+
+	%
+
+	\subsection{Experiment 1: Discussion}
+
+	%
+
+%
+
+\section{Choice of module to explore}
+
 	% Experiment 2
-			\paragraph{Experiment 2: Which task should I explore now ?}
+	\subsection{Experiment 2: Methods}
+
 		\begin{itemize}
@@
 
+	%
+
+	\subsection{Experiment 2: Results}
+
+	%
+
+	\subsection{Experiment 2: Discussion}
+
+	%
+
+%
+
+\section{Choice of tool to use}
+
+	\begin{figure}[!t]
+		\center
+		\input{include/H2.tikz}
+		\caption{H2}
+		\label{H2}					
+	\end{figure}
+
 	% Experiment 3
-			\paragraph{Experiment 3: How to choose between different means to explore a given space ?}
+	\subsection{Experiment 3: Methods}
+
 		\begin{itemize}
@@
 
+	%
+
+	\subsection{Experiment 3: Results}
+
+	%
+
+	\subsection{Experiment 3: Discussion}
+
+	%
+
+%
+
+\section{Top-Down Guidance}
+
 	% Experiment 4
-			\paragraph{Experiment 4: How can high-level tasks guide the exploration of lower-level ones ?}
+	\subsection{Experiment 4: Methods}	
+	%\paragraph{Experiment 4: How can high-level tasks guide the exploration of lower-level ones ?}
+
 		\begin{itemize}
@@
 
+	%
+
+	\subsection{Experiment 4: Results}
+
+	%
+
+	\subsection{Experiment 4: Discussion}
+
+	%
+
+%
+
+\section{Robustness to perturbations}
+
 	% Experiment 5
-			\paragraph{Experiment 5: How can the system cope with perturbations on some of the forward models ?}
+	\subsection{Experiment 5: Methods}	
+	%\paragraph{Experiment 5: How can the system cope with perturbations on some of the forward models ?}
+
 		\begin{itemize}
@@
 
-\section{Results}
+	\subsection{Experiment 5: Results}
 
@@
 
-\section{Discussion}
+	\subsection{Experiment 5: Discussion}
+
+	%
+
+%
+
+	%\subsection{Algorithms}
+
+		%\paragraph{}
+		%Different module implementations (implemented):
+		%\begin{itemize}
+			%\item Motor Babbling,
+			%\item SAGG-Random.
+		%\end{itemize}
+
+		%\paragraph{}
+		%Different types of Sensorimotor models (implemented):
+		%\begin{itemize}
+			%\item NN or LWLR,
+			%\item NSLWLR to handle non stationary forward models (See Section \ref{NSLWLR}), or NSNN as NN with max gaussian\_kernel(distance) * gaussian\_kernel(time\_distance).
+		%\end{itemize}
+
+		%\paragraph{}
+		%Different possibilities to handle exploration in the hierarchy (implemented):
+		%\begin{itemize}
+			%\item MAB on all modules (greedy, softmax),
+			%\item MAB biaised on lower modules (see Sec. \ref{NSLWLR}),
+			%\item ZPDES (see Sec. \ref{zpdes}).
+		%\end{itemize}
+
+		%\paragraph{}
+		%Different types of Top-Down Drive:
+		%\begin{itemize}
+			%\item Just add noise to motor command of each module (pb: interferes with competence and progress estimation)  (implemented),
+			%\item Exploration budget around goals asked by higher models (explonential in $levels^{n+1}$ so even $n=1$ is not feasible in general but maybe in practice)  (implemented),
+			%\item Exploration budget only for the modules one layer below the babbling module (not implemented).
+			%\item Balance self-computed interest with Top-Down interest (implemented, based on the density of top-down goals).
+		%\end{itemize}
+
+	%
+
+%
+
+\section{General Discussion}
 
@@
 
-\section{Conclusion}
-The conclusion goes here.
+%\section{Conclusion}
+%The conclusion goes here.
 
@@
 % use section* for acknowledgement
-\section*{Acknowledgment}
+%\section*{Acknowledgment}
 
-The authors would like to thank...
+%The authors would like to thank...
 

### 2015-11-05 paper1/paper.tex
xp1 xp2

@@
 
+	We simulate a 2D robotic arm using tools to push an object in its environment with the help of an experienced pair. 
+	The agent can either try to push objects into boxes on its own, or produce a vocal signal that might engage the experienced pair to help move the object to reach a box.
+
+	The environment is designed such that each box is more easily reached by one different mean.
+	Box 1 is best reached with the small stick, box 2 with the long stick, and box 3 with the small stick and the help of the pair.
+
+	An iteration consists of the evaluation of a motor command given by the agent which gives
+	sensory information back to him, and 
+	finally the environment is resetted to its intial state.
+
 	\begin{figure}[!t]
@@
 
-	See Fig. \ref{env} for the initial state of the environment.
+	The next sections precisely describe the different items of the environment and their interactions.	
+	See Fig. \ref{env} for an exemple of the state of the environment.
+
+	\subsection{Robotic arm}
+
+		The 2D robotic arm has 3 joints plus a gripper located at the end-effector.
+		Each joint can rotate from $-\pi~rad$ to $\pi~rad$ around its initial position, mapped to a standard interval of $[-1,1]$.
+		The length of the 3 parts of the arm are $0.5$, $0.3$ and $0.2$ so the total length of the arm is $1$ unit.
+		The initial position of the arm is vertical with each joint at $0~rad$ and its base is fixed at position $[0, 0]$.
+		The gripper $g$ has 2 possible positions: \textit{open} ($g \geq 0$) and \textit{closed} ($g < 0$) and its initial position is \textit{open} (with $g = 0$).
+		The robotic arm thus has 4 degrees of freedom represented by a vector in $[-1,1]^4$.
+		A trajectory of the arm will be represented as a sequence of such vectors.
+
+	%
+
+	\subsection{Objects and tools}
+
+		A yellow squared object can be moved into one of the 3 fixed squared boxes. 
+		The initial position of the yellow square is $(-0.75, 1)$ and is thus unreachable with directly with the gripper.
+		One of 2 sticks can be grasped in order to reach the object.
+		A small stick of length $0.5$ is located on the left of the arm, with initial position $(-0.5, 0)$ and initial angle $\frac{3\pi}{4}$ from the horizontal line.
+		A long stick of length $1.$ is located on the right of the arm, with initial position $(0.5, 0)$ and initial angle $\frac{\pi}{4}$ from the horizontal line as in Fig. \ref{env}.
+
+		If the gripper closes near the end of one of the sticks (closer than $0.2$), it is considered grasped and will follow the gripper's position and the angle (with some noise) of the arm's last part until the gripper opens.
+		The grasped stick will have its angle equal to arm's last part plus a gaussian noise (of size $0.02$ for the small sitck and $0.1$ for the long one), updated at each step of the movement.
+
+		Similarly, if the other end of a stick reaches the yellow squared object (within $0.25$), the object will follow the end of the stick.
+		Three boxes are fixed at positions $(-1.25, 0)$, $(0, 1.75)$ and $(-1.75, 0)$ and have size $0.5$.
+		At the end of the trial, the object is considered to be in one of the box if its center is in the box.
+
+	%
+
+	\subsection{Help from an experienced pair}
+
+		A pair sitting at the right of the robot will help him put the yellow square into the closer box.
+		It will wait for the robot to move the object on its own, and if the robot also produces the good vocal signal, will move the object to the closest box.
+
+		However, as the long stick is long enough to reach the any of the 3 boxes but not the small one, the pair will help the robot only when it will use the small stick.
+		Also, as the pair is sitting on the right side of the robot, it will be unable to help reach box 1 (on the left).
+		The pair will help reach box 2 (on the front) but with a bad precision as it is far, and box 3 (on the right) with a good precision.
+		The pair will put the object at the center of box 2 (with a gaussian noise of size $0.2$ on x and y dimensions thus missing the box quite often), 
+		only if the object is located near box 2 at a distance from the base of the arm greater than $1.$ and an angle from the horizontal line between $45°$ and $105°$.
+		If the angle is between $-15°$ and $45°$, then the pair moves it towards the center of box 3 with a gaussian noise of size $0.05$, thus rarely missing the box.
+
+		We simulate a simple vocal signal controled by pitch and intensity between $-1$ and $1$.
+		The pair will engage in helping the robot only if pitch and intensity were sufficiently high ($>0.$).
+	%
+
+	\subsection{Motor control}
+
+		We use Dynamical Movement Primitive \cite{ijspeert_dynamical_2013} to control the arm's movement as this framework permits the production of a diversity of arm's trajectories with few parameters.
+		Each of the 4 arm's degree of freedom (DOF) is controlled by a DMP with a starting and a goal position equal to the rest position of the joint.
+		Each DMP is parameterized by one weight on each of 3 basis functions whose centers are distributed homogeneously throughout the movement.
+		The weights are bounded in the interval $[-200,200]$ (mapped to the standard interval $[-1,1]$) which allow each joint to cover its standard interval $[-1,1]$ during the movement.
+		Each DMP outputs a series of $50$ positions that represents a sampling of the trajectory of one joint during the movement.
+
+		The arm's movement is thus parameterized by $12$ weights, and the static vocal signal by $2$ weights.
+		Let $M_a$ be the $12D$ space of arm's commands $[-1,1]^{12}$, $M_v$ be the $2D$ vocal space, and $M$ the $14D$ global motor space.
+
+	%
+
+	\subsection{Sensory feedback}
+
+		At the end of the movement, the robot gets sensory feedback from the different items of the environment.
+		It gets the trajectory of its hand and gripper, whether the vocal signal engaged the pair or not, the trajectory of the end of the sticks, 
+		the end position of the object, and whether the object is in each box and at which distance.
+
+		The trajectory of the hand and of the end point of the sticks is the sequence of x and y positions at different time points: steps $12$, $25$, $37$ during the movement of $50$ steps.
+		The trajectory of the gripper is a sequence of $1$ or $-1$ depending whether the gripper is open or not.
+		The pair understanding of the vocal signal is represented as $1$ if intensity and pitch were correct, $-1$ otherwise.
+		For each box, the robot receives a $1$ if the object was in the box, and $0$ otherwise, plus the distance between the end position of the object and the center of the box.
+
+		The sensory information thus contains $6$ dimensions for the trajectory of the hand, $1$ for the pair help, $6$ for the trajectory of the end of each stick, $2$ for the end position of the object, and $2$ for each box.
+		The total sensory space has $44$ dimensions.
+
+	%
 

### 2015-11-06 paper1/paper.tex
xp1 xp2

@@
 
+	Curiosity-driven exploration and developmental trajectories...
+
 	The study of the control of manipulation actions in humans has revealed a modular representation of actions 
@@
 	in the hierarchy) can represent actions independently of the effectors used \cite{cangelosi2010integration}.
-
-	The same idea holds for language expressiveness which is based on syntactic hierarchical combinations 
-	on a vocabulary, that open infinite semantic possibilities. 
-	Greenfield has also argued that this parallel between manipulation and language compositionality can be found in the human ontegenic development
-	with combinatorial steps for manipulation and syntax acquired approximately at the same period and in the same order \cite{green}. 
-	Also, the author explains that the development of the neural substrates for language and tool use could be an ontogenic homology as first of all
-	the same neural computations for hierarchical combinations and their semantics should take place for both modalities, and furthermore 
-	experiments with Broca's and Wernicke's aphasics show that hierarchical organization for language and manipulation is linked. 
-	Broca's aphasics, who have less syntactic organization of speech were shown to also have problems of representation of the hierarchical organization
-	of constructions with blocks, whereas Wernicke's aphasics, whose syntax is normal but speech semantics is impaired, succeed in representing such objects 
-	hierarchies.
-
-	Functional MRI experiments by Higuchi et al. have shown that the human's neural substrates for tool use and language is indeed shared in 
-	the dorsal BA44 Broca's area \cite{higuchi}, which gives evidence for the similar neural computations used. 
-	They furthermore argue that these results supports the hypothesis that tool use have appeared first in primate evolution in F5 area,
-	and then the language has developed in humans reusing part of tool use and manipulation neural substrates in human's Broca area, homolog of primate's F5.
 
@@
 
-	\subsection{Goal of the study}
+	Here, we will rely on the SAGG-Random architecture \cite{baranes2010intrinsically}.
+	This architecture learns a single mapping between a continuous motor space and and continuous sensory (or task) 
+	space by randomly selecting goals in the sensory space. 
+	In our hierarchy of sensorimotor models, each model will be explored using the SAGG-Random procedure, but it could be replaced by any other exploration architecture.
+
+	We want to study and compare our exploration strategies in a high-dimensional continuous environment where primitive actions can be reused to influence different perceptual spaces.
+	We will use a simulated 2D robotic arm that can interact with tools and objects. 
+	The robot will have the possibility to use different tools and to ask for the help of a pair to reach certain objects.	
+	Section \ref{sec:env} shows the details of that environment.
+
+	Section \ref{sec:saggrandom} explains in detail the SAGG-Random exploration architecture and shows how it behaves on the designed environment.
+
+	\subsection{Questions of the study}
 
 		\begin{itemize}
-			\item Exploring in a structured hierarchy is more efficient than directly from $M$ to $S$.
-			\item Which task should I explore now ?
+			\item Learning a structured hierarchy is more efficient than directly from $M$ to $S$.?
+			\item Which task should be explored now ?
 			\item How to choose between different means to explore a given space ? 
 			\item How can high-level tasks guide the exploration of lower-level ones ?
-			\item How can the system cope with perturbations on some of the forward models ?		
+			\item How can the system cope with perturbations of some of the forward models ?		
 		\end{itemize}
@@
 	\subsection{Related work}
-		\cite{ugur2014, ugur2015}.
+		Explain \cite{ugur2014, ugur2015, schmerlinggoal}.
 
@@
 
-		The model from Fabisch et al. \cite{fabisch2014active} learns in a setting with a discrete task space (called contexts).
+		The model from Fabisch et al. \cite{fabisch2014active} learns a discrete task space (tasks are called contexts).
 		It uses an intrinsic motivation for learning progress, and a Multi-Armed Bandit algorithm (D-UCB) to choose on which context the agent should train for.
@@
 		by picking the context with the maximum upper confidence bound.
-		In other words, it maximizes the expected reward plus something related to the uncertainty associated with it, selecting either contexts with 
-		certain high rewards or ones with uncertain poor reward.
-		This algorithm embeds directly a solution the exploration-exploitation trade-off problem as it represents the exploitation 
-		of knowledge by the expected progress and the exploration of other solutions by the uncertainty bonus. 
+		%In other words, it maximizes the expected reward plus something related to the uncertainty associated with it, selecting either contexts with 
+		%certain high rewards or ones with uncertain poor reward.
+		%This algorithm embeds directly a solution the exploration-exploitation trade-off problem as it represents the exploitation 
+		%of knowledge by the expected progress and the exploration of other solutions by the uncertainty bonus. 
 		This algorithm supposes a stationary learning progress on each context so the authors use an adaptation 
-		(D-UCB, \cite{kocsis2006discounted}) to encompass non-stationary learning progress.
+		\cite{kocsis2006discounted} to encompass non-stationary learning progress.
 		% Sliding Window UCB: \cite{garivier2011upper}
@@
 		and actions in order to then learn the structure of Dynamic Bayesian Networks representing the temporal contingencies of those states and actions.
-		In order to choose which action to practice, the authors use the IAC \cite{oudeyer_intrinsic_2007} where the agent 
+		In order to choose which action to practice, the authors use the Intelligent-Adaptive-Curiosity algorithm \cite{oudeyer_intrinsic_2007} where the agent 
 		is intrinsically motivated to choose actions that are estimated to yield high prediction error progress.
-
-		Here, we will rely more specifically on the SAGG-RIAC architecture \cite{baranes_active_2013}.
-		This architecture learns a single mapping between continuous motor and sensori (or task) 
-		spaces with a competence-based intrinsic motivation. 
-		In our hierarchy of sensorimotor models, each model will be explored using the SAGG-RIAC procedure, but it could be replaced by another one 
-		without changing the mechanisms to learn the hierarchy that will be assessed.
 
@@
 \section{Environment}
+\label{sec:env}
 
@@
 	Box 1 is best reached with the small stick, box 2 with the long stick, and box 3 with the small stick and the help of the pair.
+
+	A simpler version of that environment will also be considered, where only the small stick is provided to the robot (environment E1) instead of both (environment E2).
 
@@
 		We simulate a simple vocal signal controled by pitch and intensity between $-1$ and $1$.
-		The pair will engage in helping the robot only if pitch and intensity were sufficiently high ($>0.$).
+		The pair will engage in helping the robot only if pitch and intensity are sufficiently high ($>0$).
 	%
@@
 		The pair understanding of the vocal signal is represented as $1$ if intensity and pitch were correct, $-1$ otherwise.
-		For each box, the robot receives a $1$ if the object was in the box, and $0$ otherwise, plus the distance between the end position of the object and the center of the box.
+		The sensory information about the boxes is composed of 2 values. 
+		The first one tells which box has the object inside ($-1$ if no one, $-0.25$ if box 1, $0.25$ if box 2, and $0.75$ if box 3).
+		The second value is the minimal distance between a box and the object at the end of the movement and after the pair helped.
+		%For each box, the robot receives a $1$ if the object was in the box, and $0$ otherwise, plus the distance between the end position of the object and the center of the box.
 
-		The sensory information thus contains $6$ dimensions for the trajectory of the hand, $1$ for the pair help, $6$ for the trajectory of the end of each stick, $2$ for the end position of the object, and $2$ for each box.
-		The total sensory space has $44$ dimensions.
+		The sensory information thus contains $6$ dimensions for the trajectory of the hand, $1$ for the pair help, $6$ for the trajectory of the end of each stick, $2$ for the end position of the object, and $2$ for the boxes.
+		The total sensory space has $34$ dimensions if only the small stick is provided to the robot (environment E1), and $40$ dimensions if both are (environment E2).
+		%The sensory information thus contains $6$ dimensions for the trajectory of the hand, $1$ for the pair help, $6$ for the trajectory of the end of each stick, $2$ for the end position of the object, and $2$ for each box.
+		%The total sensory space has $44$ dimensions.
 
@@
 \section{Random Goal Babbling}
+\label{sec:saggrandom}
+
+	Explain SAGG-Random, NN, show results on environment for GB vs MB.
+	Explain exploration in SAGG-Random, show competence and progress with different measures (and why its important to measure that).
+	The possible perturbation of the standard measure by exploration noise, and a possible fix with the following:
+
+	We have $$||s_g - s|| = ||s_g - s_{NN} + s_{NN} - s_p + s_p - s||$$ where $s_{NN}$ is the nearest neighbor of $s_g$ in the sensorimotor mapping, and is also the sensory prediction of $m$, and $s_p$ is the sensory prediction of $m + \epsilon$.
+
+	When there is no exploration, $\epsilon=0$, so $s_{NN} = s_p$ and $$||s_g - s|| = ||s_g - s_{NN} + s_p - s||$$
+	The expression $s_g - s_{NN}$ corresponds to the novelty with respect to the already reached points, and $s_p - s$ to the forward model's prediction error.
+
+	We could also use $||s_g - s_{NN} + s_p - s||$ when $\epsilon > 0$ as the basis of the computation of competence and interest.
 
@@
 
-		\begin{itemize}
-			\item Idea: to compare our simplest algorithm (explore the module with higher progress) in a realistic setting (Hierarchy (a) of Fig.
-\ref{Hierarchies}) to the control condition where a sensorimotor model is learned
+		Here we want to compare the learning of a structured hierarchy of SAGG-Random modules with the control condition where one sensorimotor model learns
 		directly from the whole motor space $M$ to the whole sensori space $S$. 
+		For the hierarchical conditions, we randomly choose the module of the hierarchy that will explore at each iteration.
+		We also compare Motor Babbling and Goal Babbling in the hierarchical and in the flat hierarchies.
+		We use hierarchy H1 (Fig. \ref{H1}), and environmnent E1.
+		Exploration: only the babbling module will add exploration noise.
 
-			\item Conditions: Hierarchy (a) vs $M \rightarrow S$, Motor Babbling vs SAGG-Random
-
-			\item Features: MAB on all modules, NN, No TDD.
-
-			\item Measures: exploration of intermediate spaces (hands, tools), exploration of top spaces (objects). Competence to reach random goals in reachable parts of intermediate and top spaces. 
-					Statistics on multiple runs to see regularity/diversity in developmental trajectories.
-		\end{itemize}
+		We measure the number of times the agent manages to grasp the tool, push the object, and reach a box.
+		TODO: exploration of all spaces (hand, tools, object, boxes), competence to reach random goals.
 
@@
 			\centering
-			\subfloat[Competences]{\includegraphics[width=6cm]{./include/H0-GB-log6-competences.png}}
-			\subfloat[Interests]{\includegraphics[width=6cm]{./include/H0-GB-log6-interests.png}}
-			\subfloat[Events]{\includegraphics[width=6cm]{./include/H0-GB-log6-events.png}}
+			\subfloat[Competences]{\includegraphics[width=6cm]{./include/H0-GB-log1-competences.png}}
+			\subfloat[Interests]{\includegraphics[width=6cm]{./include/H0-GB-log1-interests.png}}
+			\subfloat[Events]{\includegraphics[width=6cm]{./include/H0-GB-log1-events.png}}
 			\caption{Competences, interests and events using H0 with Random Goal Babbling}
@@
 			\centering
-			\subfloat[Competences]{\includegraphics[width=6cm]{./include/H1-GB-log5-competences.png}}
-			\subfloat[Interests]{\includegraphics[width=6cm]{./include/H1-GB-log5-interests.png}}
-			\subfloat[Events]{\includegraphics[width=6cm]{./include/H1-GB-log5-events.png}}
+			\subfloat[Competences]{\includegraphics[width=6cm]{./include/H1-GB-log10-competences.png}}
+			\subfloat[Interests]{\includegraphics[width=6cm]{./include/H1-GB-log10-interests.png}}
+			\subfloat[Events]{\includegraphics[width=6cm]{./include/H1-GB-log10-events.png}}
 			\caption{Competences, interests and events using H1 with Random Goal Babbling}
@@
 			\centering
-			\subfloat[Tool]{\includegraphics[width=6cm]{./include/xp1-n_tool_1.png}}
-			\subfloat[Object]{\includegraphics[width=6cm]{./include/xp1-n_obj.png}}
-			\subfloat[Box 1]{\includegraphics[width=6cm]{./include/xp1-n_box_1.png}}\\
-			\subfloat[Box 2]{\includegraphics[width=6cm]{./include/xp1-n_box_2.png}}
-			\subfloat[Box 3]{\includegraphics[width=6cm]{./include/xp1-n_box_3.png}}
+			\subfloat[Tool]{\includegraphics[width=6cm]{./include/xp1-tool_1.png}}
+			\subfloat[Object]{\includegraphics[width=6cm]{./include/xp1-obj.png}}
+			\subfloat[Box 1]{\includegraphics[width=6cm]{./include/xp1-box_1.png}}\\
+			\subfloat[Box 2]{\includegraphics[width=6cm]{./include/xp1-box_2.png}}
+			\subfloat[Box 3]{\includegraphics[width=6cm]{./include/xp1-box_3.png}}
 			\caption{Number of touch of tool, object and boxes for each 100 iterations' bin.}
@@
 
-		\begin{itemize}
-			\item Idea: to compare the different possibilities to choose the module to explore in the hierarchy: maximizing the progress, maximizing with a bias towards lower-level modules, or use ZPDES,
-					with the same hierarchy (a) of Fig. \ref{Hierarchies}.
+		Here we want to compare the different possibilities to choose the module to explore in the hierarchy: choosing the one with the max progress (proba proportional to interest), 
+		maximizing with a bias towards lower-level modules, or use ZPDES,
+		with the same hierarchy H1 (Fig. \ref{H1}), and environmnent E1.
 
-			\item Conditions: Random module, MAB on all modules, MAB with bias, ZPDES.
+		Conditions: Random module (RD), choose with proba proportional to interest (I), the same with bias toward lower levels (IB), or ZPDES.
+		Also try to make all modules add exploration noise (EXPLOA) or only the babbling module (EXPLOB).
 
-			\item Features: Hierarchy (a), SAGG-Random, NN, No TDD.
-
-			\item Measures: exploration of intermediate spaces (hands, tools), exploration of top spaces (objects). Competence to reach random goals in reachable parts of intermediate and top spaces. 
-					Statistics on multiple runs to see regularity/diversity in developmental trajectories.
-		\end{itemize}
-
+		We measure the number of times the agent manages to grasp the tool, push the object, and reach a box.
+		TODO: exploration of all spaces (hand, tools, object, boxes), competence to reach random goals.
 	%
@@
 	\subsection{Experiment 2: Results}
+
+		See Fig. \ref{resIEXPLOB} and \ref{res_xp2_events}.
+
+		\begin{figure*}[!t]
+			\centering
+			\subfloat[Competences]{\includegraphics[width=6cm]{./include/xp2-I-EXPLOB-log4-competences.png}}
+			\subfloat[Interests]{\includegraphics[width=6cm]{./include/xp2-I-EXPLOB-log4-interests.png}}
+			\subfloat[Events]{\includegraphics[width=6cm]{./include/xp2-I-EXPLOB-log4-events.png}}
+			\caption{Competences, interests and events using H1 with I-EXPLOB}
+			\label{resIEXPLOB}
+		\end{figure*}
+
+		\begin{figure*}[!t]
+			\centering
+			\subfloat[Tool]{\includegraphics[width=6cm]{./include/xp2-tool_1.png}}
+			\subfloat[Object]{\includegraphics[width=6cm]{./include/xp2-obj.png}}
+			\subfloat[Box 1]{\includegraphics[width=6cm]{./include/xp2-box_1.png}}\\
+			\subfloat[Box 2]{\includegraphics[width=6cm]{./include/xp2-box_2.png}}
+			\subfloat[Box 3]{\includegraphics[width=6cm]{./include/xp2-box_3.png}}
+			\caption{Number of touch of tool, object and boxes for each 100 iterations' bin.}
+			\label{res_xp2_events}
+		\end{figure*}
 

### 2015-11-20 paper1/paper.tex
results 1-4

@@
 		We use hierarchy H1 (Fig. \ref{H1}), and environmnent E1.
-		Exploration: only the babbling module will add exploration noise.
+		Exploration: each module will add some exploration noise (Simple TDD).
 
@@
 			\centering
-			\subfloat[Competences]{\includegraphics[width=6cm]{./include/H0-GB-log1-competences.png}}
-			\subfloat[Interests]{\includegraphics[width=6cm]{./include/H0-GB-log1-interests.png}}
-			\subfloat[Events]{\includegraphics[width=6cm]{./include/H0-GB-log1-events.png}}
-			\caption{Competences, interests and events using H0 with Random Goal Babbling}
+			\subfloat[Competences]{\includegraphics[width=4cm]{./include/xp1-H0-GB-log2-competences.png}}
+			\subfloat[Interests]{\includegraphics[width=4cm]{./include/xp1-H0-GB-log2-interests.png}}
+			\subfloat[Events]{\includegraphics[width=4cm]{./include/xp1-H0-GB-log2-events.png}}
+			\subfloat[Object exploration]{\includegraphics[width=4cm]{./include/xp1-H0-GB-log2-obj-explo.png}}
+			\caption{Competences, interests, events and object exploration using H0 with Random Goal Babbling}
 			\label{resH0GB}
@@
 			\centering
-			\subfloat[Competences]{\includegraphics[width=6cm]{./include/H1-GB-log10-competences.png}}
-			\subfloat[Interests]{\includegraphics[width=6cm]{./include/H1-GB-log10-interests.png}}
-			\subfloat[Events]{\includegraphics[width=6cm]{./include/H1-GB-log10-events.png}}
-			\caption{Competences, interests and events using H1 with Random Goal Babbling}
+			\subfloat[Competences]{\includegraphics[width=4cm]{./include/xp1-H1-GB-log1-competences.png}}
+			\subfloat[Interests]{\includegraphics[width=4cm]{./include/xp1-H1-GB-log1-interests.png}}
+			\subfloat[Events]{\includegraphics[width=4cm]{./include/xp1-H1-GB-log1-events.png}}
+			\subfloat[Object exploration]{\includegraphics[width=4cm]{./include/xp1-H1-GB-log1-obj-explo.png}}
+			\caption{Competences, interests, events and object exploration using H1 with Random Goal Babbling}
 			\label{resH1GB}
@@
 			\centering
-			\subfloat[Tool]{\includegraphics[width=6cm]{./include/xp1-tool_1.png}}
-			\subfloat[Object]{\includegraphics[width=6cm]{./include/xp1-obj.png}}
-			\subfloat[Box 1]{\includegraphics[width=6cm]{./include/xp1-box_1.png}}\\
-			\subfloat[Box 2]{\includegraphics[width=6cm]{./include/xp1-box_2.png}}
-			\subfloat[Box 3]{\includegraphics[width=6cm]{./include/xp1-box_3.png}}
-			\caption{Number of touch of tool, object and boxes for each 100 iterations' bin.}
+			\subfloat[Tool]{\includegraphics[width=4cm]{./include/xp1-event-tool_1.png}}
+			\subfloat[Object]{\includegraphics[width=4cm]{./include/xp1-event-obj.png}}
+			\subfloat[Box 1]{\includegraphics[width=4cm]{./include/xp1-event-box_1.png}}\\
+			\subfloat[Box 2]{\includegraphics[width=4cm]{./include/xp1-event-box_2.png}}
+			\subfloat[Box 3]{\includegraphics[width=4cm]{./include/xp1-event-box_3.png}}
+			\caption{Number of touch of tool, object and boxes for each 10000 iterations' bin.}
 			\label{res_xp1_events}
@@
 
-		See Fig. \ref{resH0GB}, \ref{resH1GB} and \ref{res_xp1_events}.
+		\begin{figure*}[!t]
+			\centering
+			\subfloat[Hand]{\includegraphics[width=4cm]{./include/xp1-explo-hand.png}}
+			\subfloat[Tool]{\includegraphics[width=4cm]{./include/xp1-explo-stick_1.png}}
+			\subfloat[Object]{\includegraphics[width=4cm]{./include/xp1-explo-obj.png}}
+			\subfloat[Box]{\includegraphics[width=4cm]{./include/xp1-explo-box.png}}
+			\caption{Exploration of sensory spaces.}
+			\label{res_xp1_explo}
+		\end{figure*}
+
+		See Fig. \ref{resH0GB}, \ref{resH1GB}, \ref{res_xp1_events}, \ref{res_xp1_explo}.
 
@@
 
-		Conditions: Random module (RD), choose with proba proportional to interest (I), the same with bias toward lower levels (IB), or ZPDES.
-		Also try to make all modules add exploration noise (EXPLOA) or only the babbling module (EXPLOB).
+		Conditions:
+		\begin{itemize}
+			\item Random module (RD),
+			\item choose with proba proportional to interest (I),
+			\item ZPDES (Z).
+		\end{itemize}
 
-		We measure the number of times the agent manages to grasp the tool, push the object, and reach a box.
-		TODO: exploration of all spaces (hand, tools, object, boxes), competence to reach random goals.
+		Exploration: each module will add some exploration noise (Simple TDD).
+
+		We measure the number of times the agent manages to grasp the tool, push the object, and reach a box,
+		and the exploration of all spaces (hand, tools, object, boxes).
 	%
@@
 
-		See Fig. \ref{resIEXPLOB} and \ref{res_xp2_events}.
+		See Fig. \ref{resI}, \ref{res_xp2_events} and \ref{res_xp2_explo}.
 
@@
 			\centering
-			\subfloat[Competences]{\includegraphics[width=6cm]{./include/xp2-I-EXPLOB-log4-competences.png}}
-			\subfloat[Interests]{\includegraphics[width=6cm]{./include/xp2-I-EXPLOB-log4-interests.png}}
-			\subfloat[Events]{\includegraphics[width=6cm]{./include/xp2-I-EXPLOB-log4-events.png}}
-			\caption{Competences, interests and events using H1 with I-EXPLOB}
-			\label{resIEXPLOB}
+			\subfloat[Competences]{\includegraphics[width=4cm]{./include/xp2-H1-GB-log1-competences.png}}
+			\subfloat[Interests]{\includegraphics[width=4cm]{./include/xp2-H1-GB-log1-interests.png}}
+			\subfloat[Events]{\includegraphics[width=4cm]{./include/xp2-H1-GB-log1-events.png}}
+			\caption{Competences, interests and events using H1 with I}
+			\label{resI}
 		\end{figure*}
@@
 			\centering
-			\subfloat[Tool]{\includegraphics[width=6cm]{./include/xp2-tool_1.png}}
-			\subfloat[Object]{\includegraphics[width=6cm]{./include/xp2-obj.png}}
-			\subfloat[Box 1]{\includegraphics[width=6cm]{./include/xp2-box_1.png}}\\
-			\subfloat[Box 2]{\includegraphics[width=6cm]{./include/xp2-box_2.png}}
-			\subfloat[Box 3]{\includegraphics[width=6cm]{./include/xp2-box_3.png}}
-			\caption{Number of touch of tool, object and boxes for each 100 iterations' bin.}
+			\subfloat[Tool]{\includegraphics[width=4cm]{./include/xp2-event-tool_1.png}}
+			\subfloat[Object]{\includegraphics[width=4cm]{./include/xp2-event-obj.png}}
+			\subfloat[Box 1]{\includegraphics[width=4cm]{./include/xp2-event-box_1.png}}\\
+			\subfloat[Box 2]{\includegraphics[width=4cm]{./include/xp2-event-box_2.png}}
+			\subfloat[Box 3]{\includegraphics[width=4cm]{./include/xp2-event-box_3.png}}
+			\caption{Number of touch of tool, object and boxes for each 10000 iterations' bin.}
 			\label{res_xp2_events}
+		\end{figure*}
+
+		\begin{figure*}[!t]
+			\centering
+			\subfloat[Hand]{\includegraphics[width=4cm]{./include/xp2-explo-hand.png}}
+			\subfloat[Tool]{\includegraphics[width=4cm]{./include/xp2-explo-stick_1.png}}
+			\subfloat[Object]{\includegraphics[width=4cm]{./include/xp2-explo-obj.png}}
+			\subfloat[Box]{\includegraphics[width=4cm]{./include/xp2-explo-box.png}}
+			\caption{Exploration of sensory spaces.}
+			\label{res_xp2_explo}
 		\end{figure*}
@@
 	\subsection{Experiment 2: Discussion}
+
+	%
+
+%
+
+\section{Top-Down Guidance}
+
+	% Experiment 3
+	\subsection{Experiment 3: Methods}	
+	%\paragraph{Experiment 3: How can high-level tasks guide the exploration of lower-level ones ?}
+
+		\begin{itemize}
+			\item Idea: to compare different possibilities of Top-Down Guidance, with hierarchy H1 with TD guidance at different levels.
+
+			\item Condition STDD: (simple TDD): add noise to motor command of each module (pb: interferes with competence estimation?).
+
+			\item Condition EXPLO-N: explore $n$ points and returns the best (exponential if all modules explore $n$ points, so I've implemented that only the chosen module explores $n$ points, and the others add exploration noise)
+			%\item Condition BST: balance between self-interest and top-down points (one parameter).
+
+			\item Features: H1, choose module based on interest (I), NN.
+
+			\item Measures: exploration of intermediate spaces (hands, tools), exploration of top spaces (objects). Competence to reach random goals in reachable parts of intermediate and top spaces. 
+					Statistics on multiple runs to see regularity/diversity in developmental trajectories.
+		\end{itemize}
+
+	%
+
+	\subsection{Experiment 3: Results}
+
+		See Fig. \ref{res_xp3_events} and \ref{res_xp3_explo}.
+
+		\begin{figure*}[!t]
+			\centering
+			\subfloat[Tool]{\includegraphics[width=4cm]{./include/xp3-event-tool_1.png}}
+			\subfloat[Object]{\includegraphics[width=4cm]{./include/xp3-event-obj.png}}
+			\subfloat[Box 1]{\includegraphics[width=4cm]{./include/xp3-event-box_1.png}}\\
+			\subfloat[Box 2]{\includegraphics[width=4cm]{./include/xp3-event-box_2.png}}
+			\subfloat[Box 3]{\includegraphics[width=4cm]{./include/xp3-event-box_3.png}}
+			\caption{Number of touch of tool, object and boxes for each 10000 iterations' bin.}
+			\label{res_xp3_events}
+		\end{figure*}
+
+		\begin{figure*}[!t]
+			\centering
+			\subfloat[Hand]{\includegraphics[width=4cm]{./include/xp3-explo-hand.png}}
+			\subfloat[Tool]{\includegraphics[width=4cm]{./include/xp3-explo-stick_1.png}}
+			\subfloat[Object]{\includegraphics[width=4cm]{./include/xp3-explo-obj.png}}
+			\subfloat[Box]{\includegraphics[width=4cm]{./include/xp3-explo-box.png}}
+			\caption{Exploration of sensory spaces.}
+			\label{res_xp3_explo}
+		\end{figure*}
+
+	%
+
+	\subsection{Experiment 3: Discussion}
 
@@
 
-	% Experiment 3
-	\subsection{Experiment 3: Methods}
+	% Experiment 4
+	\subsection{Experiment 4: Methods}
 
@@
 			\item Idea: to explain how we can choose between different means (e.g. different tools) using the one with the maximal competence, or maximal progress.
-					We can use the hierarchy (b) of Fig. \ref{Hierarchies}, in order to have 2 different tools to move the object.
+					We use the hierarchy H2, in order to have 2 different tools to move the object.
 
-			\item Conditions: maximize competence vs progress, noise on each tool, reachability (e.g. size) of each tool.
+			\item Conditions: maximize competence vs interest vs interest if babbling otherwise competence (C, I, IB), local vs global computation of commpetence or interest (L, G), noise on each tool, reachability (e.g.
+size) of each tool.
 
-			\item Features: Hierarchy (b), MAB on all modules, SAGG-Random, NN, No TDD.
+			\item Features: Hierarchy H2, choose module based on interest (I), SAGG-Random, NN, Simple TDD.
 
-			\item Measures: exploration of intermediate spaces (hand, tools), exploration of top spaces (object). Competence to reach random goals in reachable parts of intermediate and top spaces. 
-					Statistics on multiple runs to see regularity/diversity in developmental trajectories.
-		\end{itemize}
-
-	%
-
-	\subsection{Experiment 3: Results}
-
-	%
-
-	\subsection{Experiment 3: Discussion}
-
-	%
-
-%
-
-\section{Top-Down Guidance}
-
-	% Experiment 4
-	\subsection{Experiment 4: Methods}	
-	%\paragraph{Experiment 4: How can high-level tasks guide the exploration of lower-level ones ?}
-
-		\begin{itemize}
-			\item Idea: to compare different possibilities of Top-Down Guidance, with hierarchy (c) of Fig. \ref{Hierarchies} in order to have TD guidance at different levels: 
-					arm with one higher model, hand with 2 higher models, tool1 with one higher model, or tool2 with 2 higher models.
-
-			\item Conditions: No TDD, Just add noise to motor command of each module (pb: interferes with competence estimation) 
-					vs explore $n$ points and returns the best (warning: exponential)
-					vs only one layer below the babbling module explores $n$ points.
-
-			\item Features: Hierarchy (c), MAB on all modules with bias (or no bias?), SAGG-Random, NN.
-
-			\item Measures: exploration of intermediate spaces (hands, tools), exploration of top spaces (objects). Competence to reach random goals in reachable parts of intermediate and top spaces. 
+			\item Measures: TODO:choice of tool depending on the targeted box, exploration of intermediate spaces (hand, tools), exploration of top spaces (object).
+Competence to reach random goals in reachable parts of intermediate and top spaces.
 					Statistics on multiple runs to see regularity/diversity in developmental trajectories.
@@
 	\subsection{Experiment 4: Results}
+
+		See Fig. \ref{res_xp4_events} and \ref{res_xp4_explo}.
+
+		\begin{figure*}[!t]
+			\centering
+			\subfloat[Tool1]{\includegraphics[width=4cm]{./include/xp4-event-tool_1.png}}
+			\subfloat[Tool2]{\includegraphics[width=4cm]{./include/xp4-event-tool_2.png}}
+			\subfloat[Object]{\includegraphics[width=4cm]{./include/xp4-event-obj.png}}\\
+			\subfloat[Box 1]{\includegraphics[width=4cm]{./include/xp4-event-box_1.png}}
+			\subfloat[Box 2]{\includegraphics[width=4cm]{./include/xp4-event-box_2.png}}
+			\subfloat[Box 3]{\includegraphics[width=4cm]{./include/xp4-event-box_3.png}}
+			\caption{Number of touch of tools, object and boxes for each 10000 iterations' bin.}
+			\label{res_xp4_events}
+		\end{figure*}
+
+		\begin{figure*}[!t]
+			\centering
+			\subfloat[Hand]{\includegraphics[width=4cm]{./include/xp4-explo-hand.png}}
+			\subfloat[Tool1]{\includegraphics[width=4cm]{./include/xp4-explo-stick_1.png}}
+			\subfloat[Tool2]{\includegraphics[width=4cm]{./include/xp4-explo-stick_2.png}}\\
+			\subfloat[Object]{\includegraphics[width=4cm]{./include/xp4-explo-obj.png}}
+			\subfloat[Box]{\includegraphics[width=4cm]{./include/xp4-explo-box.png}}
+			\caption{Exploration of sensory spaces.}
+			\label{res_xp4_explo}
+		\end{figure*}
 
@@
 			\item Idea: to apply perturbations to one of the possible forward models, either blocking, shifting or randomizing one dimension. 
-					We can use the hierarchy (d) of Fig.
-\ref{Hierarchies} in order to see an adaptation at 2 levels: the use of one hand to use one tool, the use of both tools to move the object even if only one is perturbated.
+					We can use the hierarchy H2 in order to see an adaptation at 2 levels: the use of the hand to use one tool, the use of the unbroken tool instead of the broken one.
 
-			\item Conditions: No perturbations, which model is perturbated (arm, tool), type of perturbation (blocking, shifting, random).
+			\item Conditions: No perturbations, which model is perturbated (arm, tool2), type of perturbation (blocking, shifting, noise).
 
-			\item Features: Hierarchy (d), MAB on all modules, SAGG-Random, NN, best TDD.
+			\item Features: Hierarchy H2, choose module based on interest (I), SAGG-Random, NSNN, best TDD.
 

### 2016-01-14 paper1/paper.tex
upd

@@
 		We use hierarchy H1 (Fig. \ref{H1}), and environmnent E1.
-		Exploration: each module will add some exploration noise (Simple TDD).
+		Exploration: only the chosen module add some exploration noise (No TDD).
 
@@
 			\centering
-			\subfloat[Competences]{\includegraphics[width=4cm]{./include/xp1-H0-GB-log2-competences.png}}
-			\subfloat[Interests]{\includegraphics[width=4cm]{./include/xp1-H0-GB-log2-interests.png}}
-			\subfloat[Events]{\includegraphics[width=4cm]{./include/xp1-H0-GB-log2-events.png}}
-			\subfloat[Object exploration]{\includegraphics[width=4cm]{./include/xp1-H0-GB-log2-obj-explo.png}}
+			\subfloat[Competences]{\includegraphics[width=4cm]{./include/xp1-H0-GB-log8-competences.png}}
+			\subfloat[Interests]{\includegraphics[width=4cm]{./include/xp1-H0-GB-log8-interests.png}}
+			\subfloat[Events]{\includegraphics[width=4cm]{./include/xp1-H0-GB-log8-events.png}}
+			\subfloat[Object exploration]{\includegraphics[width=4cm]{./include/xp1-H0-GB-log8-obj-explo.png}}
 			\caption{Competences, interests, events and object exploration using H0 with Random Goal Babbling}
@@
 			\centering
-			\subfloat[Competences]{\includegraphics[width=4cm]{./include/xp1-H1-GB-log1-competences.png}}
-			\subfloat[Interests]{\includegraphics[width=4cm]{./include/xp1-H1-GB-log1-interests.png}}
-			\subfloat[Events]{\includegraphics[width=4cm]{./include/xp1-H1-GB-log1-events.png}}
-			\subfloat[Object exploration]{\includegraphics[width=4cm]{./include/xp1-H1-GB-log1-obj-explo.png}}
+			\subfloat[Competences]{\includegraphics[width=4cm]{./include/xp1-H1-GB-log3-competences.png}}
+			\subfloat[Interests]{\includegraphics[width=4cm]{./include/xp1-H1-GB-log3-interests.png}}
+			\subfloat[Events]{\includegraphics[width=4cm]{./include/xp1-H1-GB-log3-events.png}}
+			\subfloat[Object exploration]{\includegraphics[width=4cm]{./include/xp1-H1-GB-log3-obj-explo.png}}
 			\caption{Competences, interests, events and object exploration using H1 with Random Goal Babbling}
@@
 
-		\begin{figure*}[!t]
-			\centering
-			\subfloat[Tool]{\includegraphics[width=4cm]{./include/xp1-event-tool_1.png}}
-			\subfloat[Object]{\includegraphics[width=4cm]{./include/xp1-event-obj.png}}
-			\subfloat[Box 1]{\includegraphics[width=4cm]{./include/xp1-event-box_1.png}}\\
-			\subfloat[Box 2]{\includegraphics[width=4cm]{./include/xp1-event-box_2.png}}
-			\subfloat[Box 3]{\includegraphics[width=4cm]{./include/xp1-event-box_3.png}}
-			\caption{Number of touch of tool, object and boxes for each 10000 iterations' bin.}
-			\label{res_xp1_events}
-		\end{figure*}
+		%\begin{figure*}[!t]
+			%\centering
+			%\subfloat[Tool]{\includegraphics[width=4cm]{./include/xp1-event-tool_1.png}}
+			%\subfloat[Object]{\includegraphics[width=4cm]{./include/xp1-event-obj.png}}
+			%\subfloat[Box 1]{\includegraphics[width=4cm]{./include/xp1-event-box_1.png}}\\
+			%\subfloat[Box 2]{\includegraphics[width=4cm]{./include/xp1-event-box_2.png}}
+			%\subfloat[Box 3]{\includegraphics[width=4cm]{./include/xp1-event-box_3.png}}
+			%\caption{Number of touch of tool, object and boxes for each 10000 iterations' bin.}
+			%\label{res_xp1_events}
+		%\end{figure*}
 
@@
 
-		See Fig. \ref{resH0GB}, \ref{resH1GB}, \ref{res_xp1_events}, \ref{res_xp1_explo}.
+		See Fig. \ref{resH0GB}, \ref{resH1GB}, \ref{res_xp1_explo}.
 
@@
 
-		Exploration: each module will add some exploration noise (Simple TDD).
+		Exploration: only the chosen module add some exploration noise (No TDD).
 
@@
 
-		See Fig. \ref{resI}, \ref{res_xp2_events} and \ref{res_xp2_explo}.
+		See Fig. \ref{resI}, \ref{res_xp2_explo}.
 
@@
 			\centering
-			\subfloat[Competences]{\includegraphics[width=4cm]{./include/xp2-H1-GB-log1-competences.png}}
-			\subfloat[Interests]{\includegraphics[width=4cm]{./include/xp2-H1-GB-log1-interests.png}}
-			\subfloat[Events]{\includegraphics[width=4cm]{./include/xp2-H1-GB-log1-events.png}}
+			\subfloat[Competences]{\includegraphics[width=4cm]{./include/xp2-H1-GB-log7-competences.png}}
+			\subfloat[Interests]{\includegraphics[width=4cm]{./include/xp2-H1-GB-log7-interests.png}}
+			\subfloat[Events]{\includegraphics[width=4cm]{./include/xp2-H1-GB-log7-events.png}}
+			\subfloat[Object exploration]{\includegraphics[width=4cm]{./include/xp2-H1-GB-log7-obj-explo.png}}
 			\caption{Competences, interests and events using H1 with I}
@@
 
-		\begin{figure*}[!t]
-			\centering
-			\subfloat[Tool]{\includegraphics[width=4cm]{./include/xp2-event-tool_1.png}}
-			\subfloat[Object]{\includegraphics[width=4cm]{./include/xp2-event-obj.png}}
-			\subfloat[Box 1]{\includegraphics[width=4cm]{./include/xp2-event-box_1.png}}\\
-			\subfloat[Box 2]{\includegraphics[width=4cm]{./include/xp2-event-box_2.png}}
-			\subfloat[Box 3]{\includegraphics[width=4cm]{./include/xp2-event-box_3.png}}
-			\caption{Number of touch of tool, object and boxes for each 10000 iterations' bin.}
-			\label{res_xp2_events}
-		\end{figure*}
+		%\begin{figure*}[!t]
+			%\centering
+			%\subfloat[Tool]{\includegraphics[width=4cm]{./include/xp2-event-tool_1.png}}
+			%\subfloat[Object]{\includegraphics[width=4cm]{./include/xp2-event-obj.png}}
+			%\subfloat[Box 1]{\includegraphics[width=4cm]{./include/xp2-event-box_1.png}}\\
+			%\subfloat[Box 2]{\includegraphics[width=4cm]{./include/xp2-event-box_2.png}}
+			%\subfloat[Box 3]{\includegraphics[width=4cm]{./include/xp2-event-box_3.png}}
+			%\caption{Number of touch of tool, object and boxes for each 10000 iterations' bin.}
+			%\label{res_xp2_events}
+		%\end{figure*}
 
@@
 
-			\item Condition STDD: (simple TDD): add noise to motor command of each module (pb: interferes with competence estimation?).
+			\item Condition NTDD: (No TDD): Only the babbling module add motor exploration noise.
 
-			\item Condition EXPLO-N: explore $n$ points and returns the best (exponential if all modules explore $n$ points, so I've implemented that only the chosen module explores $n$ points, and the others add exploration noise)
-			%\item Condition BST: balance between self-interest and top-down points (one parameter).
+			\item Condition STDD: (simple TDD): add noise to motor commands of all modules (pb: interferes with competence estimation? loose interest of hierarchy?).
+
+			\item Condition EXPLO-N: the babbling module chooses a goal $s_g$ and infers its motor command $m$. 
+					The lower level modules involved will use $m$ as a goal and will try to reach it with $n$ explorative motor commands and will finally return the now infered best motor command.
+					Thus there are $n$ explorative actions ($n=3$) for $1$ non explorative action (which still can be surprising and useful in the case of a regressive sensorimotor model).
+
+			\item Condition BST (Balance Self-generation of goals and Top-Down Drive): $0.5$ probability to choose a self-generated goal, and $0.5$ probability to choose a goal around goals asked by upper-level modules.
 
@@
 
-		\begin{figure*}[!t]
-			\centering
-			\subfloat[Tool]{\includegraphics[width=4cm]{./include/xp3-event-tool_1.png}}
-			\subfloat[Object]{\includegraphics[width=4cm]{./include/xp3-event-obj.png}}
-			\subfloat[Box 1]{\includegraphics[width=4cm]{./include/xp3-event-box_1.png}}\\
-			\subfloat[Box 2]{\includegraphics[width=4cm]{./include/xp3-event-box_2.png}}
-			\subfloat[Box 3]{\includegraphics[width=4cm]{./include/xp3-event-box_3.png}}
-			\caption{Number of touch of tool, object and boxes for each 10000 iterations' bin.}
-			\label{res_xp3_events}
-		\end{figure*}
+		%\begin{figure*}[!t]
+			%\centering
+			%\subfloat[Tool]{\includegraphics[width=4cm]{./include/xp3-event-tool_1.png}}
+			%\subfloat[Object]{\includegraphics[width=4cm]{./include/xp3-event-obj.png}}
+			%\subfloat[Box 1]{\includegraphics[width=4cm]{./include/xp3-event-box_1.png}}\\
+			%\subfloat[Box 2]{\includegraphics[width=4cm]{./include/xp3-event-box_2.png}}
+			%\subfloat[Box 3]{\includegraphics[width=4cm]{./include/xp3-event-box_3.png}}
+			%\caption{Number of touch of tool, object and boxes for each 10000 iterations' bin.}
+			%\label{res_xp3_events}
+		%\end{figure*}
 
@@
 
-		\begin{figure*}[!t]
-			\centering
-			\subfloat[Tool1]{\includegraphics[width=4cm]{./include/xp4-event-tool_1.png}}
-			\subfloat[Tool2]{\includegraphics[width=4cm]{./include/xp4-event-tool_2.png}}
-			\subfloat[Object]{\includegraphics[width=4cm]{./include/xp4-event-obj.png}}\\
-			\subfloat[Box 1]{\includegraphics[width=4cm]{./include/xp4-event-box_1.png}}
-			\subfloat[Box 2]{\includegraphics[width=4cm]{./include/xp4-event-box_2.png}}
-			\subfloat[Box 3]{\includegraphics[width=4cm]{./include/xp4-event-box_3.png}}
-			\caption{Number of touch of tools, object and boxes for each 10000 iterations' bin.}
-			\label{res_xp4_events}
-		\end{figure*}
+		%\begin{figure*}[!t]
+			%\centering
+			%\subfloat[Tool1]{\includegraphics[width=4cm]{./include/xp4-event-tool_1.png}}
+			%\subfloat[Tool2]{\includegraphics[width=4cm]{./include/xp4-event-tool_2.png}}
+			%\subfloat[Object]{\includegraphics[width=4cm]{./include/xp4-event-obj.png}}\\
+			%\subfloat[Box 1]{\includegraphics[width=4cm]{./include/xp4-event-box_1.png}}
+			%\subfloat[Box 2]{\includegraphics[width=4cm]{./include/xp4-event-box_2.png}}
+			%\subfloat[Box 3]{\includegraphics[width=4cm]{./include/xp4-event-box_3.png}}
+			%\caption{Number of touch of tools, object and boxes for each 10000 iterations' bin.}
+			%\label{res_xp4_events}
+		%\end{figure*}
 

### 2016-01-14 cogsci2016/paper.tex
init cogsci paper

% 
% Annual Cognitive Science Conference
% Sample LaTeX Paper -- Proceedings Format
%

% Original : Ashwin Ram (ashwin@cc.gatech.edu)       04/01/1994
% Modified : Johanna Moore (jmoore@cs.pitt.edu)      03/17/1995
% Modified : David Noelle (noelle@ucsd.edu)          03/15/1996
% Modified : Pat Langley (langley@cs.stanford.edu)   01/26/1997
% Latex2e corrections by Ramin Charles Nakisa        01/28/1997 
% Modified : Tina Eliassi-Rad (eliassi@cs.wisc.edu)  01/31/1998
% Modified : Trisha Yannuzzi (trisha@ircs.upenn.edu) 12/28/1999 (in process)
% Modified : Mary Ellen Foster (M.E.Foster@ed.ac.uk) 12/11/2000
% Modified : Ken Forbus                              01/23/2004
% Modified : Eli M. Silk (esilk@pitt.edu)            05/24/2005
% Modified : Niels Taatgen (taatgen@cmu.edu)         10/24/2006
% Modified : David Noelle (dnoelle@ucmerced.edu)     11/19/2014

%% Change "letterpaper" in the following line to "a4paper" if you must.

\documentclass[10pt,letterpaper]{article}

\usepackage{cogsci}
\usepackage{pslatex}
\usepackage{apacite}

\title{Curiosity-Driven Development of Tool Use Precursors}

\author{{\large \bf S\'ebastien Forestier (sebastien.forestier@inria.fr)} \\
	INRIA Bordeaux Sud-Ouest\\
	Bordeaux, France
  \AND {\large \bf Pierre-Yves Oudeyer (pierre-yves.oudeyer@inria.fr} \\
	INRIA Bordeaux Sud-Ouest\\
	Bordeaux, France}

\begin{document}

\maketitle

\begin{abstract}
This is the abstract.

\textbf{Keywords:} 
curiosity-driven learning; tool use; goal babbling; overlapping waves; 
\end{abstract}

\section{Introduction}

%

\section{Methods}

%

\section{Results}

%

\section{Discussion}

%

\begin{figure}[ht]
\begin{center}
\fbox{CoGNiTiVe ScIeNcE}
\end{center}
\caption{This is a figure.} 
\label{sample-figure}
\end{figure}

\section{Acknowledgments}

Place acknowledgments (including funding information) in a section at
the end of the paper.

\nocite{fabisch2014active}

\bibliographystyle{apacite}

\setlength{\bibleftmargin}{.125in}
\setlength{\bibindent}{-\bibleftmargin}

\bibliography{include/bibliography}

\end{document}

### 2016-01-15 cogsci2016/paper.tex
env

@@
 
+\usepackage{tikz}
+\usetikzlibrary{arrows,shapes,snakes,automata,backgrounds,petri}
+
 \title{Curiosity-Driven Development of Tool Use Precursors}
@@
 
+	\cite{flow}
+	\cite{kidd}
+	\cite{baranes2010intrinsically}
+	\cite{baranes_active_2013}
+	\cite{moulin-frier_self-organization_2014}
+	\cite{gottlieb_information-seeking_2013}
+	\cite{moulin-frier_explauto:_2014}
+	\cite{oudeyer_intrinsic_2007}
+	\cite{ijspeert_dynamical_2013}
+	\cite{riac}
+	\cite{sch}
+	\cite{oudeyer2014evolution}
+	\cite{cangelosi2010integration}
+	\cite{santucci2013}
+	\cite{ugur2015}
+	\cite{schmerlinggoal}
+	\cite{oudeyer_what_2007}
+	\cite{mugan2009}
+	\cite{metzen2013}
+	\cite{horde}
+	\cite{mugan}
+	\cite{vig}
+	\cite{sutton1999between}
+	\cite{}
+	\cite{}
+
 %
@@
 \section{Methods}
+
+	\subsection{Environment}
+	\label{sec:env}
+
+		\paragraph{}
+		We simulate a 2D robotic arm using tools to move an object into different boxes in the environment. 		
+		In each trial, we execute a motor command given by the agent, we evaluate its consequences on the sensory dimensions and we give him
+		this sensory feedback. Finally the environment is resetted to its intial state.
+
+		The next sections precisely describe the different items of the environment and their interactions.	
+		See Fig. \ref{env} for an exemple of the state of the environment.
+
+		\begin{figure}[h]
+			\centering
+			\includegraphics[width=8cm]{./include/tools.png}
+			\caption{Play Environment}
+			\label{env}
+		\end{figure}
+
+		\subsubsection{Robotic arm}
+
+			The 2D robotic arm has 3 joints plus a gripper located at the end-effector.
+			Each joint can rotate from $-\pi~rad$ to $\pi~rad$ around its initial position, mapped to a standard interval of $[-1,1]$.
+			The length of the 3 parts of the arm are $0.5$, $0.3$ and $0.2$ so the total length of the arm is $1$ unit.
+			The initial position of the arm is vertical with each joint at $0~rad$ and its base is fixed at position $[0, 0]$.
+			The gripper $g$ has 2 possible positions: \textit{open} ($g \geq 0$) and \textit{closed} ($g < 0$) and its initial position is \textit{open} (with $g = 0$).
+			The robotic arm thus has 4 degrees of freedom represented by a vector in $[-1,1]^4$.
+			A trajectory of the arm will be represented as a sequence of such vectors.
+
+		%
+
+		\subsubsection{Objects and tools}
+
+			A yellow sphere can be moved into one of the 4 fixed squared boxes. 
+			The initial position of the sphere is $(0, 1.2)$ and is thus unreachable directly with the gripper.
+			One of two sticks can be grasped in order to reach the object.
+			A small stick of length $0.3$ is located on the right of the arm, with initial position $(0.75, 0.25)$ and initial angle $\frac{\pi}{4}$ from the horizontal line.
+			A long stick of length $0.6$ is located on the left of the arm, with initial position $(-0.75, 0.25)$ and initial angle $\frac{3\pi}{4}$ from the horizontal line as in Fig. \ref{env}.			
+			If the gripper closes near the end of one of the sticks (closer than $0.1$), it is considered grasped and will follow the gripper's position and the angle of the arm's last part until the gripper opens.
+			Similarly, if the other end of a stick reaches the sphere (within $0.1$), the object will follow the end of the stick.
+			Four boxes are fixed at positions $(-1, 0)$, $(-0.5, 1)$, $(1.1, 1.3)$ and $(1.6, 0)$ and have size $0.4$, 
+			so that the two boxes on the left can be reached by the two sticks, and the two boxes on the right can only be reached by the long stick.
+			At the end of the trial, the object is considered to be in one of the box if its center is in the box.\\
+
+		%
+
+		\subsubsection{Motor control}
+
+			We use Dynamical Movement Primitive \cite{ijspeert_dynamical_2013} to control the arm's movement as this framework permits the production of a diversity of arm's trajectories with few parameters.
+			Each of the $4$ arm's degrees-of-freedom (DOF) is controlled by a DMP with a starting and a goal position equal to the rest position of the joint.
+			Each DMP is parameterized by one weight on each of $3$ basis functions whose centers are distributed homogeneously throughout the movement duration.
+			The weights are bounded in the interval $[-200,200]$ (mapped to the standard interval $[-1,1]$) which allow each joint to fairly cover the interval $[-1,1]$ during the movement.
+			Each DMP outputs a series of $50$ positions that represents a sampling of the trajectory of one joint during the movement.		
+			The arm's movement is thus parameterized by $12$ weights which are represented by the motor space $M=[-1,1]^{12}$
+
+		%
+
+		\subsubsection{Sensory feedback}
+
+			At the end of the movement, the robot gets sensory feedback from the different items of the environment.
+			It gets the trajectory of its hand and gripper, the trajectory of the end of the sticks, 
+			the end position of the object, and whether the object is in each box.		
+			The trajectory of the hand and of the end point of the sticks are represented by sequences of x and y positions at different time points: 
+			steps $12$, $25$, $37$ during the movement of $50$ steps ($6$D for the hand and for each stick).
+			Similarly, the trajectory of the gripper is a sequence of $1$ or $-1$ depending whether the gripper is open or closed ($3$D).
+			For each box, the robot receives a $1$ if the object is in the box at the end of the movement, and $0$ otherwise ($4$D).			 
+			The sensory information thus contains $9$ values for the trajectory of the hand and gripper, $6$ for the trajectory of the end of each stick, $2$ for the end position of the object and $4$ for the boxes.
+			The total sensory space has $27$ dimensions.
+			%The sensory information thus contains $6$ dimensions for the trajectory of the hand, $1$ for the pair help, $6$ for the trajectory of the end of each stick, $2$ for the end position of the object, and $2$ for each box.
+			%The total sensory space has $44$ dimensions.
+
+		%
+
+	%
+
+	\subsection{Model's architecture}
+
+		\begin{figure}[h]
+			\center
+			\input{include/H2.tikz}
+			\caption{Hierarchy of sensorimotor models}
+			\label{H}					
+		\end{figure}
 
@@
 
-\nocite{fabisch2014active}
-
 \bibliographystyle{apacite}

### 2016-01-17 cogsci2016/paper.tex
results

@@
 
+\usepackage[caption=false,font=footnotesize]{subfig}
+
 \begin{document}
@@
 
+	Development of tool use \cite{guerin2013survey}, precursors of tool use: behavior without objects, behavior with one object, interaction of objects.	
+	Grounding of representation and planning based on a large amount of experiences. 	
+	Seemless progression between the successives phases as overlapping waves. 	
+	Ongoing process of upgrading representations.	
+	Developmental trajectories.
+
+	Curiosity studies in developmental psychology 
+	\cite{kidd}
+	\cite{gottlieb_information-seeking_2013}
+
+	Curiosity-driven modelling work, emergence of developmental trajectories.
+	\cite{oudeyer_intrinsic_2007} 
+	\cite{oudeyer_what_2007}
 	\cite{flow}
-	\cite{kidd}
+	\cite{sch}
+	\cite{santucci2013}
+	\cite{cangelosi2010integration}
+	\cite{oudeyer2014evolution}
+
+	IAC series of architectures and Explauto framework: previous experiments.
+	\cite{moulin-frier_self-organization_2014}
+	\cite{moulin-frier_explauto:_2014}
 	\cite{baranes2010intrinsically}
+	\cite{riac}
 	\cite{baranes_active_2013}
-	\cite{moulin-frier_self-organization_2014}
-	\cite{gottlieb_information-seeking_2013}
-	\cite{moulin-frier_explauto:_2014}
-	\cite{oudeyer_intrinsic_2007}
-	\cite{ijspeert_dynamical_2013}
-	\cite{riac}
-	\cite{sch}
-	\cite{oudeyer2014evolution}
-	\cite{cangelosi2010integration}
-	\cite{santucci2013}
-	\cite{ugur2015}
-	\cite{schmerlinggoal}
-	\cite{oudeyer_what_2007}
+
+	Representations in explauto and other models 
 	\cite{mugan2009}
@@
 	\cite{sutton1999between}
-	\cite{}
+
+	Other related work
+	\cite{ugur2015}
+	\cite{schmerlinggoal}
+
+	More details on experiments
+	\cite{ijspeert_dynamical_2013}
+
 	\cite{}
@@
 	\subsection{Environment}
-	\label{sec:env}
 
@@
 			Similarly, if the other end of a stick reaches the sphere (within $0.1$), the object will follow the end of the stick.
-			Four boxes are fixed at positions $(-1, 0)$, $(-0.5, 1)$, $(1.1, 1.3)$ and $(1.6, 0)$ and have size $0.4$, 
+			Ten boxes are static at positions $(-1, 0)$, $(-0.5, 1)$, $(1.1, 1.3)$ and $(1.6, 0)$ and have size $0.2$, 
 			so that the two boxes on the left can be reached by the two sticks, and the two boxes on the right can only be reached by the long stick.
@@
 			The sensory information thus contains $9$ values for the trajectory of the hand and gripper, $6$ for the trajectory of the end of each stick, $2$ for the end position of the object and $4$ for the boxes.
-			The total sensory space has $27$ dimensions.
-			%The sensory information thus contains $6$ dimensions for the trajectory of the hand, $1$ for the pair help, $6$ for the trajectory of the end of each stick, $2$ for the end position of the object, and $2$ for each box.
-			%The total sensory space has $44$ dimensions.
+			The sensory space has a total of $27$ dimensions.
 
@@
 
-	\subsection{Model's architecture}
+	\subsection{Learning architectures}
 
-		\begin{figure}[h]
+		\subsubsection{Explauto framework}
+
+			\cite{moulin-frier_explauto:_2014}
+
+		%
+
+		\subsubsection{Goal Babbling}
+
+		%
+
+		\subsubsection{SAGG-RIAC}
+
+			\cite{baranes_active_2013}
+
+		%
+
+		\subsubsection{Flat architecture}
+
+		%
+
+		\subsubsection{Hierarchical architecture}
+
+			We present here an architecture that represents sensorimotor information with a hierarchical structure.
+
+			\begin{figure}[t]
 				\center
@@
 
+	%
+
+	\subsection{Experiments}
+
+		NN, 100 iterations of Motor babbling and then 300000 iterations of the condition
+
+		Only the motor module (mod1) adds exploration noise ($\sigma=0.02$) even in hierarchical architecture.
+
+		\subsubsection{Conditions}
+
+			\begin{itemize}
+
+				\item H0-MB: Random Motor Babbling
+				\item H0-GB: Random Goal Babbling with a flat architecture learning $$M \rightarrow S_{Hand} \times S_{Stick_1} \times S_{Stick_2} \times S_{Object} \times S_{Boxes}$$
+				\item H0-TR: The same architecture but with active goal babbling (my version of SAGG-RIAC)
+				\item H1: Hierarchical architecture with Random Goal Babbling in each module, and choice of module that babbles based on interest ($\epsilon$-prop: probabilities proportional to interest but with $\epsilon=10\%$ of random choice).
+Choice of tool to use based on the maximum interest of the two modules that learn from the spaces of the tools to the object space, around the goal object point (competence progress on the k=10 NN).
+				\item H1-GR: same as H1 but the choice of module to babble is $\epsilon$-greedy with $\epsilon=0.1$
+				\item H1-CL: same as H1 but the choice of the tool to use is based on the maximum competence around the goal object point (competence of the NN)
+
+			\end{itemize}
+
+		%
+
+		\subsubsection{Measures}
+
+			Exploration of the different sensory spaces (number of reached cells in a discretization of the space divided by number of cells).
+
+		%
+
+	%
+
+%
+
 \section{Results}
+
+		\begin{figure*}[ht]
+			\centering
+			\subfloat[Hand]{\includegraphics[width=4.5cm]{./include/xp1-explo-hand.png}}
+			\subfloat[Tool]{\includegraphics[width=4.5cm]{./include/xp1-explo-stick_1.png}}
+			\subfloat[Object]{\includegraphics[width=4.5cm]{./include/xp1-explo-obj.png}}
+			\subfloat[Box]{\includegraphics[width=4.5cm]{./include/xp1-explo-box.png}}
+			\caption{Exploration of sensory spaces.}
+			\label{res_explo}
+		\end{figure*}
+
+		\begin{figure*}[ht]
+			\subfloat[]{\includegraphics[width=9cm]{./include/H1-log3-interests.png}}
+			\subfloat[]{\includegraphics[width=9cm]{./include/H1-log3-obj-explo.png}}
+			\caption{Condition H1. (a) Interests of each module. (b) Exploration of the object space: each dot is one point reached with the object at the end of one movement.}
+			\label{res_interests}
+		\end{figure*}
+
+		\begin{figure*}[ht]
+			\subfloat[H1]{\includegraphics[width=9cm]{./include/choice_mod4_H1.png}}
+			\subfloat[H1-CL]{\includegraphics[width=8.8cm]{./include/choice_mod4_H1-CL.png}}
+			\caption{Chosen tool depending on object goal position. Blue points: long stick choice. Red points: small stick choice.}
+			\label{res_choice}
+		\end{figure*}
 
@@
 
+	\subsection{H0 vs H1}
+
 	%
 
-\begin{figure}[ht]
-\begin{center}
-\fbox{CoGNiTiVe ScIeNcE}
-\end{center}
-\caption{This is a figure.} 
-\label{sample-figure}
-\end{figure}
+	\subsection{H1 vs H1-GR}
+
+	%
+
+	\subsection{H1 vs H1-CL}
+
+	%
+
+%
 
@@
 
-Place acknowledgments (including funding information) in a section at
-the end of the paper.
+%
 

### 2016-01-18 cogsci2016/paper.tex
results

@@
 	Bordeaux, France
-  \AND {\large \bf Pierre-Yves Oudeyer (pierre-yves.oudeyer@inria.fr} \\
+  \AND {\large \bf Pierre-Yves Oudeyer (pierre-yves.oudeyer@inria.fr)} \\
 	INRIA Bordeaux Sud-Ouest\\
@@
 			The robotic arm thus has 4 degrees of freedom represented by a vector in $[-1,1]^4$.
-			A trajectory of the arm will be represented as a sequence of such vectors.
+			A trajectory of the arm will be represented as a sequence of such vectors.\\
+
+		%
+
+		\subsubsection{Motor control}
+
+			We use Dynamical Movement Primitive \cite{ijspeert_dynamical_2013} to control the arm's movement as this framework permits the production of a diversity of arm's trajectories with few parameters.
+			Each of the $4$ arm's degrees-of-freedom (DOF) is controlled by a DMP with a starting and a goal position equal to the rest position of the joint.
+			Each DMP is parameterized by one weight on each of $3$ basis functions whose centers are distributed homogeneously throughout the movement duration.
+			The weights are bounded in the interval $[-200,200]$ (mapped to the standard interval $[-1,1]$) which allow each joint to fairly cover the interval $[-1,1]$ during the movement.
+			Each DMP outputs a series of $50$ positions that represents a sampling of the trajectory of one joint during the movement.		
+			The arm's movement is thus parameterized by $12$ weights which are represented by the motor space $M=[-1,1]^{12}$.\\
 
@@
 			Similarly, if the other end of a stick reaches the sphere (within $0.1$), the object will follow the end of the stick.
-			Ten boxes are static at positions $(-1, 0)$, $(-0.5, 1)$, $(1.1, 1.3)$ and $(1.6, 0)$ and have size $0.2$, 
-			so that the two boxes on the left can be reached by the two sticks, and the two boxes on the right can only be reached by the long stick.
+			Ten boxes have identifiers $1$ to $10$ and are static at positions $(-1.4, 0)$, $(-1.1, 1.1)$, $(0, 1.4)$, $(1.1, 1.1)$, $(1.4, 0)$, $(-0.9, 0)$, $(-0.6, 0.6)$, $(0, 0.9)$, $(0.6, 0.6)$ and $(0.9, 0)$ and have size $0.2$.
+			The first five boxes can only be reached with the long stick, and the other five can be reached by the two sticks.
 			At the end of the trial, the object is considered to be in one of the box if its center is in the box.\\
-
-		%
-
-		\subsubsection{Motor control}
-
-			We use Dynamical Movement Primitive \cite{ijspeert_dynamical_2013} to control the arm's movement as this framework permits the production of a diversity of arm's trajectories with few parameters.
-			Each of the $4$ arm's degrees-of-freedom (DOF) is controlled by a DMP with a starting and a goal position equal to the rest position of the joint.
-			Each DMP is parameterized by one weight on each of $3$ basis functions whose centers are distributed homogeneously throughout the movement duration.
-			The weights are bounded in the interval $[-200,200]$ (mapped to the standard interval $[-1,1]$) which allow each joint to fairly cover the interval $[-1,1]$ during the movement.
-			Each DMP outputs a series of $50$ positions that represents a sampling of the trajectory of one joint during the movement.		
-			The arm's movement is thus parameterized by $12$ weights which are represented by the motor space $M=[-1,1]^{12}$
 
@@
 			Similarly, the trajectory of the gripper is a sequence of $1$ or $-1$ depending whether the gripper is open or closed ($3$D).
-			For each box, the robot receives a $1$ if the object is in the box at the end of the movement, and $0$ otherwise ($4$D).			 
-			The sensory information thus contains $9$ values for the trajectory of the hand and gripper, $6$ for the trajectory of the end of each stick, $2$ for the end position of the object and $4$ for the boxes.
-			The sensory space has a total of $27$ dimensions.
+			The agent receives the identifier of the reached box if one of them has been reached, 0 otherwise.
+He also gets the minimal distance of the object (at the end of the movement) to the center a box, even if none have been reached.
+			%For each box, the robot receives a $1$ if the object is in the box at the end of the movement, and $0$ otherwise ($4$D).			 
+			The sensory information thus contains $9$ values for the trajectory of the hand and gripper ($S_{Hand}$), $6$ for the trajectory of the end of each stick ($S_{Stick_1}$ and $S_{Stick_2}$), $2$ for the end position of the object ($S_{Object}$) and $2$ for the boxes ($S_{Boxes}$).
+			The sensory space has a total of $25$ dimensions.
 
@@
 
-			We present here an architecture that represents sensorimotor information with a hierarchical structure.
+			We present here an architecture that represents sensorimotor information with a hierarchical structure in Fig. \ref{H1}.
+
+			Only the motor module (mod1) adds exploration noise ($\sigma=0.02$) even in hierarchical architecture. 
+			That was the key to have more efficient hierarchical exploration. 
+			Indeed, if all modules successively add exploration noise, few iterations succeed in touching the object. 
+			Alternatively, if the exploration noise is reduced, exploration is less efficient as in NN only the motor module will finally apply noise on known motor commands. 
+			With regression instead of NN, noise can instead be put only on the babbling module.
 
@@
 				\center
-				\input{include/H2.tikz}
+				\input{include/H1.tikz}
 				\caption{Hierarchy of sensorimotor models}
-				\label{H}					
+				\label{H1}					
 			\end{figure}
@@
 		NN, 100 iterations of Motor babbling and then 300000 iterations of the condition
-
-		Only the motor module (mod1) adds exploration noise ($\sigma=0.02$) even in hierarchical architecture.
 

### 2016-01-18 cogsci2016/paper.tex
results

@@
 
-\title{Curiosity-Driven Development of Tool Use Precursors}
+\title{Curiosity-Driven Development of Tool Use Precursors: a Robotic Model}
 
@@
 		We simulate a 2D robotic arm using tools to move an object into different boxes in the environment. 		
-		In each trial, we execute a motor command given by the agent, we evaluate its consequences on the sensory dimensions and we give him
-		this sensory feedback. Finally the environment is resetted to its intial state.
+		In each trial, we execute a motor trajectory given by the agent, we evaluate its consequences on the sensory dimensions and we give him
+		this sensory feedback. Finally the arm, tools and objects are resetted to their intial state.
 
 		The next sections precisely describe the different items of the environment and their interactions.	
-		See Fig. \ref{env} for an exemple of the state of the environment.
+		See Fig.\ref{env} for an exemple of the state of the environment.
 
@@
 
+			How competence and interest of modules is computed.
+
 			\begin{figure}[t]
@@
 
-		NN, 100 iterations of Motor babbling and then 300000 iterations of the condition
+		NN, $100$ iterations of Motor babbling and then $300000$ iterations of the condition. 10 trials per condition, mean and std provided.
 
@@
 
+	\paragraph{}
+	We measure the exploration of the different sensory spaces in the $6$ conditions each $5000$ iterations along the $300000$ iterations (Fig. \ref{res_explo}).
+	We provide statistical Mann-Whitney U test results of comparisons of the exploration at the end of the experiments in different pairs of conditions.
+	We first show that the Motor Babbling condition (H0-MB) quickly explores $S_{Hand}$ but explores badly the other sensory spaces, compared to the other conditions (STATS).
+	Then H0-GB and H0-Tr have similar exploration results (STATS maybe Tr better in Boxes).
+	Then H1-GR shows lower exploration of $S_{Hand}$, $S_{Stick_1}$ and $S_{Stick_2}$ than H0-GB and H0-Tr but higher exploration of $S_{Object}$ and $S_{Boxes}$ (STATS).
+	Also, H1-GR shows lower exploration of all spaces than H1 (STATS).
+	H1 shows lower exploration of $S_{Hand}$ than H0-GB and H0-Tr (STATS), similar (STATS?) exploration of $S_{Stick_1}$ and $S_{Stick_2}$ but higher exploration of $S_{Object}$ and $S_{Boxes}$ (STATS).
+	H1-CL vs H1 (STATS?).
+
 	\begin{figure*}[ht]
 		\centering
-			\subfloat[Hand]{\includegraphics[width=4.5cm]{./include/xp1-explo-hand.png}}
-			\subfloat[Tool]{\includegraphics[width=4.5cm]{./include/xp1-explo-stick_1.png}}
-			\subfloat[Object]{\includegraphics[width=4.5cm]{./include/xp1-explo-obj.png}}
-			\subfloat[Box]{\includegraphics[width=4.5cm]{./include/xp1-explo-box.png}}
+		\subfloat[$Hand$]{\includegraphics[width=4.5cm]{./include/xp1-explo-hand.png}}
+		\subfloat[$Stick_1$]{\includegraphics[width=4.5cm]{./include/xp1-explo-stick_1.png}}
+		\subfloat[$Stick_2$]{\includegraphics[width=4.5cm]{./include/xp1-explo-stick_2.png}}\\
+		\subfloat[$Object$]{\includegraphics[width=4.5cm]{./include/xp1-explo-obj.png}}
+		\subfloat[$Boxes$]{\includegraphics[width=4.5cm]{./include/xp1-explo-box.png}}
 		\caption{Exploration of sensory spaces.}
@@
 	\end{figure*}
+
+	\paragraph{}
+	Fig. \ref{res_interests} shows more details about one (randomly chosen) trial of the condition H1. 
+	We can see the interest of each module during the whole experiment.
+	The interests of modules 1, 2, 5 are almost stable, as the spaces of interests are high-dimensional and homogeneously reachable: a random exploration will find regions to learn more for more iterations than $300000$.
+	The interests of modules 3 and 6 increase abruptly when the object is touch by the corresponding tool.
+	An exemple of exploration of the $2$D space with the object is also provided in Fig. \ref{res_interests}(b) also corresponding to condition H1.
 
@@
 	\end{figure*}
+
+	\paragraph{}
+	Fig. \ref{res_choice} shows a comparison of the choice of tool to reach a given object goal position in the conditions H1 and H1-CL.
+	In those conditions, module $4$ learns a mapping between $S_{Object}$ and $S_{Boxes}$. 
+	When this module is babbling (give \# babbling in the 2 conditions: around $100000$), it chooses a random goal $s_b \in S_{Boxes}$ and infers the best object position $s_o$ to reach $s_b$.
+	To reach $s_o$, one of the tools ($Stick_1$ with module $3$ or $Stick_2$ with module $6$) has to be chosen. 
+	We plot all those choices, at position $s_o$ on a $2$D space, with color blue if $Stick_1$ was chosen and red if $Stick_2$ was chosen, with one plot for each of the two conditions.
+	We see (or soon will see in new plots, and maybe with smoothed stats along trials?) that in both conditions, 
+	goals that can only be reached with the long stick (the furthest) are actually chosen to be explored with the long stick.
+	However, goal that can be reached with both tools are more often chosen to be explored with the long stick in the interest-based choice of condition H1 than in competence-based choice of condition H1-CL.
 
@@
 
-	\subsection{H0 vs H1}
-
-	%
-
-	\subsection{H1 vs H1-GR}
+	\subsection{H0 vs H1-GR vs H1}
 
@@
 	%
+
+%
+
+\section{Conclusion}
 

### 2016-01-19 cogsci2016/paper.tex
explauto

@@
 
+		We describe in this section the different learning architectures used in the experiment.
+
 		\subsubsection{Explauto framework}
 
-			\cite{moulin-frier_explauto:_2014}
+			We use the Explauto autonomous exploration library \cite{moulin-frier_explauto:_2014} to easily define experiments with robots exploring their environment. 
+			In this framework, the agent explores a mapping between its given motor space $M$ and sensory space $S$, 
+			using a sensorimotor model that learns the mapping and an interest model that chooses which regions of the spaces to explore.
+			The sensorimotor model processes new information of the form ($m, s$) with $m \in M$ being the experimented motor parameters and $s \in S$ the received sensory feedback 
+			corresponding to that parameters. 
+			It provides forward predictions of probable $s$ given $m$ and inverse inference of a probable $m$ to reach a given $s$.
+			We use the simplest sensorimotor model, the nearest neighbor algorithm 
+			that performs the prediction of $s$ given $m$ using the nearest neighbor of $m$ in $M$ in the database of the previous experiments and returning its sensory part. 
+			The inverse inference is computed as the motor part of the nearest neighbor in $S$ of the given $s$, but with some exploration noise to allow novel motor parameters to be explored.
 
-		%
-
-		\subsubsection{Goal Babbling}
-
-		%
-
-		\subsubsection{SAGG-RIAC}
-
-			\cite{baranes_active_2013}
+			The agent also needs an interest model that chooses which regions of the motor or sensory space to explore.
+			If the agent chooses goals in the motor space and explores them it is called Motor Babbling, and if it chooses the goals to explore in the sensory space, this is Goal Babbling.
+			To choose the goals in this space of interest, different strategies are possible. 
+			The simplest one is to draw random goals in this space, but strategies based on the learning progress in different regions of the space have been shown more efficient in [ref].
+			This strategies are called active as the agent autonomously drives its exploration towards regions of the space that are both reachable and learnable. 
+			We use the SAGG-RIAC architecture \cite{baranes_active_2013} where the space of interest is the sensory space (Goal Babbling) and that incrementally splits this space into subregions where the learning progress
+			is different.
 

### 2016-01-20 cogsci2016/paper.tex
eps

@@
 			is different. 
+			The learning progress is here computed as the absolute derivative of the reaching competence. 
+			This competence associated to a sensory goal is minus the distance between the goal and the sensory point.
 
@@
 		\centering
-		\subfloat[$Hand$]{\includegraphics[width=4.5cm]{./include/xp1-explo-hand.png}}
-		\subfloat[$Stick_1$]{\includegraphics[width=4.5cm]{./include/xp1-explo-stick_1.png}}
-		\subfloat[$Stick_2$]{\includegraphics[width=4.5cm]{./include/xp1-explo-stick_2.png}}\\
-		\subfloat[$Object$]{\includegraphics[width=4.5cm]{./include/xp1-explo-obj.png}}
-		\subfloat[$Boxes$]{\includegraphics[width=4.5cm]{./include/xp1-explo-box.png}}
+		\subfloat{\includegraphics[width=14cm]{./include/xp1-explo-legend.eps}}\\
+		\vspace{-0.3cm}
+		\subfloat[$Hand$]{\includegraphics[width=3.5cm]{./include/xp1-explo-hand.eps}}
+		\subfloat[$Stick_1$]{\includegraphics[width=3.5cm]{./include/xp1-explo-stick_1.eps}}
+		\subfloat[$Stick_2$]{\includegraphics[width=3.5cm]{./include/xp1-explo-stick_2.eps}}
+		\subfloat[$Object$]{\includegraphics[width=3.5cm]{./include/xp1-explo-obj.eps}}
+		\subfloat[$Boxes$]{\includegraphics[width=3.5cm]{./include/xp1-explo-box.eps}}
 		\caption{Exploration of sensory spaces.}

### 2016-01-21 cogsci2016/paper.tex
results
intro

@@
 \usepackage{apacite}
+
+%\usepackage{hyperref}
 
@@
 
-	Development of tool use \cite{guerin2013survey}, precursors of tool use: behavior without objects, behavior with one object, interaction of objects.	
-	Grounding of representation and planning based on a large amount of experiences. 	
-	Seemless progression between the successives phases as overlapping waves. 	
-	Ongoing process of upgrading representations.	
-	Developmental trajectories.
+	\paragraph{}
+	Development of tool use: different properties \cite{guerin2013survey} (cite others?). 
+	List of some properties: grounding of representation and planning based on a large amount of experiences, ongoing process of upgrading representations (others?).
+	In that paper we will focus on one important property in the development of precursors of tool use which is the seemless progression 
+	between successives phases of behavior with tools and objects which are called overlapping waves [Siegler]. 
+	One behavioral description of the successives phases differentiate three phases \cite{guerin2013survey}.
+	In the first phase the babies engage mostly in behavior without objects (babbling), in the second phase their behavior has shifted towards interaction with one object, and then interaction between objects.
+	[more details: months, experiments]
+
+	\paragraph{}
+	We hypothesize that several mechanisms play a role in the structure of this behavioral progression and in particular 
+	1) the intrinsic motivation to explore as a self-regulation of the learning growth of complexity, and 
+	2) the structure of the representation used to encode sensorimotor experience.
 
@@
 
+	\paragraph{}
+	We will study aspects of these hypothesis leveraging and extending models of curiosity-driven learning of sensorimotor models to the exploration of given hierarchies of sensorimotor models.
+	In such hierarchies, parts of the sensory space (e.g. the position of the hand) can be used as a motor space by another higher-level model to explore other sensory spaces.
+	We do not study some other important factors of the development of tool use: the autonomous building and evolution of the hierarchy of models but we consider it given to a learning agent.
+	We also do not address the question of the role of social guidance.
+
+	Related work
 	Curiosity-driven modelling work, emergence of developmental trajectories.
@@
 	\cite{schmerlinggoal}
+	\cite{forestier2015}
+	\cite{unifying}
 
@@
 	\cite{}
+
+	Along with this paper we provide open-source Python code\footnote{Source code and notebooks available as a Github repository at \url{https://github.com/sebastien-forestier/CogSci2016}} 
+	with iPython/Jupyter notebooks that explain how to reproduce the experiments and analysis.
 
@@
 			How competence and interest of modules is computed.
+
+			\begin{figure}[t]
+				\center
+				\input{include/F.tikz}
+				\caption{Flat architecture}
+				\label{F}					
+			\end{figure}
 

### 2016-01-25 cogsci2016/paper.tex
figs
new results

@@
 	List of some properties: grounding of representation and planning based on a large amount of experiences, ongoing process of upgrading representations (others?).
-	In that paper we will focus on one important property in the development of precursors of tool use which is the seemless progression 
+	In that paper we will focus on one important property in the development of precursors of tool use which is the seamless progression 
 	between successives phases of behavior with tools and objects which are called overlapping waves [Siegler]. 
@@
 			\label{env}
+		\end{figure}
+
+		\begin{figure}[h]
+			\centering
+			\subfloat{\includegraphics[width=2.8cm]{./include/mvt-16.pdf}}
+			\subfloat{\includegraphics[width=2.8cm]{./include/mvt-32.pdf}}
+			\subfloat{\includegraphics[width=2.8cm]{./include/mvt-49.pdf}}\\
+			\hspace{-0.4cm}
+			\subfloat{\includegraphics[width=8.8cm]{./include/dmp.pdf}}
+			\caption{Exemple of one mouvement. Top: position of the arm at time steps 17, 33 and 50 along the $50$ steps movement. Bottom: value of the four Dynamical Movement Primitives during the movement.}
+			\label{mvt}
 		\end{figure}
@@
 
-				\item H0-MB: Random Motor Babbling
-				\item H0-GB: Random Goal Babbling with a flat architecture learning $$M \rightarrow S_{Hand} \times S_{Stick_1} \times S_{Stick_2} \times S_{Object} \times S_{Boxes}$$
-				\item H0-TR: The same architecture but with active goal babbling (my version of SAGG-RIAC)
-				\item H1: Hierarchical architecture with Random Goal Babbling in each module, and choice of module that babbles based on interest ($\epsilon$-prop: probabilities proportional to interest but with $\epsilon=10\%$ of random choice).
-Choice of tool to use based on the maximum interest of the two modules that learn from the spaces of the tools to the object space, around the goal object point (competence progress on the k=10 NN).
-				\item H1-GR: same as H1 but the choice of module to babble is $\epsilon$-greedy with $\epsilon=0.1$
-				\item H1-CL: same as H1 but the choice of the tool to use is based on the maximum competence around the goal object point (competence of the NN)
+				\item F-RmB: Random Motor Babbling with a flat architecture learning $M \rightarrow S_{Hand} \times S_{Stick_1} \times S_{Stick_2} \times S_{Object} \times S_{Boxes}$
+				\item F-RGB: Flat architecture, Random Goal Babbling
+				\item F-AGB: The same architecture but with active goal babbling (my version of SAGG-RIAC)
+				\item H-RGB-P-AMB: Hierarchical architecture with Random Goal Babbling in each module, and choice of module that babbles based on interest ($\epsilon$-prop: probabilities proportional to interest but with $\epsilon=10\%$ of random choice).
+Choice of tool to use based on the maximum competence of the two modules to reach the goal object point.
+				\item H-RGB-GR-AMB: same as H-RGB-P-AMB but the choice of module to babble is $\epsilon$-greedy with $\epsilon=0.1$
+				\item H-RGB-P-AMB-PGITC: same as H-RGB-P-AMB but the choice of the tool to use is based on the interest (global) of the two modules ($\epsilon$-prop).
 
@@
 	\begin{figure*}[ht]
-		\subfloat[]{\includegraphics[width=9cm]{./include/H1-log3-interests.png}}
-		\subfloat[]{\includegraphics[width=9cm]{./include/H1-log3-obj-explo.png}}
+		\centering
+		\subfloat[]{\includegraphics[width=9cm]{./include/H-RGB-P-AMB-log9-interests-100000.pdf}}
+		\subfloat[]{\includegraphics[width=9cm]{./include/H-RGB-P-AMB-log9-obj-explo.pdf}}
 		\caption{Condition H1. (a) Interests of each module. (b) Exploration of the object space: each dot is one point reached with the object at the end of one movement.}
 		\label{res_interests}
+	\end{figure*}
+
+	\begin{figure*}[ht]
+		\centering
+		\subfloat[H-RGB-GR-AMB]{\includegraphics[width=8cm]{./include/H-RGB-GR-AMB-log15-events-100000.pdf}}
+		\subfloat[H-RGB-P-AMB]{\includegraphics[width=8cm]{./include/H-RGB-P-AMB-log8-events-100000.pdf}}
+		\caption{Behavioral measure}
+		\label{res_ow}
 	\end{figure*}
@@
 	\begin{figure*}[ht]
-		\subfloat[H1]{\includegraphics[width=9cm]{./include/choice_mod4_H1.png}}
-		\subfloat[H1-CL]{\includegraphics[width=8.8cm]{./include/choice_mod4_H1-CL.png}}
+		\subfloat[H-RGB-P-AMB]{\includegraphics[width=9cm]{./include/H-RGB-P-AMB-log9-choice_mod4.png}}
+		\subfloat[H-RGB-P-AMB-PGITC]{\includegraphics[width=8.8cm]{./include/H-RGB-P-AMB-PGITC-log3-choice_mod4.png}}
 		\caption{Chosen tool depending on object goal position. Blue points: long stick choice. Red points: small stick choice.}
@@
 
-	\subsection{H0 vs H1-GR vs H1}
+	\subsection{F-AGB vs H-RGB-P-AMB vs H-RGB-GR-AMB}
 
@@
 
-	\subsection{H1 vs H1-CL}
+	\subsection{H-RGB-P-AMB vs H-RGB-P-AMB-PGITC}
 

### 2016-01-26 cogsci2016/paper.tex
new results
significativity

@@
 			\centering
-			\includegraphics[width=8cm]{./include/tools.png}
-			\caption{Play Environment}
-			\label{env}
-		\end{figure}
-
-		\begin{figure}[h]
-			\centering
+			\hspace{-0.73cm}
+			\vspace{-0.71cm}
+			\includegraphics[width=9.12cm]{./include/tools.pdf}
 			\subfloat{\includegraphics[width=2.8cm]{./include/mvt-16.pdf}}
@@
 			\subfloat{\includegraphics[width=2.8cm]{./include/mvt-49.pdf}}\\
-			\hspace{-0.4cm}
+			\hspace{-0.42cm}
 			\subfloat{\includegraphics[width=8.8cm]{./include/dmp.pdf}}
-			\caption{Exemple of one mouvement. Top: position of the arm at time steps 17, 33 and 50 along the $50$ steps movement. Bottom: value of the four Dynamical Movement Primitives during the movement.}
-			\label{mvt}
+			\caption{Top: a state of the environment. Middle: position of the arm at time steps 17, 33 and 50 along the $50$ steps movement. Bottom: value of the four DMPs during the movement.}
+			\label{env}
 		\end{figure}
@@
 	We provide statistical Mann-Whitney U test results of comparisons of the exploration at the end of the experiments in different pairs of conditions.
-	We first show that the Motor Babbling condition (H0-MB) quickly explores $S_{Hand}$ but explores badly the other sensory spaces, compared to the other conditions (STATS).
-	Then H0-GB and H0-Tr have similar exploration results (STATS maybe Tr better in Boxes).
-	Then H1-GR shows lower exploration of $S_{Hand}$, $S_{Stick_1}$ and $S_{Stick_2}$ than H0-GB and H0-Tr but higher exploration of $S_{Object}$ and $S_{Boxes}$ (STATS).
-	Also, H1-GR shows lower exploration of all spaces than H1 (STATS).
-	H1 shows lower exploration of $S_{Hand}$ than H0-GB and H0-Tr (STATS), similar (STATS?) exploration of $S_{Stick_1}$ and $S_{Stick_2}$ but higher exploration of $S_{Object}$ and $S_{Boxes}$ (STATS).
-	H1-CL vs H1 (STATS?).
+	We first show that the Motor Babbling condition (F-RmB) quickly explores $S_{Hand}$ and explores badly $S_{Object}$ and $S_{Boxes}$, compared to the other conditions ($p<0.0001$).
+	Then F-RGB and F-AGB don't have significantly different exploration results in any space ($p>0.05$), 
+	and explore less $S_{Stick_1}$, $S_{Stick_2}$, $S_{Object}$ and $S_{Boxes}$ than H-RGB-P-AMB condition ($p<0.05$).
+	Also, H-RGB-GR-AMB shows lower exploration of $S_{Hand}$, $S_{Stick_2}$ and $S_{Object}$ than H-RGB-P-AMB ($p<0.05$).
+	Condition H-RGB-P-AMB-PGITC explores more $S_{Hand}$ ($p<0.01$) and $S_{Stick_2}$ ($p<0.05$) than condition H-RGB-P-AMB.
 
@@
 		\centering
-		\subfloat{\includegraphics[width=14cm]{./include/xp1-explo-legend.eps}}\\
+		\subfloat{\includegraphics[width=14cm]{./include/xp1-explo-legend.pdf}}\\
 		\vspace{-0.3cm}
-		\subfloat[$Hand$]{\includegraphics[width=3.5cm]{./include/xp1-explo-hand.eps}}
-		\subfloat[$Stick_1$]{\includegraphics[width=3.5cm]{./include/xp1-explo-stick_1.eps}}
-		\subfloat[$Stick_2$]{\includegraphics[width=3.5cm]{./include/xp1-explo-stick_2.eps}}
-		\subfloat[$Object$]{\includegraphics[width=3.5cm]{./include/xp1-explo-obj.eps}}
-		\subfloat[$Boxes$]{\includegraphics[width=3.5cm]{./include/xp1-explo-box.eps}}
+		\subfloat[$Hand$]{\includegraphics[width=3.5cm]{./include/xp1-explo-hand.pdf}}
+		\subfloat[$Stick_1$]{\includegraphics[width=3.5cm]{./include/xp1-explo-stick_1.pdf}}
+		\subfloat[$Stick_2$]{\includegraphics[width=3.5cm]{./include/xp1-explo-stick_2.pdf}}
+		\subfloat[$Object$]{\includegraphics[width=3.5cm]{./include/xp1-explo-obj.pdf}}
+		\subfloat[$Boxes$]{\includegraphics[width=3.5cm]{./include/xp1-explo-box.pdf}}
 		\caption{Exploration of sensory spaces.}

### 2016-01-26 cogsci2016/paper.tex
results description

@@
 \usepackage{tikz}
-\usetikzlibrary{arrows,shapes,snakes,automata,backgrounds,petri}
+\usetikzlibrary{arrows,shapes,snakes,automata,backgrounds,petri, fit}
 
@@
 			\hspace{-0.73cm}
-			\vspace{-0.71cm}
+			\vspace{-0.59cm}
 			\includegraphics[width=9.12cm]{./include/tools.pdf}
@@
 
-			We present here an architecture that represents sensorimotor information with a hierarchical structure in Fig. \ref{H1}.
+			We present here an architecture that represents sensorimotor information with a hierarchical structure in Fig. \ref{Architectures}.
 
@@
 				\input{include/F.tikz}
-				\caption{Flat architecture}
-				\label{F}					
-			\end{figure}
-
-			\begin{figure}[t]
-				\center
+				\vspace{-0.25cm}
 				\input{include/H1.tikz}
-				\caption{Hierarchy of sensorimotor models}
-				\label{H1}					
+				\vspace{-0.5cm}
+				\caption{Architectures. Top: flat. Bottom: hierarchical.}
+				\label{Architectures}					
 			\end{figure}
@@
 
-		NN, $100$ iterations of Motor babbling and then $300000$ iterations of the condition. 10 trials per condition, mean and std provided.
+		Nearest Neighbors, $100$ iterations of Motor babbling and then $100000$ iterations of the condition. 10 trials per condition, mean and std provided.
 
@@
 
-			Exploration of the different sensory spaces (number of reached cells in a discretization of the space divided by number of cells).
+			We provide a measure of the different types of behaviors with the sticks and the object during exploration. 
+			We categorize the behaviors into three types.
+			In the first category ($hand$) are mouvements of the arm that did not grab any stick and thus not moved the out-of-reached object.
+			The second category ($stick$) are mouvements that did grab one of the two sticks but did not touch the object with it.
+			The third category ($object$) contains the mouvements where both a stick was grabbed and the object was moved by the stick.
+
+			Also, for each condition we measure the total exploration of the different sensory spaces during training. 
+			The exploration of the hand, sticks and object spaces is defined as the number of reached cells 
+			in a $100\times100$ discretization of the (X,Y) space of the position at timestep $50$ (end of movement).
+			The exploration of the boxes is the number of boxes that have been filled with the object during training.
 
@@
 	\paragraph{}
-	We measure the exploration of the different sensory spaces in the $6$ conditions each $5000$ iterations along the $300000$ iterations (Fig. \ref{res_explo}).
+	Fig. \ref{res_interests} shows details about one trial of the condition H-RGB-P-AMB. 
+	We can see the interest of each module during the whole experiment.
+	The interests of modules 2 and 5 increase abruptly once the arm succeeded in grabbing the corresponding stick.
+	Following that, the interests of modules 3 and 6 also increase abruptly when the object has been touched by the corresponding stick.
+	An exemple of exploration of the $2$D space with the object is also provided in Fig. \ref{res_interests}(b) corresponding to the same condition.
+
+	\begin{figure*}[ht]
+		\centering
+		\subfloat[]{\includegraphics[width=9cm]{./include/H-RGB-P-AMB-log9-interests-100000.pdf}}
+		\subfloat[]{\includegraphics[width=9cm]{./include/H-RGB-P-AMB-log9-obj-explo.pdf}}
+		\caption{Condition H-RGB-P-AMB. (a) Interests of each module. (b) Exploration of the object space: each dot is one point reached with the object at the end of one movement.}
+		\label{res_interests}
+	\end{figure*}
+
+	\paragraph{}
+	Fig. \ref{res_ow} shows the proportion of the three categories of behavior along the $100000$ iterations for conditions H-RGB-GR-AMB and H-RGB-P-AMB.
+
+	\begin{figure*}[ht]
+		\centering
+		\subfloat[H-RGB-GR-AMB]{\includegraphics[width=8cm]{./include/H-RGB-GR-AMB-log15-events-100000.pdf}}
+		\subfloat[H-RGB-P-AMB]{\includegraphics[width=8cm]{./include/H-RGB-P-AMB-log8-events-100000.pdf}}
+		\caption{Behavioral measure}
+		\label{res_ow}
+	\end{figure*}
+
+	\paragraph{}
+	Fig. \ref{res_explo} shows the total exploration of the different sensory spaces for each condition.
 	We provide statistical Mann-Whitney U test results of comparisons of the exploration at the end of the experiments in different pairs of conditions.
-	We first show that the Motor Babbling condition (F-RmB) quickly explores $S_{Hand}$ and explores badly $S_{Object}$ and $S_{Boxes}$, compared to the other conditions ($p<0.0001$).
+	Firstly, the Motor Babbling condition (F-RmB) have more explored $S_{Hand}$ and less $S_{Object}$ and $S_{Boxes}$ compared to the other conditions ($p<0.0001$).
 	Then F-RGB and F-AGB don't have significantly different exploration results in any space ($p>0.05$), 
@@
 		\centering
-		\subfloat{\includegraphics[width=14cm]{./include/xp1-explo-legend.pdf}}\\
+		\includegraphics[width=14cm]{./include/xp1-explo-legend.pdf}\\
 		\vspace{-0.3cm}
@@
 		\label{res_explo}
-	\end{figure*}
-
-	\paragraph{}
-	Fig. \ref{res_interests} shows more details about one (randomly chosen) trial of the condition H1. 
-	We can see the interest of each module during the whole experiment.
-	The interests of modules 1, 2, 5 are almost stable, as the spaces of interests are high-dimensional and homogeneously reachable: a random exploration will find regions to learn more for more iterations than $300000$.
-	The interests of modules 3 and 6 increase abruptly when the object is touch by the corresponding tool.
-	An exemple of exploration of the $2$D space with the object is also provided in Fig. \ref{res_interests}(b) also corresponding to condition H1.
-
-	\begin{figure*}[ht]
-		\centering
-		\subfloat[]{\includegraphics[width=9cm]{./include/H-RGB-P-AMB-log9-interests-100000.pdf}}
-		\subfloat[]{\includegraphics[width=9cm]{./include/H-RGB-P-AMB-log9-obj-explo.pdf}}
-		\caption{Condition H1. (a) Interests of each module. (b) Exploration of the object space: each dot is one point reached with the object at the end of one movement.}
-		\label{res_interests}
-	\end{figure*}
-
-	\begin{figure*}[ht]
-		\centering
-		\subfloat[H-RGB-GR-AMB]{\includegraphics[width=8cm]{./include/H-RGB-GR-AMB-log15-events-100000.pdf}}
-		\subfloat[H-RGB-P-AMB]{\includegraphics[width=8cm]{./include/H-RGB-P-AMB-log8-events-100000.pdf}}
-		\caption{Behavioral measure}
-		\label{res_ow}
 	\end{figure*}

### 2016-01-26 cogsci2016/paper.tex
results 100

@@
 			The 2D robotic arm has 3 joints plus a gripper located at the end-effector.
-			Each joint can rotate from $-\pi~rad$ to $\pi~rad$ around its initial position, mapped to a standard interval of $[-1,1]$.
+			Each joint can rotate from $-\pi~rad$ to $\pi~rad$ around its resting position, mapped to a standard interval of $[-1,1]$.
 			The length of the 3 parts of the arm are $0.5$, $0.3$ and $0.2$ so the total length of the arm is $1$ unit.
-			The initial position of the arm is vertical with each joint at $0~rad$ and its base is fixed at position $[0, 0]$.
-			The gripper $g$ has 2 possible positions: \textit{open} ($g \geq 0$) and \textit{closed} ($g < 0$) and its initial position is \textit{open} (with $g = 0$).
+			The resting position of the arm is vertical with each joint at $0~rad$ and its base is fixed at position $[0, 0]$.
+			The gripper $g$ has 2 possible positions: \textit{open} ($g \geq 0$) and \textit{closed} ($g < 0$) and its resting position is \textit{open} (with $g = 0$).
 			The robotic arm thus has 4 degrees of freedom represented by a vector in $[-1,1]^4$.
@@
 			A long stick of length $0.6$ is located on the left of the arm, with initial position $(-0.75, 0.25)$ and initial angle $\frac{3\pi}{4}$ from the horizontal line as in Fig. \ref{env}.			
-			If the gripper closes near the end of one of the sticks (closer than $0.1$), it is considered grasped and will follow the gripper's position and the angle of the arm's last part until the gripper opens.
+			If the gripper is closed near the end of one of the sticks (closer than $0.1$), it is considered grasped and will follow the gripper's position and the angle of the arm's last part until the gripper opens.
 			Similarly, if the other end of a stick reaches the sphere (within $0.1$), the object will follow the end of the stick.
@@
 			The trajectory of the hand and of the end point of the sticks are represented by sequences of x and y positions at different time points: 
-			steps $12$, $25$, $37$ during the movement of $50$ steps ($6$D for the hand and for each stick).
+			steps $17$, $33$, $50$ during the movement of $50$ steps ($6$D for the hand and for each stick).
 			Similarly, the trajectory of the gripper is a sequence of $1$ or $-1$ depending whether the gripper is open or closed ($3$D).
@@
 
-		Nearest Neighbors, $100$ iterations of Motor babbling and then $100000$ iterations of the condition. 10 trials per condition, mean and std provided.
+		Nearest Neighbors, $100$ iterations of Motor babbling and then $100000$ iterations of the condition. $100$ trials per condition.
 
@@
 	Firstly, the Motor Babbling condition (F-RmB) have more explored $S_{Hand}$ and less $S_{Object}$ and $S_{Boxes}$ compared to the other conditions ($p<0.0001$).
-	Then F-RGB and F-AGB don't have significantly different exploration results in any space ($p>0.05$), 
-	and explore less $S_{Stick_1}$, $S_{Stick_2}$, $S_{Object}$ and $S_{Boxes}$ than H-RGB-P-AMB condition ($p<0.05$).
-	Also, H-RGB-GR-AMB shows lower exploration of $S_{Hand}$, $S_{Stick_2}$ and $S_{Object}$ than H-RGB-P-AMB ($p<0.05$).
-	Condition H-RGB-P-AMB-PGITC explores more $S_{Hand}$ ($p<0.01$) and $S_{Stick_2}$ ($p<0.05$) than condition H-RGB-P-AMB.
+	Then, F-RGB explores all spaces less than H-RGB-RMB condition ($p<0.01$).
+	Also, H-RGB-GR-AMB shows lower exploration all spaces than H-RGB-P-AMB ($p<0.01$).
+	Condition H-RGB-P-AMB-PGITC explores more $S_{Stick_2}$ ($p<0.05$) than condition H-RGB-P-AMB, and difference is not significant in other spaces.
 
@@
 	\paragraph{}
-	Fig. \ref{res_choice} shows a comparison of the choice of tool to reach a given object goal position in the conditions H1 and H1-CL.
+	Fig. \ref{res_choice} shows a comparison of the choice of tool to reach a given object goal position in the conditions H-RGB-P-AMB and H-RGB-P-AMB-PGITC.
 	In those conditions, module $4$ learns a mapping between $S_{Object}$ and $S_{Boxes}$. 
-	When this module is babbling (give \# babbling in the 2 conditions: around $100000$), it chooses a random goal $s_b \in S_{Boxes}$ and infers the best object position $s_o$ to reach $s_b$.
-	To reach $s_o$, one of the tools ($Stick_1$ with module $3$ or $Stick_2$ with module $6$) has to be chosen. 
-	We plot all those choices, at position $s_o$ on a $2$D space, with color blue if $Stick_1$ was chosen and red if $Stick_2$ was chosen, with one plot for each of the two conditions.
-	We see (or soon will see in new plots, and maybe with smoothed stats along trials?) that in both conditions, 
-	goals that can only be reached with the long stick (the furthest) are actually chosen to be explored with the long stick.
+	When this module is babbling, it chooses a random goal $s_b \in S_{Boxes}$ and infers the best object position $s_o$ to reach $s_b$.
+	To reach $s_o$, one of the tools ($Stick_1$ with module $3$ or $Stick_2$ with module $6$) is chosen. 
+	We plot all those choices, at position $s_o$ on a $2$D space, with color blue if $Stick_1$ was chosen and red if $Stick_2$ was chosen, in one figure for each of the two conditions.
+	We can see two very different choice structures.
 	However, goal that can be reached with both tools are more often chosen to be explored with the long stick in the interest-based choice of condition H1 than in competence-based choice of condition H1-CL.

### 2016-01-27 cogsci2016/paper.tex
Flat architectures

@@
 
-	\paragraph{}
 	We hypothesize that several mechanisms play a role in the structure of this behavioral progression and in particular 
@@
 
-	\paragraph{}
 	We will study aspects of these hypothesis leveraging and extending models of curiosity-driven learning of sensorimotor models to the exploration of given hierarchies of sensorimotor models.
@@
 	Curiosity-driven modelling work, emergence of developmental trajectories.
-	\cite{oudeyer_intrinsic_2007} 
+	%\cite{oudeyer_intrinsic_2007} 
 	\cite{oudeyer_what_2007}
-	\cite{flow}
+	%\cite{flow}
 	\cite{sch}
@@
 	\cite{moulin-frier_explauto:_2014}
-	\cite{baranes2010intrinsically}
-	\cite{riac}
+	%\cite{baranes2010intrinsically}
+	%\cite{riac}
 	\cite{baranes_active_2013}
@@
 	\cite{metzen2013}
-	\cite{horde}
-	\cite{mugan}
+	%\cite{horde}
+	%\cite{mugan}
 	\cite{vig}
@@
 		this sensory feedback. Finally the arm, tools and objects are resetted to their intial state.
-
 		The next sections precisely describe the different items of the environment and their interactions.	
-		See Fig.\ref{env} for an exemple of the state of the environment.
+		See Fig.\ref{env} for an exemple state of the environment.
 
@@
 			\subfloat{\includegraphics[width=8.8cm]{./include/dmp.pdf}}
-			\caption{Top: a state of the environment. Middle: position of the arm at time steps 17, 33 and 50 along the $50$ steps movement. Bottom: value of the four DMPs during the movement.}
+			\caption{Top: a state of the environment. Middle: position of the arm at time steps $17$, $33$ and $50$ along the $50$ steps movement. Bottom: value of the four DMPs during the movement.}
 			\label{env}
@@
 
-			The 2D robotic arm has 3 joints plus a gripper located at the end-effector.
+			The 2D robotic arm has $3$ joints plus a gripper located at the end-effector.
 			Each joint can rotate from $-\pi~rad$ to $\pi~rad$ around its resting position, mapped to a standard interval of $[-1,1]$.
-			The length of the 3 parts of the arm are $0.5$, $0.3$ and $0.2$ so the total length of the arm is $1$ unit.
+			The length of the $3$ segments of the arm are $0.5$, $0.3$ and $0.2$ so the total length of the arm is $1$ unit.
 			The resting position of the arm is vertical with each joint at $0~rad$ and its base is fixed at position $[0, 0]$.
@@
 			The robotic arm thus has 4 degrees of freedom represented by a vector in $[-1,1]^4$.
-			A trajectory of the arm will be represented as a sequence of such vectors.\\
+			A trajectory of the arm will be represented as a sequence of such vectors.
 
@@
 
-			A yellow sphere can be moved into one of the 4 fixed squared boxes. 
+			A yellow sphere can be moved into one of ten fixed squared boxes. 
 			The initial position of the sphere is $(0, 1.2)$ and is thus unreachable directly with the gripper.
-			One of two sticks can be grasped in order to reach the object.
-			A small stick of length $0.3$ is located on the right of the arm, with initial position $(0.75, 0.25)$ and initial angle $\frac{\pi}{4}$ from the horizontal line.
-			A long stick of length $0.6$ is located on the left of the arm, with initial position $(-0.75, 0.25)$ and initial angle $\frac{3\pi}{4}$ from the horizontal line as in Fig. \ref{env}.			
-			If the gripper is closed near the end of one of the sticks (closer than $0.1$), it is considered grasped and will follow the gripper's position and the angle of the arm's last part until the gripper opens.
-			Similarly, if the other end of a stick reaches the sphere (within $0.1$), the object will follow the end of the stick.
-			Ten boxes have identifiers $1$ to $10$ and are static at positions $(-1.4, 0)$, $(-1.1, 1.1)$, $(0, 1.4)$, $(1.1, 1.1)$, $(1.4, 0)$, $(-0.9, 0)$, $(-0.6, 0.6)$, $(0, 0.9)$, $(0.6, 0.6)$ and $(0.9, 0)$ and have size $0.2$.
-			The first five boxes can only be reached with the long stick, and the other five can be reached by the two sticks.
-			At the end of the trial, the object is considered to be in one of the box if its center is in the box.\\
+			Two sticks can be grasped in order to reach the object.
+			A small stick of length $0.3$ is located at position $(0.75, 0.25)$ with initial angle $\frac{\pi}{4}$ from the horizontal line.
+			A long stick of length $0.6$ is located at position $(-0.75, 0.25)$ with initial angle $\frac{3\pi}{4}$ as in Fig. \ref{env}.			
+			If the gripper is closed near the handle of one stick (closer than $0.2$), it is considered grasped and will follow the gripper's position and the angle of the arm's last segment until the gripper opens.
+			Similarly, if the other end of a stick reaches the sphere (within $0.1$), the sphere will follow the end of the stick.
+			The ten boxes (identified from $1$ to $10$) are static and have size $0.2$.
+			Boxes $1$ to $5$ can only be reached with the long stick, and the other five boxes can be reached with both sticks.
+			At the end of the mouvement, the object is considered to be in one of the box if its center is in the box.
 
@@
 			At the end of the movement, the robot gets sensory feedback from the different items of the environment.
-			It gets the trajectory of its hand and gripper, the trajectory of the end of the sticks, 
-			the end position of the object, and whether the object is in each box.		
-			The trajectory of the hand and of the end point of the sticks are represented by sequences of x and y positions at different time points: 
-			steps $17$, $33$, $50$ during the movement of $50$ steps ($6$D for the hand and for each stick).
-			Similarly, the trajectory of the gripper is a sequence of $1$ or $-1$ depending whether the gripper is open or closed ($3$D).
-			The agent receives the identifier of the reached box if one of them has been reached, 0 otherwise.
-He also gets the minimal distance of the object (at the end of the movement) to the center a box, even if none have been reached.
-			%For each box, the robot receives a $1$ if the object is in the box at the end of the movement, and $0$ otherwise ($4$D).			 
-			The sensory information thus contains $9$ values for the trajectory of the hand and gripper ($S_{Hand}$), $6$ for the trajectory of the end of each stick ($S_{Stick_1}$ and $S_{Stick_2}$), $2$ for the end position of the object ($S_{Object}$) and $2$ for the boxes ($S_{Boxes}$).
-			The sensory space has a total of $25$ dimensions.
+			It gets the trajectory of the gripper ($S_{Hand}$), the trajectory of the end of the sticks ($S_{Stick_1}$ and $S_{Stick_2}$), 
+			the position of the object at the end of the mouvement ($S_{Object}$), and whether the object is in a box at the end of the mouvement and the distance between the object and the nearest box ($S_{Boxes}$).
+			The trajectory of the gripper is represented as the $x$ and $y$ positions and the aperture ($1$ or $-1$) of the gripper at $3$ time points: 
+			steps $17$, $33$, $50$ during the movement of $50$ steps ($9$D).
+			Similarly, the trajectories of the end points of the sticks are $3$-points sequences of $x$ and $y$ positions ($6$D for each stick).
+			The agent receives the identifier (from $1$ to $10$) of the reached box if one of them has been reached by the sphere, 0 otherwise. 
+			He also gets the minimal distance of the object (at the end of the movement) to the center of a box, even if none have been reached.			 
+			The sensory information thus contains $9$ values for the trajectory of the gripper, $6$ for the trajectory of the end of each stick, $2$ for the end position of the object and $2$ for the boxes.
+			The total sensory space $S$ has $25$ dimensions.
 
@@
 
-		We describe in this section the different learning architectures used in the experiment.
+		\paragraph{}
+		The problem settings for the learning agent is to explore its sensorimotor space by iteratively choosing motor parameters that represents arm trajectories and receiving sensory feedback.
+		In this section we describe the different learning architectures that we will compare in the experiment.
 
-		\subsubsection{Explauto framework}
+		\subsubsection{Flat architectures}
 
-			We use the Explauto autonomous exploration library \cite{moulin-frier_explauto:_2014} to easily define experiments with robots exploring their environment. 
-			In this framework, the agent explores a mapping between its given motor space $M$ and sensory space $S$, 
-			using a sensorimotor model that learns the mapping and an interest model that chooses which regions of the spaces to explore.
-			The sensorimotor model processes new information of the form ($m, s$) with $m \in M$ being the experimented motor parameters and $s \in S$ the received sensory feedback 
-			corresponding to that parameters. 
-			It provides forward predictions of probable $s$ given $m$ and inverse inference of a probable $m$ to reach a given $s$.
-			We use the simplest sensorimotor model, the nearest neighbor algorithm 
-			that performs the prediction of $s$ given $m$ using the nearest neighbor of $m$ in $M$ in the database of the previous experiments and returning its sensory part. 
-			The inverse inference is computed as the motor part of the nearest neighbor in $S$ of the given $s$, but with some exploration noise to allow novel motor parameters to be explored.
+			We define a flat architecture as directly learning a mapping between the motor space $M$ ($12$D) and the sensory space $S$ ($25$D).
+			The control condition is a random motor babbling condition (F-RmB) that randomly chooses new motor parameters $m$ to try at each iteration.
+			In the other conditions, the agent performs Goal Babbling, by self-generating a goal in the sensory space at each iteration and trying to reach it.
+			To do so, the agent needs a sensorimotor model that learns the mapping and provides inverse inference of a probable $m$ to reach a given $s$.
+			The sensorimotor model stores new information of the form ($m, s$) with $m \in M$ being the experimented motor parameters and $s \in S$ the associated sensory feedback. 
+			It computes the inverse inference with the nearest neighbor algorithm: 
+			it gets the motor part of the nearest neighbor of the given $s$ in $S$, and adds exploration noise (gaussian with $\sigma=0.01$) to allow new motor parameters to be explored.
 
-			The agent also needs an interest model that chooses which regions of the motor or sensory space to explore.
-			If the agent chooses goals in the motor space and explores them it is called Motor Babbling, and if it chooses the goals to explore in the sensory space, this is Goal Babbling.
-			To choose the goals in this space of interest, different strategies are possible. 
-			The simplest one is to draw random goals in this space, but strategies based on the learning progress in different regions of the space have been shown more efficient in [ref].
-			This strategies are called active as the agent autonomously drives its exploration towards regions of the space that are both reachable and learnable. 
-			We use the SAGG-RIAC architecture \cite{baranes_active_2013} where the space of interest is the sensory space (Goal Babbling) and that incrementally splits this space into subregions where the learning progress
-			is different. 
-			The learning progress is here computed as the absolute derivative of the reaching competence. 
-			This competence associated to a sensory goal is minus the distance between the goal and the sensory point.
+			The agent also needs an interest model that chooses goals in the sensory space.
+			To generate those goals, different strategies have been studied \cite{baranes_active_2013}. 
+			It was shown that estimating the learning progress in different regions of the sensory space and generating the goals where the progress is high leads to a fast learning.
+			However, this idea can't be applied in a $25$D sensory space as a learning progress signal can't be properly estimated in this volume.
+			Thus we use a simpler random generation of goals in the sensory space as an interest model in the flat random goal babbling condition (F-RGB).
+			We use the Explauto autonomous exploration library \cite{moulin-frier_explauto:_2014} to easily define those sensorimotor and interest models.
+
+			\begin{figure}[t]
+				\center
+				\input{include/F.tikz}
+				\vspace{-0.25cm}
+				\input{include/H1.tikz}
+				\vspace{-0.5cm}
+				\caption{Architectures. Top: Flat. Bottom: Hierarchical.}
+				\label{Architectures}					
+			\end{figure}
 
@@
 
-		\subsubsection{Flat architecture}
-
-		%
-
-		\subsubsection{Hierarchical architecture}
+		\subsubsection{Hierarchical architectures}
 
@@
 			How competence and interest of modules is computed.
-
-			\begin{figure}[t]
-				\center
-				\input{include/F.tikz}
-				\vspace{-0.25cm}
-				\input{include/H1.tikz}
-				\vspace{-0.5cm}
-				\caption{Architectures. Top: flat. Bottom: hierarchical.}
-				\label{Architectures}					
-			\end{figure}
-
-		%
-
-	%
-
-	\subsection{Experiments}
-
-		Nearest Neighbors, $100$ iterations of Motor babbling and then $100000$ iterations of the condition. $100$ trials per condition.
-
-		\subsubsection{Conditions}
+			The learning progress is here computed as the absolute derivative of the reaching competence. 
+			This competence associated to a sensory goal is minus the distance between the goal and the sensory point.
 
@@
 
-				\item F-RmB: Random Motor Babbling with a flat architecture learning $M \rightarrow S_{Hand} \times S_{Stick_1} \times S_{Stick_2} \times S_{Object} \times S_{Boxes}$
-				\item F-RGB: Flat architecture, Random Goal Babbling
-				\item F-AGB: The same architecture but with active goal babbling (my version of SAGG-RIAC)
-				\item H-RGB-P-AMB: Hierarchical architecture with Random Goal Babbling in each module, and choice of module that babbles based on interest ($\epsilon$-prop: probabilities proportional to interest but with $\epsilon=10\%$ of random choice).
+				\item H-RGB-RMB: Hierarchical architecture with Random Goal Babbling in each module, and Random Module Babbling. 
 				Choice of tool to use based on the maximum competence of the two modules to reach the goal object point.
+				\item H-RGB-P-AMB: same as H-RGB-RMB but Active Module Babbling with a choice of module to babble Proportional to interest of modules  ($\epsilon$-prop: probabilities proportional to interest but with $\epsilon=10\%$ of random choice).
 				\item H-RGB-GR-AMB: same as H-RGB-P-AMB but the choice of module to babble is $\epsilon$-greedy with $\epsilon=0.1$
-				\item H-RGB-P-AMB-PGITC: same as H-RGB-P-AMB but the choice of the tool to use is based on the interest (global) of the two modules ($\epsilon$-prop).
+				\item H-RGB-P-AMB-PGITC: same as H-RGB-P-AMB but the choice of the tool to use is Proportional to the Global Interest of the two modules ($\epsilon$-prop).
 
@@
 		%
+		Nearest Neighbors, $100$ iterations of Motor babbling and then $100000$ iterations of the condition. $100$ trials per condition.
 
-		\subsubsection{Measures}
+	%
+
+	\subsection{Measures}
 
@@
 		The exploration of the boxes is the number of boxes that have been filled with the object during training.
-
-		%
 
@@
 	\end{figure*}
+
+	\begin{figure}[ht]
+		\centering
+		\includegraphics[width=7cm]{./include/nbc.pdf}
+		\caption{Number of abrupt behavioral changes}
+		\label{res_nbc}
+	\end{figure}
 

### 2016-01-28 cogsci2016/paper.tex
methods

@@
 
+\usepackage{amsmath}
+
+\usepackage{relsize}
 %\usepackage{hyperref}
@@
 	\cite{ijspeert_dynamical_2013}
-
-	\cite{}
 
@@
 			Thus we use a simpler random generation of goals in the sensory space as an interest model in the flat random goal babbling condition (F-RGB).
-			We use the Explauto autonomous exploration library \cite{moulin-frier_explauto:_2014} to easily define those sensorimotor and interest models.
+			We use the Explauto autonomous exploration library \cite{moulin-frier_explauto:_2014} to easily define those sensorimotor and interest models.\\
 
@@
 
-			We present here an architecture that represents sensorimotor information with a hierarchical structure in Fig. \ref{Architectures}.
+			The $25$D sensory space can be structured to reflect the interaction of the different items of the environment.
+			Indeed, the arm motor position influence the gripper, which influence one of the tools (but not both at the same time), which influence the position of the object and the filling of the boxes.
+			We thus study here learning architectures that could make use of this sensorimotor structure, and we call them hierarchical.
+			Those architecture learn $6$ models at the same time (see Fig. \ref{Architectures}: gray squares are models). 
+			Each of those models functions in the same way as the random goal babbling flat architecture (F-RGB). 
+			Each model has a motor space (e.g.
+motor space of model $2$ is $S_{Hand}$), a sensory space (respectively $S_{Stick_1}$, see arrows in Fig.
+\ref{Architectures}, and can choose goals randomly in this sensory space.
+			At each iteration, the architecture first have to choose the model that will choose a goal, a procedure that we call Model Babbling.
+			Once a model is chosen, it finds a goal in its sensory space, and infer motor parameters (that can be in a sensory space) to reach that goal.
+			Then, it passes those parameters as a goal to be reached by the lower-level model, 
+			which similarly infers motor parameters and passes those ones until the actual $Arm$ motor space gets parameters to try in the environment (with the same exploration noise as in Flat architectures).
+			Model $4$ have also to choose which lower-level model to use in order to reach an object end position $s_o$ in $S_{Object}$, as two models ($3$ and $6$) have $S_{Object}$ as sensory space. 
+			Model $4$ chooses the tool that have allowed to reached $s_o$ as close as possible in the past.
+			Finally, when motor parameters $m$ have been tested in the environment and feedback $s$ received, the mappings of all models are updated, but if model $4$ chose one tool then the mapping of the other tool is not.
 
-			Only the motor module (mod1) adds exploration noise ($\sigma=0.02$) even in hierarchical architecture. 
-			That was the key to have more efficient hierarchical exploration. 
-			Indeed, if all modules successively add exploration noise, few iterations succeed in touching the object. 
-			Alternatively, if the exploration noise is reduced, exploration is less efficient as in NN only the motor module will finally apply noise on known motor commands. 
-			With regression instead of NN, noise can instead be put only on the babbling module.
-
-			How competence and interest of modules is computed.
-			The learning progress is here computed as the absolute derivative of the reaching competence. 
-			This competence associated to a sensory goal is minus the distance between the goal and the sensory point.
-
-			\begin{itemize}
-
-				\item H-RGB-RMB: Hierarchical architecture with Random Goal Babbling in each module, and Random Module Babbling. 
-				Choice of tool to use based on the maximum competence of the two modules to reach the goal object point.
-				\item H-RGB-P-AMB: same as H-RGB-RMB but Active Module Babbling with a choice of module to babble Proportional to interest of modules  ($\epsilon$-prop: probabilities proportional to interest but with $\epsilon=10\%$ of random choice).
-				\item H-RGB-GR-AMB: same as H-RGB-P-AMB but the choice of module to babble is $\epsilon$-greedy with $\epsilon=0.1$
-				\item H-RGB-P-AMB-PGITC: same as H-RGB-P-AMB but the choice of the tool to use is Proportional to the Global Interest of the two modules ($\epsilon$-prop).
-
-			\end{itemize}
+			A first condition is to randomly choose the model that will find a goal, this is Random Model Babbling (H-RGB-RMB).
+			The problem of Model Babbling is an instance of strategic learning \cite{nguyen2012}, 
+			where different outcomes and strategies to learn them are available and the agent learns which strategies are useful for which outcomes.
+			In that paper, they show that an active choice of the outcomes and strategies based on the learning progress on each of them increase learning efficiency compared to random choice.
+			To develop active learning strategies, we first define a measure of learning progress for each of the $6$ models.
+			When a model has been chosen to babble, it draws a random goal $s_g$, and finds motor parameters $m$ to reach it using the lower-level models.
+			The actual outcome $s$ in the sensory space of the module, associated to $m$ might be very different from $s_g$ as this goal might be unreachable, or because lower-level modules are not mature enough for that goal.
+			We define the competence associated to a goal $s_g$ as $C(s_g)=-||s_g-s||$, and the interest $I(s_g)$ associated to this goal
+			as the absolute difference between $C(s_g)$ and the mean competence of the ($k=20$) nearest previous goals.
+			The interest of a model is initialized at $0$ and updated to follow the interest of the goals:
+			$$I_{model}=\frac{n-1}{n}~I_{model} + \frac{1}{n}~I(s_g)$$
+			In condition H-RGB-P-AMB, the choice of module is proportional to their interest (probabilities are proportional to interest but with $\epsilon=10\%$ of random choice). 
+			In condition H-RGB-GR-AMB, the choice of module is greedy (module with maximum interest) but also with $\epsilon=10\%$ of random choice.
+			Finally, condition H-RGB-P-AMB-PGITC is the same as H-RGB-P-AMB but the choice of the tool to use (model $3$ or $6$) is with probabilities proportional to the interest of the two models, 
+			instead of being based on the more competent tool for the given object goal position.
 
 		%
+
+%
+
+\section{Results}
+
 	Nearest Neighbors, $100$ iterations of Motor babbling and then $100000$ iterations of the condition. $100$ trials per condition.
@@
 
-%
-
-\section{Results}
-
 	\paragraph{}
@@
 		\centering
-		\subfloat[]{\includegraphics[width=9cm]{./include/H-RGB-P-AMB-log9-interests-100000.pdf}}
-		\subfloat[]{\includegraphics[width=9cm]{./include/H-RGB-P-AMB-log9-obj-explo.pdf}}
+		\subfloat[]{\includegraphics[width=7cm]{./include/H-RGB-P-AMB-log9-interests-100000.pdf}}
+		\subfloat[]{\includegraphics[width=7cm]{./include/H-RGB-P-AMB-log9-obj-explo.pdf}}
 		\caption{Condition H-RGB-P-AMB. (a) Interests of each module. (b) Exploration of the object space: each dot is one point reached with the object at the end of one movement.}
@@
 		\centering
-		\subfloat[H-RGB-GR-AMB]{\includegraphics[width=8cm]{./include/H-RGB-GR-AMB-log15-events-100000.pdf}}
-		\subfloat[H-RGB-P-AMB]{\includegraphics[width=8cm]{./include/H-RGB-P-AMB-log8-events-100000.pdf}}
+		\subfloat[H-RGB-GR-AMB]{\includegraphics[width=7cm]{./include/H-RGB-GR-AMB-log15-events-100000.pdf}}
+		\subfloat[H-RGB-P-AMB]{\includegraphics[width=7cm]{./include/H-RGB-P-AMB-log8-events-100000.pdf}}
 		\caption{Behavioral measure}

### 2016-01-28 cogsci2016/paper.tex
intro

@@
 \usepackage{apacite}
-
-\usepackage{amsmath}
-
-\usepackage{relsize}
-%\usepackage{hyperref}
+\usepackage[caption=false,font=footnotesize]{subfig}
 
 \usepackage{tikz}
-\usetikzlibrary{arrows,shapes,snakes,automata,backgrounds,petri, fit}
+\usetikzlibrary{arrows,shapes,backgrounds,petri,fit}
 
@@
 \author{{\large \bf S\'ebastien Forestier (sebastien.forestier@inria.fr)} \\
-	INRIA Bordeaux Sud-Ouest\\
-	Bordeaux, France
+	Inria Bordeaux Sud-Ouest and Ensta Paristech,\\
+	200 Avenue de la Vieille Tour, 33405 Talence, France
   \AND {\large \bf Pierre-Yves Oudeyer (pierre-yves.oudeyer@inria.fr)} \\
-	INRIA Bordeaux Sud-Ouest\\
-	Bordeaux, France}
-
-\usepackage[caption=false,font=footnotesize]{subfig}
+	Inria Bordeaux Sud-Ouest and Ensta Paristech,\\
+	200 Avenue de la Vieille Tour, 33405 Talence, France}
 
@@
 
-	\paragraph{}
 	Development of tool use: different properties \cite{guerin2013survey} (cite others?). 
@@
 	In that paper we will focus on one important property in the development of precursors of tool use which is the seamless progression 
-	between successives phases of behavior with tools and objects which are called overlapping waves [Siegler]. 
-	One behavioral description of the successives phases differentiate three phases \cite{guerin2013survey}.
-	In the first phase the babies engage mostly in behavior without objects (babbling), in the second phase their behavior has shifted towards interaction with one object, and then interaction between objects.
+	between successives phases of behavior with tools and objects which are called overlapping waves \cite{siegler1996emerging}. 
+	One behavioral study of the successives phases differentiate three phases \cite{guerin2013survey}.
+	In the first phase the babies engage mostly in behaviors without objects, in the second phase their behavior has shifted towards interaction with one object, and then interaction between objects.
 	[more details: months, experiments]
 
+	Active curiosity-driven learning models	\cite{santucci2013}.
+	Modelling work has shown that developmental trajectories could emerge from the curiosity-driven active learning of sensorimotor models \cite{oudeyer_what_2007} \cite{moulin-frier_self-organization_2014}.
+	Details on those models.
 	We hypothesize that several mechanisms play a role in the structure of this behavioral progression and in particular 
@@
 	2) the structure of the representation used to encode sensorimotor experience.	
-
-	Curiosity studies in developmental psychology 
-	\cite{kidd}
-	\cite{gottlieb_information-seeking_2013}
-
-	We will study aspects of these hypothesis leveraging and extending models of curiosity-driven learning of sensorimotor models to the exploration of given hierarchies of sensorimotor models.
-	In such hierarchies, parts of the sensory space (e.g. the position of the hand) can be used as a motor space by another higher-level model to explore other sensory spaces.
-	We do not study some other important factors of the development of tool use: the autonomous building and evolution of the hierarchy of models but we consider it given to a learning agent.
+	[TODO]A few words on those hypothesis: how.
+	However, we do not study some other important factors of the development of tool use: the autonomous building and evolution of the hierarchy of models but we consider it given to a learning agent.
 	We also do not address the question of the role of social guidance.
 
-	Related work
-	Curiosity-driven modelling work, emergence of developmental trajectories.
-	%\cite{oudeyer_intrinsic_2007} 
-	\cite{oudeyer_what_2007}
-	%\cite{flow}
-	\cite{sch}
-	\cite{santucci2013}
-	\cite{cangelosi2010integration}
-	\cite{oudeyer2014evolution}
+	IAC series of architectures and Explauto framework: previous architectures \cite{baranes_active_2013}.
+	We will study aspects of these hypothesis leveraging and extending models of curiosity-driven learning of sensorimotor models to the exploration of hierarchies of sensorimotor models.
+	In hierarchies of sensorimotor models, one of the sensory spaces (e.g. the position of the hand) can be used as a motor space by another higher-level model to explore other sensory spaces.
+	More details on experiments: strategic learning.
 
-	IAC series of architectures and Explauto framework: previous experiments.
-	\cite{moulin-frier_self-organization_2014}
-	\cite{moulin-frier_explauto:_2014}
-	%\cite{baranes2010intrinsically}
-	%\cite{riac}
-	\cite{baranes_active_2013}
-
-	Representations in explauto and other models 
-	\cite{mugan2009}
-	\cite{metzen2013}
-	%\cite{horde}
-	%\cite{mugan}
-	\cite{vig}
-	\cite{sutton1999between}
-
-	Other related work
+	Other related work, contributions of this paper.
 	\cite{ugur2015}
@@
 
-	More details on experiments
-	\cite{ijspeert_dynamical_2013}
-
 	Along with this paper we provide open-source Python code\footnote{Source code and notebooks available as a Github repository at \url{https://github.com/sebastien-forestier/CogSci2016}} 
 	with iPython/Jupyter notebooks that explain how to reproduce the experiments and analysis.
+
+	%Representations in explauto and other models 
+	%\cite{mugan2009}
+	%\cite{metzen2013}
+	%%\cite{horde}
+	%%\cite{mugan}
+	%\cite{vig}
+	%\cite{sutton1999between}
 
@@
 
-		\paragraph{}
 		We simulate a 2D robotic arm using tools to move an object into different boxes in the environment. 		
@@
 
-			We use Dynamical Movement Primitive \cite{ijspeert_dynamical_2013} to control the arm's movement as this framework permits the production of a diversity of arm's trajectories with few parameters.
-			Each of the $4$ arm's degrees-of-freedom (DOF) is controlled by a DMP with a starting and a goal position equal to the rest position of the joint.
-			Each DMP is parameterized by one weight on each of $3$ basis functions whose centers are distributed homogeneously throughout the movement duration.
-			The weights are bounded in the interval $[-200,200]$ (mapped to the standard interval $[-1,1]$) which allow each joint to fairly cover the interval $[-1,1]$ during the movement.
+			We use Dynamical Movement Primitives \cite{ijspeert_dynamical_2013} to control the arm's movement as this framework permits the production of a diversity of arm's trajectories with few parameters.
+			Each of the $4$ arm's degrees-of-freedom (DOF) is controlled by a DMP starting at the rest position of the joint.
+			Each DMP is parameterized by one weight on each of $2$ basis functions and one weight specifying the end position of the movement.
+			The weights are bounded in the interval $[-1,1]$ and allow each joint to fairly cover the interval $[-1,1]$ during the movement.
 			Each DMP outputs a series of $50$ positions that represents a sampling of the trajectory of one joint during the movement.		
-			The arm's movement is thus parameterized by $12$ weights which are represented by the motor space $M=[-1,1]^{12}$.\\
+			The arm's movement is thus parameterized with $12$ weights, represented by the motor space $M=[-1,1]^{12}$.\\
 
@@
 
-		\paragraph{}
 		The problem settings for the learning agent is to explore its sensorimotor space by iteratively choosing motor parameters that represents arm trajectories and receiving sensory feedback.
@@
 			When a model has been chosen to babble, it draws a random goal $s_g$, and finds motor parameters $m$ to reach it using the lower-level models.
-			The actual outcome $s$ in the sensory space of the module, associated to $m$ might be very different from $s_g$ as this goal might be unreachable, or because lower-level modules are not mature enough for that goal.
+			The actual outcome $s$ in the sensory space of the model, associated to $m$ might be very different from $s_g$ as this goal might be unreachable, or because lower-level models are not mature enough for that goal.
 			We define the competence associated to a goal $s_g$ as $C(s_g)=-||s_g-s||$, and the interest $I(s_g)$ associated to this goal
@@
 			The interest of a model is initialized at $0$ and updated to follow the interest of the goals:
-			$$I_{model}=\frac{n-1}{n}~I_{model} + \frac{1}{n}~I(s_g)$$
-			In condition H-RGB-P-AMB, the choice of module is proportional to their interest (probabilities are proportional to interest but with $\epsilon=10\%$ of random choice). 
-			In condition H-RGB-GR-AMB, the choice of module is greedy (module with maximum interest) but also with $\epsilon=10\%$ of random choice.
+			\begin{equation}
+				I_{model}=\frac{n-1}{n}~I_{model} + \frac{1}{n}~I(s_g)
+			\end{equation}
+			In condition H-RGB-P-AMB, the choice of model is proportional to their interest (probabilities are proportional to interest but with $\epsilon=10\%$ of random choice). 
+			In condition H-RGB-GR-AMB, the choice of model is greedy (model with maximum interest) but also with $\epsilon=10\%$ of random choice.
 			Finally, condition H-RGB-P-AMB-PGITC is the same as H-RGB-P-AMB but the choice of the tool to use (model $3$ or $6$) is with probabilities proportional to the interest of the two models, 
@@
 
-	Nearest Neighbors, $100$ iterations of Motor babbling and then $100000$ iterations of the condition. $100$ trials per condition.
+	We perform $100$ simulations per condition. 
+	Each simulation starts with $100$ iterations of motor babbling and then runs for $100000$ iterations of the condition.
+	In this section we provide results for different types of measures. 
+	First we show an exemple of a run of a hierarchical condition to illustrate a possible evolution of the interest of each model, and the result in the exploration of the object space.
+	Then, we define a behavioral measure to categorize the different types of behaviors with objects and study the structure of their evolution.
+	We also give a measure of the total exploration of the different spaces during simulations.
+	Finally, we compare the structure of tool choice made to reach object goal position during exploration in the two conditions for which only this choice differs.
 
-	%
+	Fig. \ref{res_interests} shows details about one trial of the condition H-RGB-P-AMB. 
+	We can see the interest of each model during the whole experiment.
+	The interests of models 2 and 5 increase abruptly once the arm succeeded in grabbing the corresponding stick.
+	Following that, the interests of models 3 and 6 also increase abruptly when the object has been touched by the corresponding stick.
+	An exemple of exploration of the $2$D space with the object is also provided in Fig. \ref{res_interests}(b) corresponding to the same condition.
 
-	\subsection{Measures}
+	\begin{figure*}[ht]
+		\centering
+		\subfloat[]{\includegraphics[width=7cm]{./include/H-RGB-P-AMB-log9-interests-100000.pdf}}
+		\subfloat[]{\includegraphics[width=7cm]{./include/H-RGB-P-AMB-log9-obj-explo.pdf}}
+		\caption{Condition H-RGB-P-AMB. (a) Interests of each model. (b) Exploration of the object space: each dot is one point reached with the object at the end of one movement.}
+		\label{res_interests}
+	\end{figure*}
 
@@
 	The third category ($object$) contains the mouvements where both a stick was grabbed and the object was moved by the stick.
+	Fig. \ref{res_ow} shows the prototypical evolution of the proportion of the three categories of behavior along the $100000$ iterations for conditions H-RGB-GR-AMB and H-RGB-P-AMB.
+    We performed a more detailed analysis by counting the trials where the evolution of the three types of behaviors were similar to the one of Fig. \ref{res_ow}(b).
+    A structure was considered similar if it validated each of the following criteria:
+    behaviors of categories $stick$ and $object$ increase quikly from $0$ to more than $10\%$ (potentially after an initial phase with a steady low value), 
+    and are followed by a plateau (steady curve with small slope) with no abrupt changes, and behaviors of category $object$ start to raise at least $1000$ iterations after $stick$ started to raise.
+    We counted no structures of that type in Flat conditions, $7$ for H-RGB-GR-AMB, $60$ for H-RGB-RMB, $70$ for H-RGB-P-AMB and $79$ for H-RGB-P-AMB-PGITC.
+    Also, the median number of abrupt changes (steady change of more than $10\%$) in conditions F-RmB, F-RGB, H-RGB-RMB, H-RGB-P-AMB, H-RGB-GR-AMB and H-RGB-P-AMB-PGITC was respectively $0$, $1$, $2$, $2$, $6$, $1$,
+    with a significant difference between condition H-RGB-GR-AMB and the others (Mann-Whitney U tests, $p<0.0001$).
+
+	\begin{figure}[ht]
+		\centering
+		\includegraphics[width=4.4cm]{./include/H-RGB-GR-AMB-log15-events-100000.pdf}
+		\hspace{-0.4cm}
+		\includegraphics[width=4.4cm]{./include/H-RGB-P-AMB-log8-events-100000.pdf}
+		\caption{Behavioral measure. Left: H-RGB-GR-AMB, Right: H-RGB-P-AMB.}
+		\label{res_ow}
+	\end{figure}
+
+	%\begin{figure}[ht]
+		%\centering
+		%\includegraphics[width=7cm]{./include/nbc.pdf}
+		%\caption{Number of abrupt behavioral changes}
+		%\label{res_nbc}
+	%\end{figure}
 
@@
 	The exploration of the boxes is the number of boxes that have been filled with the object during training.
-
-	%
-
-	\paragraph{}
-	Fig. \ref{res_interests} shows details about one trial of the condition H-RGB-P-AMB. 
-	We can see the interest of each module during the whole experiment.
-	The interests of modules 2 and 5 increase abruptly once the arm succeeded in grabbing the corresponding stick.
-	Following that, the interests of modules 3 and 6 also increase abruptly when the object has been touched by the corresponding stick.
-	An exemple of exploration of the $2$D space with the object is also provided in Fig. \ref{res_interests}(b) corresponding to the same condition.
-
-	\begin{figure*}[ht]
-		\centering
-		\subfloat[]{\includegraphics[width=7cm]{./include/H-RGB-P-AMB-log9-interests-100000.pdf}}
-		\subfloat[]{\includegraphics[width=7cm]{./include/H-RGB-P-AMB-log9-obj-explo.pdf}}
-		\caption{Condition H-RGB-P-AMB. (a) Interests of each module. (b) Exploration of the object space: each dot is one point reached with the object at the end of one movement.}
-		\label{res_interests}
-	\end{figure*}
-
-	\paragraph{}
-	Fig. \ref{res_ow} shows the proportion of the three categories of behavior along the $100000$ iterations for conditions H-RGB-GR-AMB and H-RGB-P-AMB.
-
-	\begin{figure*}[ht]
-		\centering
-		\subfloat[H-RGB-GR-AMB]{\includegraphics[width=7cm]{./include/H-RGB-GR-AMB-log15-events-100000.pdf}}
-		\subfloat[H-RGB-P-AMB]{\includegraphics[width=7cm]{./include/H-RGB-P-AMB-log8-events-100000.pdf}}
-		\caption{Behavioral measure}
-		\label{res_ow}
-	\end{figure*}
-
-	\begin{figure}[ht]
-		\centering
-		\includegraphics[width=7cm]{./include/nbc.pdf}
-		\caption{Number of abrupt behavioral changes}
-		\label{res_nbc}
-	\end{figure}
-
-	\paragraph{}
 	Fig. \ref{res_explo} shows the total exploration of the different sensory spaces for each condition.
-	We provide statistical Mann-Whitney U test results of comparisons of the exploration at the end of the experiments in different pairs of conditions.
+	We provide statistical Mann-Whitney U test results of comparisons of the exploration in different pairs of conditions.
 	Firstly, the Motor Babbling condition (F-RmB) have more explored $S_{Hand}$ and less $S_{Object}$ and $S_{Boxes}$ compared to the other conditions ($p<0.0001$).
@@
 		\includegraphics[width=14cm]{./include/xp1-explo-legend.pdf}\\
-		\vspace{-0.3cm}
+		\vspace{-0.4cm}
 		\subfloat[$Hand$]{\includegraphics[width=3.5cm]{./include/xp1-explo-hand.pdf}}
@@
 		\subfloat[$Object$]{\includegraphics[width=3.5cm]{./include/xp1-explo-obj.pdf}}
-		\subfloat[$Boxes$]{\includegraphics[width=3.5cm]{./include/xp1-explo-box.pdf}}
+		\subfloat[$Boxes$]{\includegraphics[width=3.3cm]{./include/xp1-explo-box.pdf}}
 		\caption{Exploration of sensory spaces.}
@@
 
-	\paragraph{}
 	Fig. \ref{res_choice} shows a comparison of the choice of tool to reach a given object goal position in the conditions H-RGB-P-AMB and H-RGB-P-AMB-PGITC.
-	In those conditions, module $4$ learns a mapping between $S_{Object}$ and $S_{Boxes}$. 
-	When this module is babbling, it chooses a random goal $s_b \in S_{Boxes}$ and infers the best object position $s_o$ to reach $s_b$.
-	To reach $s_o$, one of the tools ($Stick_1$ with module $3$ or $Stick_2$ with module $6$) is chosen. 
+	In those conditions, model $4$ learns a mapping between $S_{Object}$ and $S_{Boxes}$. 
+	When this model is babbling, it chooses a random goal $s_b \in S_{Boxes}$ and infers the best object position $s_o$ to reach $s_b$.
+	To reach $s_o$, one of the tools ($Stick_1$ with model $3$ or $Stick_2$ with model $6$) is chosen. 
 	We plot all those choices, at position $s_o$ on a $2$D space, with color blue if $Stick_1$ was chosen and red if $Stick_2$ was chosen, in one figure for each of the two conditions.
 	We can see two very different choice structures.
-	However, goal that can be reached with both tools are more often chosen to be explored with the long stick in the interest-based choice of condition H1 than in competence-based choice of condition H1-CL.
+	However, goal that can be reached with both tools are more often chosen to be explored with the long stick in the interest-based choice of condition H-RGB-P-AMB-PGITC than in competence-based choice of condition H-RGB-P-AMB.
 
-	\begin{figure*}[ht]
-		\subfloat[H-RGB-P-AMB]{\includegraphics[width=9cm]{./include/H-RGB-P-AMB-log9-choice_mod4.png}}
-		\subfloat[H-RGB-P-AMB-PGITC]{\includegraphics[width=8.8cm]{./include/H-RGB-P-AMB-PGITC-log3-choice_mod4.png}}
-		\caption{Chosen tool depending on object goal position. Blue points: long stick choice. Red points: small stick choice.}
+	\begin{figure}[ht]
+		\centering
+		\includegraphics[width=4.5cm]{./include/H-RGB-P-AMB-log9-choice_mod4.png}
+		\hspace{-0.6cm}
+		\includegraphics[width=4.5cm]{./include/H-RGB-P-AMB-PGITC-log3-choice_mod4.png}
+		\caption{Chosen tool depending on object goal position. Blue points: long stick choice. Red points: small stick choice. Left: H-RGB-P-AMB, Right: H-RGB-P-AMB-PGITC.}
 		\label{res_choice}
-	\end{figure*}
+	\end{figure}
 
@@
 
-\section{Conclusion}
-
-%
-
 \section{Acknowledgments}

### 2016-01-28 cogsci2016/paper.tex
intro

@@
 
-	Active curiosity-driven learning models	\cite{santucci2013}.
-	Modelling work has shown that developmental trajectories could emerge from the curiosity-driven active learning of sensorimotor models \cite{oudeyer_what_2007} \cite{moulin-frier_self-organization_2014}.
-	Details on those models.
 	We hypothesize that several mechanisms play a role in the structure of this behavioral progression and in particular 
@@
 	2) the structure of the representation used to encode sensorimotor experience.	
-	[TODO]A few words on those hypothesis: how.
-	However, we do not study some other important factors of the development of tool use: the autonomous building and evolution of the hierarchy of models but we consider it given to a learning agent.
-	We also do not address the question of the role of social guidance.
+	Indeed, curiosity-driven learning models with an intrinsic motivation towards situations yielding a high learning progress 
+	have shown that developmental trajectories could emerge from the active learning of sensorimotor mappings, in very different settings.
+	In the Playground Experiment \cite{oudeyer_what_2007}, a quadruped robot learned how to use its motor primitives to interact with the items of an infant play mat and a robot peer.
+	Also, in a study of the self-organization of vocalizations \cite{moulin-frier_self-organization_2014}, an agent had to learn how to
+	use a vocal synthesizer by self-exploration or with the help of humans' demonstrations of phonetic items. 
+	In both studies, developmental trajectories of increasing complexity are emerging from learning, with both regularities in developmental steps and diversity.
+	The diversity comes from different mechanisms: random generation in the algorithms, variability in the environment, and the multiples attractors of the dynamic learning system.
+	In those models, the agent learns only one mapping that relates a motor space to a sensory or task space. 
+	However, in the perspective of an open-ended development of reusable skills, and specifically in the development of tool use, multiple interdependent task spaces should be available to the agent
+	as for instance complex actions with tools could make use of previously learned parameterized interaction with the tool.
 
-	IAC series of architectures and Explauto framework: previous architectures \cite{baranes_active_2013}.
-	We will study aspects of these hypothesis leveraging and extending models of curiosity-driven learning of sensorimotor models to the exploration of hierarchies of sensorimotor models.
-	In hierarchies of sensorimotor models, one of the sensory spaces (e.g. the position of the hand) can be used as a motor space by another higher-level model to explore other sensory spaces.
-	More details on experiments: strategic learning.
+	We will thus study aspects of the hypothesis leveraging and extending previous models of curiosity-driven learning.
+	We will define hierarchies of sensorimotor models that structure the sensory space to reflect the interaction of the different items of the environment.
+	In such hierarchies of models to explore, different exploration choices are available to the agent at each learning iteration: which model to explore, and how to explore that model.
+	This problem is an instance of strategic learning \cite{nguyen2012}, 
+	where different outcomes and strategies are available and the agent has to learn which strategies are useful for which outcomes. 
+	We will define and compare several strategies based on active learning to solve this problem.
+
+	Setup: architecture, model babbling, arm
+
+	However, we do not study some other important factors of the development of tool use.
+	We consider the hierarchy of models given to the agent and do not study its autonomous building and evolution during developmental stages.
+	Also, social guidance with imitation and mimicry is of central importance for the development of tool use in infants but we do not address the question
+	of its modeling in this paper nor the interplay and tradeoff between social learning and self-exploration.
+	Another important feature of young infants' learning of tool use is the need to adapt to a developing body and to the maturation of vision during ontogenetic development, 
+	but here we consider motor control and sensory perception steady over the simulated learning time span.
 
@@
 
-			\begin{figure}[t]
-				\center
-				\input{include/F.tikz}
-				\vspace{-0.25cm}
-				\input{include/H1.tikz}
-				\vspace{-0.5cm}
-				\caption{Architectures. Top: Flat. Bottom: Hierarchical.}
-				\label{Architectures}					
-			\end{figure}
+			%\begin{figure}[t]
+				%\center
+				%\input{include/F.tikz}
+				%\vspace{-0.25cm}
+				%\input{include/H1.tikz}
+				%\vspace{-0.5cm}
+				%\caption{Architectures. Top: Flat. Bottom: Hierarchical.}
+				%\label{Architectures}					
+			%\end{figure}
 

### 2016-01-29 cogsci2016/paper.tex
intro

@@
 
-	Development of tool use: different properties \cite{guerin2013survey} (cite others?). 
-	List of some properties: grounding of representation and planning based on a large amount of experiences, ongoing process of upgrading representations (others?).
-	In that paper we will focus on one important property in the development of precursors of tool use which is the seamless progression 
-	between successives phases of behavior with tools and objects which are called overlapping waves \cite{siegler1996emerging}. 
-	One behavioral study of the successives phases differentiate three phases \cite{guerin2013survey}.
-	In the first phase the babies engage mostly in behaviors without objects, in the second phase their behavior has shifted towards interaction with one object, and then interaction between objects.
-	[more details: months, experiments]
+	The ontegenetic development of tool use shows different properties \cite{guerin2013survey}: 
+	representations are grounded on a large amount of experiences and follow an ongoing process of upgrading [cite others?].
+	In this paper we focus on one important property in the development of precursors of tool use which is the seamless progression 
+	between overlapping phases of behavior with tools and objects which have been called overlapping waves \cite{siegler1996emerging}. 
+	The behavioral study of these phases differentiate three categories of behaviors \cite{guerin2013survey}.
+	In the first phase, from birth to one year old, babies engage in behaviors without objects, in the second phase, from 4-5 months old, their behavior shifts towards more interaction with a single object, and from 9 months old, begins a simple relational play with several objects.
+	[more details?]
 
@@
 
-	We will thus study aspects of the hypothesis leveraging and extending previous models of curiosity-driven learning.
-	We will define hierarchies of sensorimotor models that structure the sensory space to reflect the interaction of the different items of the environment.
+	In this paper we study aspects of those hypothesis leveraging and extending previous models of curiosity-driven learning.
+	We define hierarchies of sensorimotor models that structure the sensory space to reflect the interaction of the different items of the environment.
 	In such hierarchies of models to explore, different exploration choices are available to the agent at each learning iteration: which model to explore, and how to explore that model.
@@
 	where different outcomes and strategies are available and the agent has to learn which strategies are useful for which outcomes. 
-	We will define and compare several strategies based on active learning to solve this problem.
+	We define and compare several strategies based on active learning to solve this problem.
+	We compare the different learning conditions in a $2$D environment where a simulated arm with three joints plus a gripper can grab tools to move an out-of-reach object.
+	We measure the different phases of behavior during exploration and compare the structure of the behavioral waves. [more results here?]
 
-	Setup: architecture, model babbling, arm
-
-	However, we do not study some other important factors of the development of tool use.
+	However, here we do not study some other important factors in the development of tool use.
 	We consider the hierarchy of models given to the agent and do not study its autonomous building and evolution during developmental stages.
@@
 
-	Other related work, contributions of this paper.
+	Other related work.
 	\cite{ugur2015}

### 2016-01-29 cogsci2016/paper.tex
intro

@@
 	In this paper we focus on one important property in the development of precursors of tool use which is the seamless progression 
-	between overlapping phases of behavior with tools and objects which have been called overlapping waves \cite{siegler1996emerging}. 
+	between overlapping phases of behavior with tools and objects, which have been called overlapping waves \cite{siegler1996emerging}. 
 	The behavioral study of these phases differentiate three categories of behaviors \cite{guerin2013survey}.
@@
 	We measure the different phases of behavior during exploration and compare the structure of the behavioral waves. [more results here?]
+
+	To our knowledge, this model is the first to show overlapping waves structure in the development of tool use [can we say it is the first model of curiosity-driven development of tool use ?].
 
@@
 
-	\subsection{F-AGB vs H-RGB-P-AMB vs H-RGB-GR-AMB}
+	\subsection{F-RGB vs H-RGB-P-AMB vs H-RGB-GR-AMB}
+
+		Results show different structures of behavior evolution in those 3 conditions.
 
@@
 	\subsection{H-RGB-P-AMB vs H-RGB-P-AMB-PGITC}
+
+		Different structure of tool choice: overlapping waves of strategies to fulfill given goals in condition H-RGB-P-AMB-PGITC.
 

### 2016-01-29 cogsci2016/paper.tex
figure
discussion

@@
 
-	The ontegenetic development of tool use shows different properties \cite{guerin2013survey}: 
+	The ontegenetic development of tool use shows different properties \cite{guerin2013survey}, \cite{fenson1976developmental}: 
 	representations are grounded on a large amount of experiences and follow an ongoing process of upgrading [cite others?].
@@
 
-			%\begin{figure}[t]
-				%\center
-				%\input{include/F.tikz}
-				%\vspace{-0.25cm}
-				%\input{include/H1.tikz}
-				%\vspace{-0.5cm}
-				%\caption{Architectures. Top: Flat. Bottom: Hierarchical.}
-				%\label{Architectures}					
-			%\end{figure}
+			\begin{figure}[t]
+				\center
+				\input{include/F.tikz}
+				\vspace{-0.25cm}
+				\input{include/H1.tikz}
+				\vspace{-0.5cm}
+				\caption{Architectures. Top: Flat. Bottom: Hierarchical.}
+				\label{Architectures}					
+			\end{figure}
 
@@
 	Then, F-RGB explores all spaces less than H-RGB-RMB condition ($p<0.01$).
+	H-RGB-RMB explores more $S_{Hand}$ ($p<0.001$) and less $S_{Object}$ ($p<0.05$) than H-RGB-P-AMB.
 	Also, H-RGB-GR-AMB shows lower exploration all spaces than H-RGB-P-AMB ($p<0.01$).
@@
 		\subfloat[$Boxes$]{\includegraphics[width=3.3cm]{./include/xp1-explo-box.pdf}}
-		\caption{Exploration of sensory spaces.}
+		\caption{Exploration of sensory spaces. Box plots show for each condition and space the median and quartiles of the $100$ trials.}
 		\label{res_explo}
@@
 
+		Results show that random model babbling and active model babbling both show overlapping waves structure in the evolution of the three behaviors, 
+		but random model babbling explores slightly less the object position.
+		In this setup, the difference is more on the cognitive or intentional level, as active model babbling monitors the progress on each model whereas random model babbling do not, than on a quantitative level,
+		because here all models are still useful to explore.
+		However, in others setups where some tasks are learned much faster than others and where at some point it become useless to explore a mastered task, then active model babbling would
+		make a key difference on a quantitative exploration point of view, and on the structure of the evolution of the measured behaviors.
+
 	%

### 2016-01-29 cogsci2016/paper.tex
discussion

@@
 			The actual outcome $s$ in the sensory space of the model, associated to $m$ might be very different from $s_g$ as this goal might be unreachable, or because lower-level models are not mature enough for that goal.
-			We define the competence associated to a goal $s_g$ as $C(s_g)=-||s_g-s||$, and the interest $I(s_g)$ associated to this goal
-			as the absolute difference between $C(s_g)$ and the mean competence of the ($k=20$) nearest previous goals.
-			The interest of a model is initialized at $0$ and updated to follow the interest of the goals:
+			We define the competence associated to a goal $s_g$ as minus the distance between the goal and the reached point, divided by the maximal distance in this space, to scale this measure across different spaces:
+
+			\begin{equation}
+				C(s_g)=-\frac{||s_g-s||}{max_{s'}||s'-s||}
+			\end{equation}
+			 and the interest $I(s_g)$ associated to this goal as 
+			\begin{equation}
+				I(s_g) = |C(s_g) - mean_{kNN}C(s)|
+			\end{equation}
+			the absolute difference between $C(s_g)$ and the mean competence of the ($k=20$) nearest previous goals.
+			The interest of a model is initialized at $0$ and updated to follow the interest of the goals (with rate $n=200$):
 			\begin{equation}
@@
 
-	\subsection{F-RGB vs H-RGB-P-AMB vs H-RGB-GR-AMB}
+	\subsection{Structure of the evolution of behavior}
 
-		Results show different structures of behavior evolution in those 3 conditions.
-
-		Results show that random model babbling and active model babbling both show overlapping waves structure in the evolution of the three behaviors, 
+		Results show different structures of behavior evolution in the different conditions.
+		F-RGB shows 
+		H-RGB-GR-AMB shows successive behavioral steps with abrupt changes.
+		Random model babbling and active model babbling both show overlapping waves structure in the evolution of the three behaviors, 
 		but random model babbling explores slightly less the object position.
@@
 
-	\subsection{H-RGB-P-AMB vs H-RGB-P-AMB-PGITC}
+	\subsection{Variability of strategies to reach goals}
 

### 2016-01-29 cogsci2016/paper.tex
discussion

@@
 \author{{\large \bf S\'ebastien Forestier (sebastien.forestier@inria.fr)} \\
-	Inria Bordeaux Sud-Ouest and Ensta Paristech,\\
-	200 Avenue de la Vieille Tour, 33405 Talence, France
+	Inria Bordeaux Sud-Ouest and Ensta Paristech, France
   \AND {\large \bf Pierre-Yves Oudeyer (pierre-yves.oudeyer@inria.fr)} \\
-	Inria Bordeaux Sud-Ouest and Ensta Paristech,\\
-	200 Avenue de la Vieille Tour, 33405 Talence, France}
+	Inria Bordeaux Sud-Ouest and Ensta Paristech, France}
 
@@
 \textbf{Keywords:} 
-curiosity-driven learning; tool use; goal babbling; overlapping waves; 
+curiosity-driven learning; tool use; goal babbling; overlapping waves; developmental trajectory; hierarchical skill learning; HiCu model
 \end{abstract}
@@
 
-	The ontegenetic development of tool use shows different properties \cite{guerin2013survey}, \cite{fenson1976developmental}: 
+	The ontogenetic development of tool use shows different properties \cite{guerin2013survey}, \cite{fenson1976developmental}: 
 	representations are grounded on a large amount of experiences and follow an ongoing process of upgrading [cite others?].
@@
 	use a vocal synthesizer by self-exploration or with the help of humans' demonstrations of phonetic items. 
+	Their model reproduces accurately major phases of infant vocal development until $6$ month old.
 	In both studies, developmental trajectories of increasing complexity are emerging from learning, with both regularities in developmental steps and diversity.
-	The diversity comes from different mechanisms: random generation in the algorithms, variability in the environment, and the multiples attractors of the dynamic learning system.
-	In those models, the agent learns only one mapping that relates a motor space to a sensory or task space. 
-	However, in the perspective of an open-ended development of reusable skills, and specifically in the development of tool use, multiple interdependent task spaces should be available to the agent
+	The diversity comes from different mechanisms: stochasticity in the algorithms, variability in the environment, and the multiples attractors of the dynamic learning system.
+	In existing models, the agent learns only one mapping that relates a motor space to a sensory or task space. 
+	However, in the perspective of an open-ended development of reusable skills, and specifically in the development of tool use, multiple interdependent and hierarchically organized task spaces should be available to the agent
 	as for instance complex actions with tools could make use of previously learned parameterized interaction with the tool.
 
-	In this paper we study aspects of those hypothesis leveraging and extending previous models of curiosity-driven learning.
+	In this paper we study aspects of those hypothesis leveraging previous models of curiosity-driven learning and extending them to the active exploration of sensorimotor and task spaces.
 	We define hierarchies of sensorimotor models that structure the sensory space to reflect the interaction of the different items of the environment.
 	In such hierarchies of models to explore, different exploration choices are available to the agent at each learning iteration: which model to explore, and how to explore that model.
-	This problem is an instance of strategic learning \cite{nguyen2012}, 
+	The problem of finding an efficient active choice strategy is an instance of strategic learning \cite{nguyen2012}, 
 	where different outcomes and strategies are available and the agent has to learn which strategies are useful for which outcomes. 
-	We define and compare several strategies based on active learning to solve this problem.
+	We define and compare several strategies to study the role of active learning and hierarchical representation in the structuration of developmental trajectories.
 	We compare the different learning conditions in a $2$D environment where a simulated arm with three joints plus a gripper can grab tools to move an out-of-reach object.
@@
 
-		We simulate a 2D robotic arm using tools to move an object into different boxes in the environment. 		
-		In each trial, we execute a motor trajectory given by the agent, we evaluate its consequences on the sensory dimensions and we give him
+		We simulate a 2D robotic arm that can grasp tools that can be used to move an object into different boxes in the environment. 		
+		In each trial, the agent executes a motor trajectory, we evaluate its consequences on the sensory dimensions and we give him
 		this sensory feedback. Finally the arm, tools and objects are resetted to their intial state.
@@
 			\subfloat{\includegraphics[width=8.8cm]{./include/dmp.pdf}}
-			\caption{Top: a state of the environment. Middle: position of the arm at time steps $17$, $33$ and $50$ along the $50$ steps movement. Bottom: value of the four DMPs during the movement.}
+			\caption{Top: a state of the environment.
+Middle: position of the arm at time steps $17$, $33$ and $50$ along the $50$ steps movement.
+Bottom: trajectory of each of the four virtual motors, generated by a DMP.}
 			\label{env}
@@
 
-			A yellow sphere can be moved into one of ten fixed squared boxes. 
-			The initial position of the sphere is $(0, 1.2)$ and is thus unreachable directly with the gripper.
-			Two sticks can be grasped in order to reach the object.
+			Two sticks can be grasped by the handle side in order to catch an out-of-reached object.
 			A small stick of length $0.3$ is located at position $(0.75, 0.25)$ with initial angle $\frac{\pi}{4}$ from the horizontal line.
 			A long stick of length $0.6$ is located at position $(-0.75, 0.25)$ with initial angle $\frac{3\pi}{4}$ as in Fig. \ref{env}.	
+			A yellow sphere can be caught by the magnetic side of one of the two sticks, moved and possibly placed into one of ten fixed squared boxes. 
+			The initial position of the sphere is $(0, 1.2)$ and is thus unreachable directly with the gripper.		
 			If the gripper is closed near the handle of one stick (closer than $0.2$), it is considered grasped and will follow the gripper's position and the angle of the arm's last segment until the gripper opens.
@@
 			Boxes $1$ to $5$ can only be reached with the long stick, and the other five boxes can be reached with both sticks.
-			At the end of the mouvement, the object is considered to be in one of the box if its center is in the box.
+			At the end of the movement, the object is considered to be in one of the box if its center is in the box.
 
@@
 			At the end of the movement, the robot gets sensory feedback from the different items of the environment.
-			It gets the trajectory of the gripper ($S_{Hand}$), the trajectory of the end of the sticks ($S_{Stick_1}$ and $S_{Stick_2}$), 
-			the position of the object at the end of the mouvement ($S_{Object}$), and whether the object is in a box at the end of the mouvement and the distance between the object and the nearest box ($S_{Boxes}$).
+			It gets the trajectory of the gripper ($S_{Hand}$, $9$D), the trajectory of the end of the sticks ($S_{Stick_1}, $6$D$ and $S_{Stick_2}, $6$D$), 
+			the position of the object at the end of the mouvement ($S_{Object}, $2$D$), and whether the object is in a box at the end of the mouvement and the distance between the object and the nearest box ($S_{Boxes}, $2$D$).
 			The trajectory of the gripper is represented as the $x$ and $y$ positions and the aperture ($1$ or $-1$) of the gripper at $3$ time points: 
@@
 			It was shown that estimating the learning progress in different regions of the sensory space and generating the goals where the progress is high leads to a fast learning.
-			However, this idea can't be applied in a $25$D sensory space as a learning progress signal can't be properly estimated in this volume.
+			However, this idea cannot be applied in a $25$D sensory space as a learning progress signal cannot be properly estimated in this volume.
 			Thus we use a simpler random generation of goals in the sensory space as an interest model in the flat random goal babbling condition (F-RGB).
@@
 \ref{Architectures}, and can choose goals randomly in this sensory space.
-			At each iteration, the architecture first have to choose the model that will choose a goal, a procedure that we call Model Babbling.
+			At each iteration, the architecture first have to choose the model in which to choose a goal, a procedure that we call Model Babbling.
 			Once a model is chosen, it finds a goal in its sensory space, and infer motor parameters (that can be in a sensory space) to reach that goal.
@@
 			Model $4$ chooses the tool that have allowed to reached $s_o$ as close as possible in the past.
-			Finally, when motor parameters $m$ have been tested in the environment and feedback $s$ received, the mappings of all models are updated, but if model $4$ chose one tool then the mapping of the other tool is not.
+			Finally, when motor parameters $m$ have been tested in the environment and feedback $s$ received, the mappings of all models are updated, but if model $4$ chose one tool then the mapping of the other tool is not.\\
 
-			A first condition is to randomly choose the model that will find a goal, this is Random Model Babbling (H-RGB-RMB).
+		%
+
+		\subsubsection{Random vs Active Model Babbling}
+
+			A first condition is to randomly choose the model that will find a goal, this is Random Model Babbling (H-RMB).
 			The problem of Model Babbling is an instance of strategic learning \cite{nguyen2012}, 
@@
 			\end{equation}
-			In condition H-RGB-P-AMB, the choice of model is proportional to their interest (probabilities are proportional to interest but with $\epsilon=10\%$ of random choice). 
-			In condition H-RGB-GR-AMB, the choice of model is greedy (model with maximum interest) but also with $\epsilon=10\%$ of random choice.
-			Finally, condition H-RGB-P-AMB-PGITC is the same as H-RGB-P-AMB but the choice of the tool to use (model $3$ or $6$) is with probabilities proportional to the interest of the two models, 
+			In condition H-P-AMB, the choice of model is proportional to their interest (probabilities are proportional to interest but with $\epsilon=10\%$ of random choice). 
+			In condition H-GR-AMB, the choice of model is greedy (model with maximum interest) but also with $\epsilon=10\%$ of random choice.
+			Finally, condition H-P-AMB-ATC is the same as H-P-AMB but the choice of the tool to use (model $3$ or $6$) is with probabilities proportional to the interest of the two models, 
 			instead of being based on the more competent tool for the given object goal position.
@@
 
-	Fig. \ref{res_interests} shows details about one trial of the condition H-RGB-P-AMB. 
+	Fig. \ref{res_interests} shows details about one trial of the condition H-P-AMB. 
 	We can see the interest of each model during the whole experiment.
@@
 		\subfloat[]{\includegraphics[width=7cm]{./include/H-RGB-P-AMB-log9-obj-explo.pdf}}
-		\caption{Condition H-RGB-P-AMB. (a) Interests of each model. (b) Exploration of the object space: each dot is one point reached with the object at the end of one movement.}
+		\caption{Condition H-P-AMB. (a) Interests of each model. (b) Exploration of the object space: each dot is one point reached with the object at the end of one movement.}
 		\label{res_interests}
@@
 	The third category ($object$) contains the mouvements where both a stick was grabbed and the object was moved by the stick.
-	Fig. \ref{res_ow} shows the prototypical evolution of the proportion of the three categories of behavior along the $100000$ iterations for conditions H-RGB-GR-AMB and H-RGB-P-AMB.
+	Fig. \ref{res_ow} shows the prototypical evolution of the proportion of the three categories of behavior along the $100000$ iterations for conditions H-GR-AMB and H-P-AMB.
     We performed a more detailed analysis by counting the trials where the evolution of the three types of behaviors were similar to the one of Fig. \ref{res_ow}(b).
@@
     and are followed by a plateau (steady curve with small slope) with no abrupt changes, and behaviors of category $object$ start to raise at least $1000$ iterations after $stick$ started to raise.
-    We counted no structures of that type in Flat conditions, $7$ for H-RGB-GR-AMB, $60$ for H-RGB-RMB, $70$ for H-RGB-P-AMB and $79$ for H-RGB-P-AMB-PGITC.
-    Also, the median number of abrupt changes (steady change of more than $10\%$) in conditions F-RmB, F-RGB, H-RGB-RMB, H-RGB-P-AMB, H-RGB-GR-AMB and H-RGB-P-AMB-PGITC was respectively $0$, $1$, $2$, $2$, $6$, $1$,
-    with a significant difference between condition H-RGB-GR-AMB and the others (Mann-Whitney U tests, $p<0.0001$).
+    We counted no structures of that type in Flat conditions, $7$ for H-GR-AMB, $60$ for H-RMB, $70$ for H-P-AMB and $79$ for H-P-AMB-ATC.
+    Also, the median number of abrupt changes (steady change of more than $10\%$) in conditions F-RmB, F-RGB, H-RMB, H-P-AMB, H-GR-AMB and H-P-AMB-ATC was respectively $0$, $1$, $2$, $2$, $6$, $1$, 
+    with a significant difference between condition H-GR-AMB and the others (Mann-Whitney U tests, $p<0.0001$).
+
+	\begin{table}[!ht]
+		\small
+		\begin{center} 
+		\caption{Behavioral analysis} 
+		\label{sample-table} 
+		\vskip 0.12in
+		\begin{tabular}{| c | c | c |} 
+			\hline
+			Condition  &  \begin{tabular}{@{}c@{}}Number of Trials \\ validating criteria\end{tabular}   & \begin{tabular}{@{}c@{}}Median number of  \\ Abrupt changes \end{tabular}\\
+			\hline
+			F-RmB        &    0 &  0\\
+			F-RGB        &    0 &  1\\
+			H-RMB        &   60 &  2\\
+			H-P-AMB      &   70 &  2\\
+			H-GR-AMB     &    7 &  6\\
+			H-P-AMB-ATC  &   79 &  1\\
+			\hline
+		\end{tabular} 
+		\end{center} 
+	\end{table}
 
@@
 		\includegraphics[width=4.4cm]{./include/H-RGB-P-AMB-log8-events-100000.pdf}
-		\caption{Behavioral measure. Left: H-RGB-GR-AMB, Right: H-RGB-P-AMB.}
+		\caption{Behavioral measure. Left: H-GR-AMB, Right: H-P-AMB.}
 		\label{res_ow}
@@
 	Firstly, the Motor Babbling condition (F-RmB) have more explored $S_{Hand}$ and less $S_{Object}$ and $S_{Boxes}$ compared to the other conditions ($p<0.0001$).
-	Then, F-RGB explores all spaces less than H-RGB-RMB condition ($p<0.01$).
-	H-RGB-RMB explores more $S_{Hand}$ ($p<0.001$) and less $S_{Object}$ ($p<0.05$) than H-RGB-P-AMB.
-	Also, H-RGB-GR-AMB shows lower exploration all spaces than H-RGB-P-AMB ($p<0.01$).
-	Condition H-RGB-P-AMB-PGITC explores more $S_{Stick_2}$ ($p<0.05$) than condition H-RGB-P-AMB, and difference is not significant in other spaces.
+	Then, F-RGB explores all spaces less than H-RMB condition ($p<0.01$).
+	H-RMB explores more $S_{Hand}$ ($p<0.001$) and less $S_{Object}$ ($p<0.05$) than H-P-AMB.
+	Also, H-GR-AMB shows lower exploration all spaces than H-P-AMB ($p<0.01$).
+	Condition H-P-AMB-ATC explores more $S_{Stick_2}$ ($p<0.05$) than condition H-P-AMB, and difference is not significant in other spaces.
 
@@
 
-	Fig. \ref{res_choice} shows a comparison of the choice of tool to reach a given object goal position in the conditions H-RGB-P-AMB and H-RGB-P-AMB-PGITC.
+	Fig. \ref{res_choice} shows a comparison of the choice of tool to reach a given object goal position in the conditions H-P-AMB and H-P-AMB-ATC.
 	In those conditions, model $4$ learns a mapping between $S_{Object}$ and $S_{Boxes}$. 
@@
 	We can see two very different choice structures.
-	However, goal that can be reached with both tools are more often chosen to be explored with the long stick in the interest-based choice of condition H-RGB-P-AMB-PGITC than in competence-based choice of condition H-RGB-P-AMB.
+	However, goal that can be reached with both tools are more often chosen to be explored with the long stick in the interest-based choice of condition H-P-AMB-ATC than in competence-based choice of condition H-P-AMB.
 
@@
 		\includegraphics[width=4.5cm]{./include/H-RGB-P-AMB-PGITC-log3-choice_mod4.png}
-		\caption{Chosen tool depending on object goal position. Blue points: long stick choice. Red points: small stick choice. Left: H-RGB-P-AMB, Right: H-RGB-P-AMB-PGITC.}
+		\caption{Chosen tool depending on object goal position. Blue points: long stick choice. Red points: small stick choice. Left: H-P-AMB, Right: H-P-AMB-ATC.}
 		\label{res_choice}
@@
 		F-RGB shows 
-		H-RGB-GR-AMB shows successive behavioral steps with abrupt changes.
+		H-GR-AMB shows successive behavioral steps with abrupt changes.
 		Random model babbling and active model babbling both show overlapping waves structure in the evolution of the three behaviors, 
@@
 
-		Different structure of tool choice: overlapping waves of strategies to fulfill given goals in condition H-RGB-P-AMB-PGITC.
+		Different structure of tool choice: overlapping waves of strategies to fulfill given goals in condition H-P-AMB-ATC.
 
 	%
-
-%
-
-\section{Acknowledgments}
 

### 2016-01-29 cogsci2016/paper.tex
discussion
corrections

@@
 
+	\subsection{Structure of the evolution of behaviors}
+
 		We provide a measure of the different types of behaviors with the sticks and the object during exploration. 
 		We categorize the behaviors into three types.
-	In the first category ($hand$) are mouvements of the arm that did not grab any stick and thus not moved the out-of-reached object.
+		In the first category ($hand$) are mouvements of the arm that did not grab any stick and thus did not move the out-of-reached object.
 		The second category ($stick$) are mouvements that did grab one of the two sticks but did not touch the object with it.
@@
 		and are followed by a plateau (steady curve with small slope) with no abrupt changes, and behaviors of category $object$ start to raise at least $1000$ iterations after $stick$ started to raise.
-    We counted no structures of that type in Flat conditions, $7$ for H-GR-AMB, $60$ for H-RMB, $70$ for H-P-AMB and $79$ for H-P-AMB-ATC.
-    Also, the median number of abrupt changes (steady change of more than $10\%$) in conditions F-RmB, F-RGB, H-RMB, H-P-AMB, H-GR-AMB and H-P-AMB-ATC was respectively $0$, $1$, $2$, $2$, $6$, $1$, 
+		See Table \ref{table} for the results of this analysis per condition.
+		Also, the median number of abrupt changes across trials for each condition are reported in the same table (as the sum of steady changes of more than $10\%$ in the three behaviors).
 		with a significant difference between condition H-GR-AMB and the others (Mann-Whitney U tests, $p<0.0001$).
@@
 			\caption{Behavioral analysis} 
-		\label{sample-table} 
+			\label{table} 
 			\vskip 0.12in
@@
 
-	%\begin{figure}[ht]
-		%\centering
-		%\includegraphics[width=7cm]{./include/nbc.pdf}
-		%\caption{Number of abrupt behavioral changes}
-		%\label{res_nbc}
-	%\end{figure}
+	%
+
+	\subsection{Exploration efficiency}
 
@@
 
+	%
+
+	\subsection{Structure of tool choice}
+
 		Fig. \ref{res_choice} shows a comparison of the choice of tool to reach a given object goal position in the conditions H-P-AMB and H-P-AMB-ATC.
@@
 		To reach $s_o$, one of the tools ($Stick_1$ with model $3$ or $Stick_2$ with model $6$) is chosen. 
-	We plot all those choices, at position $s_o$ on a $2$D space, with color blue if $Stick_1$ was chosen and red if $Stick_2$ was chosen, in one figure for each of the two conditions.
+		We plot all those choices model $4$ made during exploration, at position $s_o$ on a $2$D space, with color blue if $Stick_1$ was chosen and red if $Stick_2$ was chosen, in one figure for each of the two conditions.
 		We can see two very different choice structures.
@@
 
+%
+
 \section{Discussion}
 
-	\subsection{Structure of the evolution of behavior}
+	\subsection{Structure of the evolution of behaviors}
 
 		Results show different structures of behavior evolution in the different conditions.
-		F-RGB shows 
 		H-GR-AMB shows successive behavioral steps with abrupt changes.

### 2016-01-30 cogsci2016/paper.tex
intro

@@
 
-	The ontogenetic development of tool use shows different properties \cite{guerin2013survey}, \cite{fenson1976developmental}: 
-	representations are grounded on a large amount of experiences and follow an ongoing process of upgrading [cite others?].
-	In this paper we focus on one important property in the development of precursors of tool use which is the seamless progression 
-	between overlapping phases of behavior with tools and objects, which have been called overlapping waves \cite{siegler1996emerging}. 
-	The behavioral study of these phases differentiate three categories of behaviors \cite{guerin2013survey}.
-	In the first phase, from birth to one year old, babies engage in behaviors without objects, in the second phase, from 4-5 months old, their behavior shifts towards more interaction with a single object, and from 9 months old, begins a simple relational play with several objects.
-	[more details?]
+	The understanding of tool use development in young children is one of the key question for the more general understanding of the ontogeny of human cognition.
+	Indeed, a series of abilities are progressively developed from the simplest reaching movements of the arms through more dexterous manipulation of a spoon, towards advanced control of multiple interacting objects.
+	The latter shows an understanding of shapes, forces and other physical properties that can be recruited for mental transformations and planning operations which are pillars of human cognition.
+	Children's development has first been described as staircase-like successive stages in which all children go through \cite{piaget1952origins}.
+	More recently, a different view was developed \cite{siegler1996emerging} describing variability among children's developmental paths and in a child's set of current methods to solve a same task (called overlapping waves).
+	This applies in particular to the development of tool use precursors, which can be described as three consecutive and overlapping stages of behaviours \cite{guerin2013survey}: 
+	behaviours without objects, behaviours with a single object, and behaviours with several interacting objects.
+	A study of free manipulative play \cite{fenson1976developmental} shows that play at $7$ months was mostly composed of tactile and visual examination and mouthing of one object, 
+	but simple relational acts of banging two objects together was already common.
+	Later at $13\frac{1}{2}$ months, another study reveals that most children instead prefer to explore the relationships
+	among objects \cite{Zelazo198095}.
 
-	We hypothesize that several mechanisms play a role in the structure of this behavioral progression and in particular 
+	In this paper we focus on the study of this seamless progression between overlapping phases of behaviour with objects.	
+	We hypothesize that several mechanisms play a role in the structure of this behavioural progression and in particular 
 	1) the intrinsic motivation to explore as a self-regulation of the learning growth of complexity, and 
@@
 
-	In this paper we study aspects of those hypothesis leveraging previous models of curiosity-driven learning and extending them to the active exploration of sensorimotor and task spaces.
+	We study aspects of those hypothesis leveraging previous models of curiosity-driven learning and extending them to the active exploration of sensorimotor and task spaces.
 	We define hierarchies of sensorimotor models that structure the sensory space to reflect the interaction of the different items of the environment.
@@
 	We compare the different learning conditions in a $2$D environment where a simulated arm with three joints plus a gripper can grab tools to move an out-of-reach object.
-	We measure the different phases of behavior during exploration and compare the structure of the behavioral waves. [more results here?]
+	We measure the different phases of behaviour during exploration and compare the structure of the behavioural waves. [more results here?]
 
+	Robotics related work.
+	\cite{ugur2015}
 	To our knowledge, this model is the first to show overlapping waves structure in the development of tool use [can we say it is the first model of curiosity-driven development of tool use ?].
@@
 
-	Other related work.
-	\cite{ugur2015}
-	\cite{schmerlinggoal}
+	Footnote
 	\cite{forestier2015}
@@
 	First we show an exemple of a run of a hierarchical condition to illustrate a possible evolution of the interest of each model, and the result in the exploration of the object space.
-	Then, we define a behavioral measure to categorize the different types of behaviors with objects and study the structure of their evolution.
+	Then, we define a behavioural measure to categorize the different types of behaviours with objects and study the structure of their evolution.
 	We also give a measure of the total exploration of the different spaces during simulations.
@@
 
-	\subsection{Structure of the evolution of behaviors}
+	\subsection{Structure of the evolution of behaviours}
 
-		We provide a measure of the different types of behaviors with the sticks and the object during exploration. 
-		We categorize the behaviors into three types.
+		We provide a measure of the different types of behaviours with the sticks and the object during exploration. 
+		We categorize the behaviours into three types.
 		In the first category ($hand$) are mouvements of the arm that did not grab any stick and thus did not move the out-of-reached object.
@@
 		The third category ($object$) contains the mouvements where both a stick was grabbed and the object was moved by the stick.
-		Fig. \ref{res_ow} shows the prototypical evolution of the proportion of the three categories of behavior along the $100000$ iterations for conditions H-GR-AMB and H-P-AMB.
-		We performed a more detailed analysis by counting the trials where the evolution of the three types of behaviors were similar to the one of Fig. \ref{res_ow}(b).
+		Fig. \ref{res_ow} shows the prototypical evolution of the proportion of the three categories of behaviour along the $100000$ iterations for conditions H-GR-AMB and H-P-AMB.
+		We performed a more detailed analysis by counting the trials where the evolution of the three types of behaviours were similar to the one of Fig. \ref{res_ow}(b).
 		A structure was considered similar if it validated each of the following criteria:
-		behaviors of categories $stick$ and $object$ increase quikly from $0$ to more than $10\%$ (potentially after an initial phase with a steady low value), 
-		and are followed by a plateau (steady curve with small slope) with no abrupt changes, and behaviors of category $object$ start to raise at least $1000$ iterations after $stick$ started to raise.
+		behaviours of categories $stick$ and $object$ increase quikly from $0$ to more than $10\%$ (potentially after an initial phase with a steady low value), 
+		and are followed by a plateau (steady curve with small slope) with no abrupt changes, and behaviours of category $object$ start to raise at least $1000$ iterations after $stick$ started to raise.
 		See Table \ref{table} for the results of this analysis per condition.
-		Also, the median number of abrupt changes across trials for each condition are reported in the same table (as the sum of steady changes of more than $10\%$ in the three behaviors).
+		Also, the median number of abrupt changes across trials for each condition are reported in the same table (as the sum of steady changes of more than $10\%$ in the three behaviours).
 		with a significant difference between condition H-GR-AMB and the others (Mann-Whitney U tests, $p<0.0001$).
@@
 			\begin{center} 
-			\caption{Behavioral analysis} 
+			\caption{behavioural analysis} 
 			\label{table} 
@@
 			\includegraphics[width=4.4cm]{./include/H-RGB-P-AMB-log8-events-100000.pdf}
-			\caption{Behavioral measure. Left: H-GR-AMB, Right: H-P-AMB.}
+			\caption{behavioural measure. Left: H-GR-AMB, Right: H-P-AMB.}
 			\label{res_ow}
@@
 
-	\subsection{Structure of the evolution of behaviors}
+	\subsection{Structure of the evolution of behaviours}
 
-		Results show different structures of behavior evolution in the different conditions.
-		H-GR-AMB shows successive behavioral steps with abrupt changes.
-		Random model babbling and active model babbling both show overlapping waves structure in the evolution of the three behaviors, 
+		Results show different structures of behaviour evolution in the different conditions.
+		H-GR-AMB shows successive behavioural steps with abrupt changes.
+		Random model babbling and active model babbling both show overlapping waves structure in the evolution of the three behaviours, 
 		but random model babbling explores slightly less the object position.
@@
 		However, in others setups where some tasks are learned much faster than others and where at some point it become useless to explore a mastered task, then active model babbling would
-		make a key difference on a quantitative exploration point of view, and on the structure of the evolution of the measured behaviors.
+		make a key difference on a quantitative exploration point of view, and on the structure of the evolution of the measured behaviours.
 

### 2016-01-30 cogsci2016/paper.tex
intro

@@
 	Children's development has first been described as staircase-like successive stages in which all children go through \cite{piaget1952origins}.
-	More recently, a different view was developed \cite{siegler1996emerging} describing variability among children's developmental paths and in a child's set of current methods to solve a same task (called overlapping waves).
+	More recently, a different view was developed \cite{siegler1996emerging} describing variability among children's developmental paths and in a child's set of current methods to solve a same task. 
 	This applies in particular to the development of tool use precursors, which can be described as three consecutive and overlapping stages of behaviours \cite{guerin2013survey}: 
 	behaviours without objects, behaviours with a single object, and behaviours with several interacting objects.
-	A study of free manipulative play \cite{fenson1976developmental} shows that play at $7$ months was mostly composed of tactile and visual examination and mouthing of one object, 
-	but simple relational acts of banging two objects together was already common.
-	Later at $13\frac{1}{2}$ months, another study reveals that most children instead prefer to explore the relationships
-	among objects \cite{Zelazo198095}.
+	A study of free play \cite{Zelazo198095} shows that at $9\frac{1}{2}$ months play is mostly composed of tactile examination, waving, banging and mouthing of a single object, 
+	but that simple relational acts of banging two objects together is already common.
+	Later at $13\frac{1}{2}$ months, the study reveals that most children instead prefer to explore the relationships
+	among objects, but still show behaviors of the previous phase. 
+	Furthermore, they show that this overlapping phases pattern averaged across children is also present in a longitudinal study of a single child.
 

### 2016-01-30 cogsci2016/paper.tex
intro

@@
 	Children's development has first been described as staircase-like successive stages in which all children go through \cite{piaget1952origins}.
-	More recently, a different view was developed \cite{siegler1996emerging} describing variability among children's developmental paths and in a child's set of current methods to solve a same task. 
-	This applies in particular to the development of tool use precursors, which can be described as three consecutive and overlapping stages of behaviours \cite{guerin2013survey}: 
-	behaviours without objects, behaviours with a single object, and behaviours with several interacting objects.
+	More recently, different views were developed describing variability among children's developmental paths. 
+	Siegler's overlapping waves theory \cite{siegler1996emerging} also describes variability in a child's set of current methods to solve a problem, and documents their evolution. 
+	In particular, the development of tool use precursors can be described as three consecutive and overlapping stages of behaviours \cite{guerin2013survey}: 
+	body babbling, behaviours with a single object, and behaviours with several interacting objects.
 	A study of free play \cite{Zelazo198095} shows that at $9\frac{1}{2}$ months play is mostly composed of tactile examination, waving, banging and mouthing of a single object, 
@@
 
-	In this paper we focus on the study of this seamless progression between overlapping phases of behaviour with objects.	
+	In this paper we focus on the study of this progression between overlapping phases of behaviours with objects in a robotic model and in particular on the use of concurrent methods to solve a problem.
 	We hypothesize that several mechanisms play a role in the structure of this behavioural progression and in particular 

### 2016-01-30 cogsci2016/paper.tex
intro

@@
 \begin{abstract}
-This is the abstract.
+This is the abstract.\\
+This is the abstract.\\
+This is the abstract.\\
+This is the abstract.\\
+This is the abstract.\\
+This is the abstract.\\
+This is the abstract.\\
 
 \textbf{Keywords:} 
-curiosity-driven learning; tool use; goal babbling; overlapping waves; developmental trajectory; hierarchical skill learning; HiCu model
+curiosity-driven learning; tool use; goal babbling; overlapping waves; developmental trajectory; hierarchical skill learning; HACOB model
 \end{abstract}
@@
 	2) the structure of the representation used to encode sensorimotor experience.	
-	Indeed, curiosity-driven learning models with an intrinsic motivation towards situations yielding a high learning progress 
-	have shown that developmental trajectories could emerge from the active learning of sensorimotor mappings, in very different settings.
+	Active learning is a paradigm where the learning agent chooses which actions to perform in its environment.
+	To make this choice the agent can optimize some extrinsic rewards given by the environment, as in standard Reinfocement Learning tasks.
+	These extrinsic rewards are not suited for an open-ended autonomous exploration of the environment that could reflect children learning by free play.
+	Based on infant's developmental psychology, different types of intrinsic motivations have been studied \cite{santucci2013}.
+	One way to define an intrinsic motivation is to autonomously search for situations where the learning progress is high, so as to avoid unreachable or unlearnable situations.
+	Computational models have shown that developmental trajectories could emerge from the curiosity-driven learning of sensorimotor mappings, in very different settings.
 	In the Playground Experiment \cite{oudeyer_what_2007}, a quadruped robot learned how to use its motor primitives to interact with the items of an infant play mat and a robot peer.
@@
 	use a vocal synthesizer by self-exploration or with the help of humans' demonstrations of phonetic items. 
-	Their model reproduces accurately major phases of infant vocal development until $6$ month old.
+	This model reproduces accurately major phases of infant vocal development until $6$ months.
 	In both studies, developmental trajectories of increasing complexity are emerging from learning, with both regularities in developmental steps and diversity.
 	The diversity comes from different mechanisms: stochasticity in the algorithms, variability in the environment, and the multiples attractors of the dynamic learning system.
-	In existing models, the agent learns only one mapping that relates a motor space to a sensory or task space. 
+	In existing models, the agent learns only one mapping that relates a motor space to a single task space. 
 	However, in the perspective of an open-ended development of reusable skills, and specifically in the development of tool use, multiple interdependent and hierarchically organized task spaces should be available to the agent
-	as for instance complex actions with tools could make use of previously learned parameterized interaction with the tool.
+	as for instance using a tool to act upon an object could make use of previously explored parameterized interaction with the tool.
 
-	We study aspects of those hypothesis leveraging previous models of curiosity-driven learning and extending them to the active exploration of sensorimotor and task spaces.
+	We study aspects of those hypothesis leveraging previous models of curiosity-driven learning and extending them to the active exploration of hierarchical sensorimotor and task spaces.
 	We define hierarchies of sensorimotor models that structure the sensory space to reflect the interaction of the different items of the environment.
@@
 	where different outcomes and strategies are available and the agent has to learn which strategies are useful for which outcomes. 
-	We define and compare several strategies to study the role of active learning and hierarchical representation in the structuration of developmental trajectories.
-	We compare the different learning conditions in a $2$D environment where a simulated arm with three joints plus a gripper can grab tools to move an out-of-reach object.
-	We measure the different phases of behaviour during exploration and compare the structure of the behavioural waves. [more results here?]
+	This can be viewed as a generalization of active learning methods in machine learning.
+	We define the HACOB (Hierarchical Active Curiosity-driven mOdel Babbling) architecture and compare several possible strategies 
+	to study the role of active learning and hierarchical representation in the structuration of developmental trajectories.
+	We compare the different learning conditions in a $2$D environment where a simulated arm with three joints plus a gripper can grab one of two available tools to move an out-of-reach object.
+	We measure the different phases of behaviour during exploration and compare the different structures of behavioural evolution.
 
-	Robotics related work.
-	\cite{ugur2015}
-	To our knowledge, this model is the first to show overlapping waves structure in the development of tool use [can we say it is the first model of curiosity-driven development of tool use ?].
+	To our knowledge, HACOB is the first model of the curiosity-driven development of tool use, 
+	and the first to show the autonomous emergence of overlapping phases of behaviour in the development of object manipulation skills.
+	Here we define  tool use as the ability to perform different effects on an object with the help of an intermediate object, using some sort of learned inverse mapping.
+	Our model is also the first to allow the intrinsically-motivated parallel exploration of different tools to reach a same goal, in line with Siegler's overlapping waves theory.
+	Other models predefine successive learning phases in the learning of object affordances \cite{ugur2015}, or do not study the role of intrinsic motivation in the learning of tool affordances \cite{stoytchev2005behavior}.
 
 	However, here we do not study some other important factors in the development of tool use.
-	We consider the hierarchy of models given to the agent and do not study its autonomous building and evolution during developmental stages.
+	We consider the hierarchy of sensorimotor models to learn as given to the agent and do not study its autonomous building and evolution during developmental stages.
 	Also, social guidance with imitation and mimicry is of central importance for the development of tool use in infants but we do not address the question
@@
 
-	Footnote
-	\cite{forestier2015}
-	\cite{unifying}
-
 	Along with this paper we provide open-source Python code\footnote{Source code and notebooks available as a Github repository at \url{https://github.com/sebastien-forestier/CogSci2016}} 
 	with iPython/Jupyter notebooks that explain how to reproduce the experiments and analysis.
-
-	%Representations in explauto and other models 
-	%\cite{mugan2009}
-	%\cite{metzen2013}
-	%%\cite{horde}
-	%%\cite{mugan}
-	%\cite{vig}
-	%\cite{sutton1999between}
 
@@
 		The problem settings for the learning agent is to explore its sensorimotor space by iteratively choosing motor parameters that represents arm trajectories and receiving sensory feedback.
-		In this section we describe the different learning architectures that we will compare in the experiment.
+		In this section we describe the different learning architectures that we will compare in the experiment.\\
 
@@
 			We thus study here learning architectures that could make use of this sensorimotor structure, and we call them hierarchical.
+			%\footnote{Other work have used a simple hierarchy of two sensorimotor models for object manipulation: \cite{forestier2015} and \cite{unifying}.}
 			Those architecture learn $6$ models at the same time (see Fig. \ref{Architectures}: gray squares are models). 

### 2016-01-31 cogsci2016/paper.tex
methods

@@
 
-		The problem settings for the learning agent is to explore its sensorimotor space by iteratively choosing motor parameters that represents arm trajectories and receiving sensory feedback.
-		In this section we describe the different learning architectures that we will compare in the experiment.\\
+		The problem settings for the learning agent is to explore its sensorimotor space and collect data so as to generate diversity in the produced effects and to learn an inverse model to 
+		be able to reproduce those effects.
+		In this section we describe the different learning architectures that we will compare in the experiments.\\
 
@@
 			We define a flat architecture as directly learning a mapping between the motor space $M$ ($12$D) and the sensory space $S$ ($25$D).
-			The control condition is a random motor babbling condition (F-RmB) that randomly chooses new motor parameters $m$ to try at each iteration.
-			In the other conditions, the agent performs Goal Babbling, by self-generating a goal in the sensory space at each iteration and trying to reach it.
 			To do so, the agent needs a sensorimotor model that learns the mapping and provides inverse inference of a probable $m$ to reach a given $s$.
@@
 			The agent also needs an interest model that chooses goals in the sensory space.
+			The control condition is a random motor babbling condition (F-RmB) that randomly chooses new motor parameters $m$ to try at each iteration.
+			In the other conditions, the agent performs Goal Babbling, a method by which it self-generates a goal in the sensory space at each iteration and trying to reach it.
 			To generate those goals, different strategies have been studied \cite{baranes_active_2013}. 
@@
 			However, this idea cannot be applied in a $25$D sensory space as a learning progress signal cannot be properly estimated in this volume.
-			Thus we use a simpler random generation of goals in the sensory space as an interest model in the flat random goal babbling condition (F-RGB).
+			Thus we use a simpler random generation of goals in the sensory space as an interest model in the flat random goal babbling condition (F-RGB), 
+			which was nevertheless proven to be highly efficient in complex sensorimotor spaces \cite{rolf}.
 			We use the Explauto autonomous exploration library \cite{moulin-frier_explauto:_2014} to easily define those sensorimotor and interest models.\\
@@
 			At each iteration, the architecture first have to choose the model in which to choose a goal, a procedure that we call Model Babbling.
-			Once a model is chosen, it finds a goal in its sensory space, and infer motor parameters (that can be in a sensory space) to reach that goal.
-			Then, it passes those parameters as a goal to be reached by the lower-level model, 
+			Once a model is chosen, it finds a goal in its sensory space, and infer motor parameters (that can be in the sensory space of a lower-level model) to reach that goal.
+			Then, it passes those parameters as a goal to be reached by a lower-level model, 
 			which similarly infers motor parameters and passes those ones until the actual $Arm$ motor space gets parameters to try in the environment (with the same exploration noise as in Flat architectures).
 			Model $4$ have also to choose which lower-level model to use in order to reach an object end position $s_o$ in $S_{Object}$, as two models ($3$ and $6$) have $S_{Object}$ as sensory space. 
-			Model $4$ chooses the tool that have allowed to reached $s_o$ as close as possible in the past.
-			Finally, when motor parameters $m$ have been tested in the environment and feedback $s$ received, the mappings of all models are updated, but if model $4$ chose one tool then the mapping of the other tool is not.\\
+			Model $4$ chooses the tool that have allowed to reached $s_o$ as close as possible in the past, e.g. if model $3$ has in its history a reached sensory
+			point $s$ closer to $s_o$ than any reached point with model $6$, then model $3$ is chosen.
+			Finally, when motor parameters $m$ have been tested in the environment and feedback $s$ received, the mappings of all models are updated, but if model $4$ have chosen a given tool, then the mapping of the other tool is not.\\
 

### 2016-01-31 cogsci2016/paper.tex
methods

@@
 	However, here we do not study some other important factors in the development of tool use.
-	We consider the hierarchy of sensorimotor models to learn as given to the agent and do not study its autonomous building and evolution during developmental stages.
+	We consider the hierarchy of sensorimotor models to learn as given to the agent and do not study its autonomous building and evolution.
 	Also, social guidance with imitation and mimicry is of central importance for the development of tool use in infants but we do not address the question
@@
 		this sensory feedback. Finally the arm, tools and objects are resetted to their intial state.
-		The next sections precisely describe the different items of the environment and their interactions.	
+		The next sections precisely describe the items of the environment and their interactions.	
 		See Fig.\ref{env} for an exemple state of the environment.
@@
 			\hspace{-0.73cm}
-			\vspace{-0.59cm}
+			\vspace{-1.31cm}
 			\includegraphics[width=9.12cm]{./include/tools.pdf}
@@
 			\caption{Top: a state of the environment.
-Middle: position of the arm at time steps $17$, $33$ and $50$ along the $50$ steps movement.
+Middle: position of the arm at time steps $17$, $33$ and $50$,  with some intermediate positions, along the $50$ steps movement.
 Bottom: trajectory of each of the four virtual motors, generated by a DMP.}
@@
 			Each joint can rotate from $-\pi~rad$ to $\pi~rad$ around its resting position, mapped to a standard interval of $[-1,1]$.
-			The length of the $3$ segments of the arm are $0.5$, $0.3$ and $0.2$ so the total length of the arm is $1$ unit.
-			The resting position of the arm is vertical with each joint at $0~rad$ and its base is fixed at position $[0, 0]$.
+			The length of the $3$ segments of the arm are $0.5$, $0.3$ and $0.2$ so the length of the arm is $1$ unit.
+			The resting position of the arm is vertical with joints at $0~rad$ and its base is fixed at position $[0, 0]$.
 			The gripper $g$ has 2 possible positions: \textit{open} ($g \geq 0$) and \textit{closed} ($g < 0$) and its resting position is \textit{open} (with $g = 0$).
-			The robotic arm thus has 4 degrees of freedom represented by a vector in $[-1,1]^4$.
+			The robotic arm has 4 degrees of freedom represented by a vector in $[-1,1]^4$.
 			A trajectory of the arm will be represented as a sequence of such vectors.
@@
 			Each DMP outputs a series of $50$ positions that represents a sampling of the trajectory of one joint during the movement.		
-			The arm's movement is thus parameterized with $12$ weights, represented by the motor space $M=[-1,1]^{12}$.\\
+			The arm's movement is thus parameterized with $12$ weights, represented by the motor space $M=[-1,1]^{12}$.
 
@@
 
-		The problem settings for the learning agent is to explore its sensorimotor space and collect data so as to generate diversity in the produced effects and to learn an inverse model to 
+		The problem settings for the learning agent is to explore its sensorimotor space and collect data so as to generate a diversity of effects and to learn an inverse model to 
 		be able to reproduce those effects.
-		In this section we describe the different learning architectures that we will compare in the experiments.\\
+		In this section we describe the learning architectures that we will compare in the experiments.
 
@@
 			which was nevertheless proven to be highly efficient in complex sensorimotor spaces \cite{rolf}.
-			We use the Explauto autonomous exploration library \cite{moulin-frier_explauto:_2014} to easily define those sensorimotor and interest models.\\
+			We use the Explauto autonomous exploration library \cite{moulin-frier_explauto:_2014} to easily define those sensorimotor and interest models.
 
@@
 				\label{Architectures}					
+				\vspace{-0.5cm}
 			\end{figure}
@@
 			point $s$ closer to $s_o$ than any reached point with model $6$, then model $3$ is chosen.
-			Finally, when motor parameters $m$ have been tested in the environment and feedback $s$ received, the mappings of all models are updated, but if model $4$ have chosen a given tool, then the mapping of the other tool is not.\\
+			Finally, when motor parameters $m$ have been tested in the environment and feedback $s$ received, the mappings of all models are updated, but if model $4$ have chosen a given tool, then the mapping of the other tool is not.
 
@@
 			\end{equation}
-			In condition H-P-AMB, the choice of model is proportional to their interest (probabilities are proportional to interest but with $\epsilon=10\%$ of random choice). 
+			In condition H-P-AMB, the choice of model is probabilistic and proportional to their interest (but with $\epsilon=10\%$ of random choice). 
 			In condition H-GR-AMB, the choice of model is greedy (model with maximum interest) but also with $\epsilon=10\%$ of random choice.
@@
 			instead of being based on the more competent tool for the given object goal position.
+			We call HACOB this Hierarchical Active Curiosity-driven mOdel Babbling algorithmic architecture with the algorithms H-P-AMB and H-P-AMB-ATC being two variants of the architecture.
 
@@
 	In this section we provide results for different types of measures. 
-	First we show an exemple of a run of a hierarchical condition to illustrate a possible evolution of the interest of each model, and the result in the exploration of the object space.
-	Then, we define a behavioural measure to categorize the different types of behaviours with objects and study the structure of their evolution.
+	We define a behavioural measure to categorize the types of behaviours with objects and study the structure of their evolution.
 	We also give a measure of the total exploration of the different spaces during simulations.
@@
 	The interests of models 2 and 5 increase abruptly once the arm succeeded in grabbing the corresponding stick.
-	Following that, the interests of models 3 and 6 also increase abruptly when the object has been touched by the corresponding stick.
-	An exemple of exploration of the $2$D space with the object is also provided in Fig. \ref{res_interests}(b) corresponding to the same condition.
+	Following that, the interests of models 3 and 6 increase abruptly once the object has been touched by the corresponding stick.
+	An exemple of exploration of the $2$D space of the object is also provided in Fig. \ref{res_interests}(b) for the same condition.
 
-	\begin{figure*}[ht]
+	\begin{figure}[ht]
 		\centering
-		\subfloat[]{\includegraphics[width=7cm]{./include/H-RGB-P-AMB-log9-interests-100000.pdf}}
-		\subfloat[]{\includegraphics[width=7cm]{./include/H-RGB-P-AMB-log9-obj-explo.pdf}}
-		\caption{Condition H-P-AMB. (a) Interests of each model. (b) Exploration of the object space: each dot is one point reached with the object at the end of one movement.}
+		\subfloat{\includegraphics[width=4.5cm]{./include/H-RGB-P-AMB-log9-interests-100000.pdf}}
+		\hspace{-0.7cm}
+		\subfloat{\includegraphics[width=4.5cm]{./include/H-RGB-P-AMB-log9-obj-explo.pdf}}
+		\caption{Condition H-P-AMB. Left: Interests of each model. Right: Exploration of the object space: each dot is one point reached with the object at the end of a movement.}
 		\label{res_interests}
-	\end{figure*}
+	\end{figure}
 
-	\subsection{Structure of the evolution of behaviours}
+	\subsubsection{Structure of the evolution of behaviours}
 
@@
 			\begin{center} 
-			\caption{behavioural analysis} 
+			\caption{Behavioural analysis} 
 			\label{table} 
@@
 
-		\begin{figure}[ht]
+		\begin{figure*}[ht]
 			\centering
-			\includegraphics[width=4.4cm]{./include/H-RGB-GR-AMB-log15-events-100000.pdf}
+			\includegraphics[width=5.5cm]{./include/F-RGB-log53-events-100000.pdf}
 			\hspace{-0.4cm}
-			\includegraphics[width=4.4cm]{./include/H-RGB-P-AMB-log8-events-100000.pdf}
-			\caption{behavioural measure. Left: H-GR-AMB, Right: H-P-AMB.}
+			\includegraphics[width=5.5cm]{./include/H-RGB-GR-AMB-log15-events-100000.pdf}
+			\hspace{-0.4cm}
+			\includegraphics[width=5.5cm]{./include/H-RGB-P-AMB-log8-events-100000.pdf}
+			\caption{Behavioural phases typical exemples.
+Left: F-RGB.
+Middle: H-GR-AMB, Right: H-P-AMB.
+Only hierarchical active condition H-P-AMB shows overlapping phases of behaviour similar to infant development.}
 			\label{res_ow}
-		\end{figure}
+		\end{figure*}
 
@@
 
-	\subsection{Exploration efficiency}
+	\subsubsection{Exploration efficiency}
 
@@
 			\vspace{-0.4cm}
-			\subfloat[$Hand$]{\includegraphics[width=3.5cm]{./include/xp1-explo-hand.pdf}}
-			\subfloat[$Stick_1$]{\includegraphics[width=3.5cm]{./include/xp1-explo-stick_1.pdf}}
-			\subfloat[$Stick_2$]{\includegraphics[width=3.5cm]{./include/xp1-explo-stick_2.pdf}}
-			\subfloat[$Object$]{\includegraphics[width=3.5cm]{./include/xp1-explo-obj.pdf}}
-			\subfloat[$Boxes$]{\includegraphics[width=3.3cm]{./include/xp1-explo-box.pdf}}
+			\subfloat[$Hand$]{\includegraphics[height=5.5cm]{./include/xp1-explo-hand.pdf}}
+			\subfloat[$Stick_1$]{\includegraphics[height=5.5cm]{./include/xp1-explo-stick_1.pdf}}
+			\subfloat[$Stick_2$]{\includegraphics[height=5.5cm]{./include/xp1-explo-stick_2.pdf}}
+			\subfloat[$Object$]{\includegraphics[height=5.5cm]{./include/xp1-explo-obj.pdf}}
+			\subfloat[$Boxes$]{\includegraphics[height=5.5cm]{./include/xp1-explo-box.pdf}}
 			\caption{Exploration of sensory spaces. Box plots show for each condition and space the median and quartiles of the $100$ trials.}
@@
 
-	\subsection{Structure of tool choice}
+	\subsubsection{Structure of tool choice}
 
@@
 			\includegraphics[width=4.5cm]{./include/H-RGB-P-AMB-PGITC-log3-choice_mod4.png}
-			\caption{Chosen tool depending on object goal position. Blue points: long stick choice. Red points: small stick choice. Left: H-P-AMB, Right: H-P-AMB-ATC.}
+			\caption{Chosen tool depending on object goal position. Blue points: long stick choice. Red points: small stick choice. Left: condition H-P-AMB, strong boundaries 
+			between tool choice regions. Right: condition H-P-AMB-ATC, parallel exploration of both tools for the same goals.}
 			\label{res_choice}
@@
 
-	\subsection{Structure of the evolution of behaviours}
+	\subsubsection{Structure of the evolution of behaviours}
 
@@
 
-	\subsection{Variability of strategies to reach goals}
+	\subsubsection{Variability of strategies to reach goals}
 

### 2016-01-31 cogsci2016/paper.tex
figures

@@
 		\centering
-		\subfloat{\includegraphics[width=4.5cm]{./include/H-RGB-P-AMB-log9-interests-100000.pdf}}
 		\hspace{-0.7cm}	
-		\subfloat{\includegraphics[width=4.5cm]{./include/H-RGB-P-AMB-log9-obj-explo.pdf}}
+		\vspace{0pt}
+		\includegraphics[width=4.4cm]{./include/H-RGB-P-AMB-log9-interests-100000.png}
+		\hspace{-0.1cm}	
+		%\vspace{-0.2cm}
+		\vspace{0pt}
+		\includegraphics[width=4.26cm]{./include/obj-explo.pdf}
 		\caption{Condition H-P-AMB. Left: Interests of each model. Right: Exploration of the object space: each dot is one point reached with the object at the end of a movement.}
@@
 			\hspace{-0.4cm}
-			\includegraphics[width=5.5cm]{./include/H-RGB-GR-AMB-log15-events-100000.pdf}
+			\includegraphics[width=5.5cm]{./include/H-RGB-GR-AMB-log13-events-100000.pdf}
 			\hspace{-0.4cm}
-			\includegraphics[width=5.5cm]{./include/H-RGB-P-AMB-log8-events-100000.pdf}
+			\includegraphics[width=5.5cm]{./include/H-RGB-P-AMB-log38-events-100000.pdf}
 			\caption{Behavioural phases typical exemples.
@@
 			\centering
-			\includegraphics[width=4.5cm]{./include/H-RGB-P-AMB-log9-choice_mod4.png}
-			\hspace{-0.6cm}
-			\includegraphics[width=4.5cm]{./include/H-RGB-P-AMB-PGITC-log3-choice_mod4.png}
+			\includegraphics[width=4.3cm]{./include/choice-H-RGB-P-AMB.pdf}
+			\hspace{-0.2cm}
+			\includegraphics[width=4.3cm]{./include/choice-H-RGB-P-AMB-PGITC.pdf}
 			\caption{Chosen tool depending on object goal position. Blue points: long stick choice. Red points: small stick choice. Left: condition H-P-AMB, strong boundaries 

### 2016-01-31 cogsci2016/paper.tex
discussion

@@
 		Results show different structures of behaviour evolution in the different conditions.		
-		H-GR-AMB shows successive behavioural steps with abrupt changes.
-		Random model babbling and active model babbling both show overlapping waves structure in the evolution of the three behaviours, 
-		but random model babbling explores slightly less the object position.
-		In this setup, the difference is more on the cognitive or intentional level, as active model babbling monitors the progress on each model whereas random model babbling do not, than on a quantitative level,
-		because here all models are still useful to explore.
-		However, in others setups where some tasks are learned much faster than others and where at some point it become useless to explore a mastered task, then active model babbling would
-		make a key difference on a quantitative exploration point of view, and on the structure of the evolution of the measured behaviours.
+		Flat architectures do not use the structure of the environment and do not separate the high-dimensional sensorimotor space into learnable subspaces.
+		Therefore, they do not show structure in the behavioural evolution but rather steady proportions of the three behaviours.
+		By contrast, hierarchical condition H-GR-AMB shows successive behavioural steps with abrupt changes, which reflects the greedy choice of model to babble.
+		When one model becomes more interesting than another, it is chosen
+		for a large number of iterations until another model exceeds its interest.
+		However, random model babbling shows overlapping phases structures in the evolution of the three behaviours more compatible with infants' studies ($60\%$), 
+		but less than active model babbling ($70\%$ and $79\%$).
+		This is because random model babbling does not adapt its choice of models to their interests along development.
+		Indeed, it often explores model $1$ even if it is sufficiently explored to make progress on higher-level models, 
+		and so explores less the object position space than active model babbling (H-P-AMB).
+		Also, in this setup, all models are still useful to explore after the number of iterations simulated 
+		here so the first behavioural phases ($hand$ and $stick$) do not lessen towards the end of the simulations in active conditions. 
+		Consequently, the difference between active and random model babbling is more on the cognitive or intentional level, 
+		as active model babbling monitors the current progress of each model whereas random model babbling do not, than on a quantitative level.
+		However, in others setups where some tasks are learned much faster than others and where at some point it become useless to explore a mastered task, active model babbling would
+		make a key difference on a quantitative exploration point of view and on the structure of the evolution of the measured behaviours.
 
@@
 
-		Different structure of tool choice: overlapping waves of strategies to fulfill given goals in condition H-P-AMB-ATC.
+		The comparison of conditions H-P-AMB and H-P-AMB-ATC shows that when the agent chooses the tool to reach a given object goal position based on the interest of the corresponding models,
+		both tools are trained to reach all goals instead of training only the best performing tool.
+		Indeed, we can see that with the active choice of tool, the small stick has produced more diverse effects on the object than in the best choice of tool's condition, even if those effects could also have been
+		generated with the long tool.
+		The active tool choice is in accordance with Siegler's overlapping waves theory that documents the parallell use of non-optimal strategies in infants in different contexts
+		and explains that a non-optimal strategy gains to be refined as it might turn to be finally a good one for this or for different but related problems.
 
 	%
+
+	Finally, in our model, H is determinant and A reinforces the emergence of structures.
+	Link with children ?
+	First model to
 

### 2016-02-01 cogsci2016/paper.tex
figures
comments Arthur

@@
 	In existing models, the agent learns only one mapping that relates a motor space to a single task space. 
-	However, in the perspective of an open-ended development of reusable skills, and specifically in the development of tool use, multiple interdependent and hierarchically organized task spaces should be available to the agent
-	as for instance using a tool to act upon an object could make use of previously explored parameterized interaction with the tool.
+	However, in the perspective of an open-ended development of reusable skills, and specifically in the development of tool use, multiple interdependent and hierarchically organized task spaces should be available to the agent.
+	For instance, using a tool to act upon an object could make use of previously explored parameterized interaction with the tool.
 
@@
 		We simulate a 2D robotic arm that can grasp tools that can be used to move an object into different boxes in the environment. 		
-		In each trial, the agent executes a motor trajectory, we evaluate its consequences on the sensory dimensions and we give him
-		this sensory feedback. Finally the arm, tools and objects are resetted to their intial state.
+		In each trial, the agent executes a motor trajectory and gets the associated sensory feedback. 
+		Finally the arm, tools and objects are resetted to their intial state.
 		The next sections precisely describe the items of the environment and their interactions.	
@@
 
-		\subsubsection{Robotic arm}
+		\subsubsection{Robotic Arm}
 
@@
 
-		\subsubsection{Motor control}
+		\subsubsection{Motor Control}
 
@@
 
-		\subsubsection{Objects and tools}
+		\subsubsection{Objects and Tools}
 
-			Two sticks can be grasped by the handle side in order to catch an out-of-reached object.
+			Two sticks can be grasped by the handle side in order to catch an out-of-reach object.
 			A small stick of length $0.3$ is located at position $(0.75, 0.25)$ with initial angle $\frac{\pi}{4}$ from the horizontal line.
@@
 			The initial position of the sphere is $(0, 1.2)$ and is thus unreachable directly with the gripper.		
-			If the gripper is closed near the handle of one stick (closer than $0.2$), it is considered grasped and will follow the gripper's position and the angle of the arm's last segment until the gripper opens.
-			Similarly, if the other end of a stick reaches the sphere (within $0.1$), the sphere will follow the end of the stick.
+			If the gripper is closed near the handle of one stick (closer than $0.2$), it is considered grasped and follows the gripper's position and the angle of the arm's last segment until the gripper opens.
+			Similarly, if the magnetic side of a stick reaches the sphere (within $0.1$), the sphere will then follow the magnet.
 			The ten boxes (identified from $1$ to $10$) are static and have size $0.2$.
@@
 
-		\subsubsection{Sensory feedback}
+		\subsubsection{Sensory Feedback}
 
@@
 
-	\subsection{Learning architectures}
+	\subsection{Learning Architectures}
 
@@
 
-		\subsubsection{Flat architectures}
+		\subsubsection{Flat Architectures}
 
@@
 			The control condition is a random motor babbling condition (F-RmB) that randomly chooses new motor parameters $m$ to try at each iteration.
-			In the other conditions, the agent performs Goal Babbling, a method by which it self-generates a goal in the sensory space at each iteration and trying to reach it.
+			In the other conditions, the agent performs Goal Babbling, a method by which it self-generates a goal in the sensory space at each iteration and tries to reach it.
 			To generate those goals, different strategies have been studied \cite{baranes_active_2013}. 
@@
 
-		\subsubsection{Hierarchical architectures}
+		\subsubsection{Hierarchical Architectures}
 
@@
 motor space of model $2$ is $S_{Hand}$), a sensory space (respectively $S_{Stick_1}$, see arrows in Fig.
-\ref{Architectures}, and can choose goals randomly in this sensory space.
+\ref{Architectures}), and can choose goals randomly in this sensory space.
 			At each iteration, the architecture first have to choose the model in which to choose a goal, a procedure that we call Model Babbling.
@@
 			\end{equation}
-			the absolute difference between $C(s_g)$ and the mean competence of the ($k=20$) nearest previous goals.
+			the absolute difference between $C(s_g)$ and the mean competence of the ($k=20$) nearest previous goals (k-Nearest Neighbours algorithm).
 			The interest of a model is initialized at $0$ and updated to follow the interest of the goals (with rate $n=200$):
@@
 
-	\subsubsection{Structure of the evolution of behaviours}
+	\subsubsection{Structure of the Evolution of Behaviours}
 
@@
 			\includegraphics[width=5.5cm]{./include/F-RGB-log53-events-100000.pdf}
-			\hspace{-0.4cm}
 			\includegraphics[width=5.5cm]{./include/H-RGB-GR-AMB-log13-events-100000.pdf}
-			\hspace{-0.4cm}
 			\includegraphics[width=5.5cm]{./include/H-RGB-P-AMB-log38-events-100000.pdf}
@@
 
-	\subsubsection{Exploration efficiency}
+	\subsubsection{Exploration Efficiency}
 
@@
 		The exploration of the hand, sticks and object spaces is defined as the number of reached cells 
-		in a $100\times100$ discretization of the (X,Y) space of the position at timestep $50$ (end of movement).
+		in a $100\times100$ discretization of the (X,Y) space of their position at the end of the movement.
 		The exploration of the boxes is the number of boxes that have been filled with the object during training.
 		Fig. \ref{res_explo} shows the total exploration of the different sensory spaces for each condition.
-		We provide statistical Mann-Whitney U test results of comparisons of the exploration in different pairs of conditions.
-		Firstly, the Motor Babbling condition (F-RmB) have more explored $S_{Hand}$ and less $S_{Object}$ and $S_{Boxes}$ compared to the other conditions ($p<0.0001$).
-		Then, F-RGB explores all spaces less than H-RMB condition ($p<0.01$).
-		H-RMB explores more $S_{Hand}$ ($p<0.001$) and less $S_{Object}$ ($p<0.05$) than H-P-AMB.
-		Also, H-GR-AMB shows lower exploration all spaces than H-P-AMB ($p<0.01$).
-		Condition H-P-AMB-ATC explores more $S_{Stick_2}$ ($p<0.05$) than condition H-P-AMB, and difference is not significant in other spaces.
+		We provide statistical Mann-Whitney U test results of comparisons of the exploration for some pairs of conditions.
+		One star means $p<0.05$, two: $p<0.01$, three: $p<0.001$ and four: $p<0.0001$.
+		%Firstly, the Motor Babbling condition (F-RmB) have more explored $S_{Hand}$ and less $S_{Object}$ and $S_{Boxes}$ compared to the other conditions ($p<0.0001$).
+		%Then, F-RGB explores all spaces less than H-RMB condition ($p<0.01$).
+		%H-RMB explores more $S_{Hand}$ ($p<0.001$) and less $S_{Object}$ ($p<0.05$) than H-P-AMB.
+		%Also, H-GR-AMB shows lower exploration of all spaces than H-P-AMB ($p<0.01$).
+		%Condition H-P-AMB-ATC explores more $S_{Stick_2}$ ($p<0.05$) than condition H-P-AMB, and difference is not significant in other spaces.
 
@@
 
-	\subsubsection{Structure of tool choice}
+	\subsubsection{Structure of Tool Choice}
 
 		Fig. \ref{res_choice} shows a comparison of the choice of tool to reach a given object goal position in the conditions H-P-AMB and H-P-AMB-ATC.
-		In those conditions, model $4$ learns a mapping between $S_{Object}$ and $S_{Boxes}$. 
-		When this model is babbling, it chooses a random goal $s_b \in S_{Boxes}$ and infers the best object position $s_o$ to reach $s_b$.
+		When model $4$ is babbling, it infers the best object position $s_o$ to reach a random goal $s_b \in S_{Boxes}$.
 		To reach $s_o$, one of the tools ($Stick_1$ with model $3$ or $Stick_2$ with model $6$) is chosen. 
-		We plot all those choices model $4$ made during exploration, at position $s_o$ on a $2$D space, with color blue if $Stick_1$ was chosen and red if $Stick_2$ was chosen, in one figure for each of the two conditions.
-		We can see two very different choice structures.
-		However, goal that can be reached with both tools are more often chosen to be explored with the long stick in the interest-based choice of condition H-P-AMB-ATC than in competence-based choice of condition H-P-AMB.
+		We plot all the choices that model $4$ made during exploration, at position $s_o$ on a $2$D space, with color blue if $Stick_1$ was chosen and red if $Stick_2$ was chosen, 
+		in one figure for each of the two conditions.
+		In condition H-P-AMB, we can see strong boundaries between tool choice regions.
+		By contrast, in condition H-P-AMB-ATC, both tools are chosen in all regions.
 
@@
 			\caption{Chosen tool depending on object goal position. Blue points: long stick choice. Red points: small stick choice. Left: condition H-P-AMB, strong boundaries 
-			between tool choice regions. Right: condition H-P-AMB-ATC, parallel exploration of both tools for the same goals.}
+			between tool choice regions. Right: condition H-P-AMB-ATC, parallel exploration of both tools in all regions.}
 			\label{res_choice}
@@
 		However, in others setups where some tasks are learned much faster than others and where at some point it become useless to explore a mastered task, active model babbling would
-		make a key difference on a quantitative exploration point of view and on the structure of the evolution of the measured behaviours.
+		make a key difference on a quantitative exploration point of view and on the structure of the evolution of the measured behaviours.\\
 
@@
 
-	\subsubsection{Variability of strategies to reach goals}
+	\subsubsection{Variability of Strategies to Reach Goals}
 
@@
 
-	Finally, in our model, H is determinant and A reinforces the emergence of structures.
+	Finally, in our model, the hierarchical structure is a determining factor for the emergence of structured behavioural phases, and the active learning reinforces this emergence.
 	Link with children ?
-	First model to
+	First model to ?
 

### 2016-02-01 cogsci2016/paper.tex
typos

@@
 	The latter shows an understanding of shapes, forces and other physical properties that can be recruited for mental transformations and planning operations which are pillars of human cognition.
-	Children's development has first been described as staircase-like successive stages in which all children go through \cite{piaget1952origins}.
+	Child development has first been described as staircase-like successive stages in which all children go through \cite{piaget1952origins}.
 	More recently, different views were developed describing variability among children's developmental paths. 
@@
 	Active learning is a paradigm where the learning agent chooses which actions to perform in its environment.
-	To make this choice the agent can optimize some extrinsic rewards given by the environment, as in standard Reinfocement Learning tasks.
+	To make this choice the agent can optimize some extrinsic rewards given by the environment, as in standard Reinforcement Learning tasks.
 	These extrinsic rewards are not suited for an open-ended autonomous exploration of the environment that could reflect children learning by free play.
@@
 	We define the HACOB (Hierarchical Active Curiosity-driven mOdel Babbling) architecture and compare several possible strategies 
-	to study the role of active learning and hierarchical representation in the structuration of developmental trajectories.
+	to study the role of active learning and hierarchical representation in the structuring of developmental trajectories.
 	We compare the different learning conditions in a $2$D environment where a simulated arm with three joints plus a gripper can grab one of two available tools to move an out-of-reach object.
@@
 	Also, social guidance with imitation and mimicry is of central importance for the development of tool use in infants but we do not address the question
-	of its modeling in this paper nor the interplay and tradeoff between social learning and self-exploration.
+	of its modeling in this paper nor the interplay and trade-off between social learning and self-exploration.
 	Another important feature of young infants' learning of tool use is the need to adapt to a developing body and to the maturation of vision during ontogenetic development, 
@@
 		In each trial, the agent executes a motor trajectory and gets the associated sensory feedback. 
-		Finally the arm, tools and objects are resetted to their intial state.
+		Finally the arm, tools and objects are resetted to their initial state.
 		The next sections precisely describe the items of the environment and their interactions.	
-		See Fig.\ref{env} for an exemple state of the environment.
+		See Fig.\ref{env} for an example state of the environment.
 
@@
 			It gets the trajectory of the gripper ($S_{Hand}$, $9$D), the trajectory of the end of the sticks ($S_{Stick_1}, $6$D$ and $S_{Stick_2}, $6$D$), 
-			the position of the object at the end of the mouvement ($S_{Object}, $2$D$), and whether the object is in a box at the end of the mouvement and the distance between the object and the nearest box ($S_{Boxes}, $2$D$).
+			the position of the object at the end of the movement ($S_{Object}, $2$D$), and whether the object is in a box at the end of the movement and the distance between the object and the nearest box ($S_{Boxes}, $2$D$).
 			The trajectory of the gripper is represented as the $x$ and $y$ positions and the aperture ($1$ or $-1$) of the gripper at $3$ time points: 
@@
 	Following that, the interests of models 3 and 6 increase abruptly once the object has been touched by the corresponding stick.
-	An exemple of exploration of the $2$D space of the object is also provided in Fig. \ref{res_interests}(b) for the same condition.
+	An example of exploration of the $2$D space of the object is also provided in Fig. \ref{res_interests}(b) for the same condition.
 
@@
 		We categorize the behaviours into three types.
-		In the first category ($hand$) are mouvements of the arm that did not grab any stick and thus did not move the out-of-reached object.
-		The second category ($stick$) are mouvements that did grab one of the two sticks but did not touch the object with it.
-		The third category ($object$) contains the mouvements where both a stick was grabbed and the object was moved by the stick.
+		In the first category ($hand$) are movements of the arm that did not grab any stick and thus did not move the out-of-reached object.
+		The second category ($stick$) are movements that did grab one of the two sticks but did not touch the object with it.
+		The third category ($object$) contains the movements where both a stick was grabbed and the object was moved by the stick.
 		Fig. \ref{res_ow} shows the prototypical evolution of the proportion of the three categories of behaviour along the $100000$ iterations for conditions H-GR-AMB and H-P-AMB.
@@
 		A structure was considered similar if it validated each of the following criteria:
-		behaviours of categories $stick$ and $object$ increase quikly from $0$ to more than $10\%$ (potentially after an initial phase with a steady low value), 
+		behaviours of categories $stick$ and $object$ increase quickly from $0$ to more than $10\%$ (potentially after an initial phase with a steady low value), 
 		and are followed by a plateau (steady curve with small slope) with no abrupt changes, and behaviours of category $object$ start to raise at least $1000$ iterations after $stick$ started to raise.
@@
 			\includegraphics[width=5.5cm]{./include/H-RGB-P-AMB-log38-events-100000.pdf}
-			\caption{Behavioural phases typical exemples.
+			\caption{Behavioural phases typical examples.
 Left: F-RGB.
@@
 		Results show different structures of behaviour evolution in the different conditions.		
-		Flat architectures do not use the structure of the environment and do not separate the high-dimensional sensorimotor space into learnable subspaces.
+		Flat architectures do not use the structure of the environment and do not separate the high-dimensional sensorimotor space into learnable sub-spaces.
 		Therefore, they do not show structure in the behavioural evolution but rather steady proportions of the three behaviours.
@@
 		generated with the long tool.
-		The active tool choice is in accordance with Siegler's overlapping waves theory that documents the parallell use of non-optimal strategies in infants in different contexts
+		The active tool choice is in accordance with Siegler's overlapping waves theory that documents the parallel use of non-optimal strategies in infants in different contexts
 		and explains that a non-optimal strategy gains to be refined as it might turn to be finally a good one for this or for different but related problems.

### 2016-02-01 cogsci2016/paper.tex
abstract

@@
 \begin{abstract}
-This is the abstract.\\
-This is the abstract.\\
-This is the abstract.\\
-This is the abstract.\\
-This is the abstract.\\
-This is the abstract.\\
-This is the abstract.\\
+Studies of child development of tool use precursors show successive but overlapping phases of qualitatively different types of behaviours.
+We hypothethize that two mechanisms in particular play a role in the structuring of these phases: the intrinsic motivation to explore and the representation used to encode sensorimotor experience.
+Previous models show how curiosity-driven learning mechanisms could allow the emergence of developmental trajectories.
+We build upon those models and present the HACOB (Hierarchical Active Curiosity-driven mOdel Babbling) architecture 
+that actively chooses which sensorimotor model to train in a hierarchy a models representing the environmental structure.
+We define a robotic arm in a $2$D environment with objects and we show that overlapping phases of behaviour are autonomously emerging in active model babbling conditions.
+To our knowledge, this is the first model of the curiosity-driven development of tool use and the first to actively explore non-optimal methods to reach a goal, in accordance with Siegler's overlapping waves theory.
 

### 2016-02-01 cogsci2016/paper.tex
intro

@@
 	Active learning is a paradigm where the learning agent chooses which actions to perform in its environment.
-	To make this choice the agent can optimize some extrinsic rewards given by the environment, as in standard Reinforcement Learning tasks.
+	To make this choice the agent can optimize extrinsic rewards given by the environment, as in standard Reinforcement Learning tasks.
 	These extrinsic rewards are not suited for an open-ended autonomous exploration of the environment that could reflect children learning by free play.
@@
 	In the Playground Experiment \cite{oudeyer_what_2007}, a quadruped robot learned how to use its motor primitives to interact with the items of an infant play mat and a robot peer.
-	Also, in a study of the self-organization of vocalizations \cite{moulin-frier_self-organization_2014}, an agent had to learn how to
+	Also, in a study of the learning of vocalizations \cite{moulin-frier_self-organization_2014}, an agent had to learn how to
 	use a vocal synthesizer by self-exploration or with the help of humans' demonstrations of phonetic items. 
 	This model reproduces accurately major phases of infant vocal development until $6$ months.
-	In both studies, developmental trajectories of increasing complexity are emerging from learning, with both regularities in developmental steps and diversity.
+	In both studies, developmental trajectories are emerging from learning, with both regularities in developmental steps and diversity.
 	The diversity comes from different mechanisms: stochasticity in the algorithms, variability in the environment, and the multiples attractors of the dynamic learning system.
@@
 	We compare the different learning conditions in a $2$D environment where a simulated arm with three joints plus a gripper can grab one of two available tools to move an out-of-reach object.
-	We measure the different phases of behaviour during exploration and compare the different structures of behavioural evolution.
+	We measure the different phases of behaviour during exploration and compare their structures.
 

### 2016-02-01 cogsci2016/paper.tex
figures
Update paper.tex
updates of the introduction

@@
 \usetikzlibrary{arrows,shapes,backgrounds,petri,fit}
+
+\setcounter{topnumber}{4}
+\setcounter{bottomnumber}{3}
+\setcounter{totalnumber}{5}
+\renewcommand{\topfraction}{0.95}
+\renewcommand{\bottomfraction}{0.85}
+\renewcommand{\textfraction}{0.2}
+\renewcommand{\floatpagefraction}{0.7}
+
+%\usepackage{fixltx2e}
 
@@
 	2) the structure of the representation used to encode sensorimotor experience.
-	Active learning is a paradigm where the learning agent chooses which actions to perform in its environment.
-	To make this choice the agent can optimize extrinsic rewards given by the environment, as in standard Reinforcement Learning tasks.
-	These extrinsic rewards are not suited for an open-ended autonomous exploration of the environment that could reflect children learning by free play.
-	Based on infant's developmental psychology, different types of intrinsic motivations have been studied \cite{santucci2013}.
-	One way to define an intrinsic motivation is to autonomously search for situations where the learning progress is high, so as to avoid unreachable or unlearnable situations.
-	Computational models have shown that developmental trajectories could emerge from the curiosity-driven learning of sensorimotor mappings, in very different settings.
-	In the Playground Experiment \cite{oudeyer_what_2007}, a quadruped robot learned how to use its motor primitives to interact with the items of an infant play mat and a robot peer.
-	Also, in a study of the learning of vocalizations \cite{moulin-frier_self-organization_2014}, an agent had to learn how to
-	use a vocal synthesizer by self-exploration or with the help of humans' demonstrations of phonetic items. 
+
+	Intrinsic motivation, sometimes called "curiosity", have been identified to play a fundamental role in driving spontaneous exploration in infant free play (REF Kidd and Hayden, 2015).
+They have been defined as mechanisms that push infants to explore activities for their own sake, driven by the search of novelty, surprise, dissonances or optimal challenge (Gottlieb et al., 2013).
+In the last decade, various families of computational models of intrinsic motivation were developped, often based on the formal frameworks of active learning and reinforcement learning (Baldassarre and Mirolli, 2013).
+One family of models, that has targeted to study the developmental dimensions of intrinsic motivation, has considered a curiosity-driven learning mechanism where
+the learner actively engages in sensorimotor activities that provide high learning progress, avoiding situations that are too easy or too difficult and progressively focusing on activities of increasing complexity (Gottlieb et al., 2013).
+
+	Such computational models have shown that developmental trajectories could emerge from the curiosity-driven learning of sensorimotor mappings, in very different settings.
+	In the Playground Experiment (REF Gottlieb et al., 2013), a quadruped robot motivated to maximize its learning progress acquired how to use its motor primitives to interact with the items of an infant play mat and a robot peer, following a self-organized learning curriculum.
+	In a model of active vocal development \cite{moulin-frier_self-organization_2014}, an agent had to learn how to
+	produce sounds with its vocal tract by self-exploration combined with imitation of adult speech sounds. 
 	This model reproduces accurately major phases of infant vocal development until $6$ months.
 	In both studies, developmental trajectories are emerging from learning, with both regularities in developmental steps and diversity.
-	The diversity comes from different mechanisms: stochasticity in the algorithms, variability in the environment, and the multiples attractors of the dynamic learning system.
-	In existing models, the agent learns only one mapping that relates a motor space to a single task space. 
+Regularities result from the attractor dynamics of the interaction between motivated learning, the body and the environment.
+	The diversity comes from different mechanisms: stochasticity in the algorithms, variability in the environment, and the multiple attractors of the dynamic learning system.
+	Existing models have considered the exploration and learning of sensorimotor correspondances mapping a motor space to a single task/sensori space. 
 	However, in the perspective of an open-ended development of reusable skills, and specifically in the development of tool use, multiple interdependent and hierarchically organized task spaces should be available to the agent.
@@
 
+	\begin{figure}[t]
+		\centering
+		\hspace{-0.7cm}	
+		\vspace{0pt}
+		\includegraphics[width=4.4cm]{./include/H-RGB-P-AMB-log9-interests-100000.png}
+		\hspace{-0.1cm}	
+		%\vspace{-0.2cm}
+		\vspace{0pt}
+		\includegraphics[width=4.26cm]{./include/obj-explo.pdf}
+		\caption{Condition H-P-AMB. Left: Interests of each model. Right: Exploration of the object space: each dot is one point reached with the object at the end of a movement.}
+		\label{res_interests}
+	\end{figure}
+
+	\begin{figure*}[t]
+		\centering
+		\includegraphics[width=5.5cm]{./include/F-RGB-log53-events-100000.pdf}
+		\includegraphics[width=5.5cm]{./include/H-RGB-GR-AMB-log13-events-100000.pdf}
+		\includegraphics[width=5.5cm]{./include/H-RGB-P-AMB-log38-events-100000.pdf}
+		\caption{Behavioural phases typical examples.
+Left: F-RGB.
+Middle: H-GR-AMB, Right: H-P-AMB.
+Only hierarchical active condition H-P-AMB shows overlapping phases of behaviour similar to infant development.}
+		\label{res_ow}
+	\end{figure*}
+
+	\begin{figure*}[t]
+		\centering
+		\includegraphics[width=14cm]{./include/xp1-explo-legend.pdf}\\
+		\vspace{-0.4cm}
+		\subfloat[$Hand$]{\includegraphics[height=5.5cm]{./include/xp1-explo-hand.pdf}}
+		\subfloat[$Stick_1$]{\includegraphics[height=5.5cm]{./include/xp1-explo-stick_1.pdf}}
+		\subfloat[$Stick_2$]{\includegraphics[height=5.5cm]{./include/xp1-explo-stick_2.pdf}}
+		\subfloat[$Object$]{\includegraphics[height=5.5cm]{./include/xp1-explo-obj.pdf}}
+		\subfloat[$Boxes$]{\includegraphics[height=5.5cm]{./include/xp1-explo-box.pdf}}
+		\caption{Exploration of sensory spaces. Box plots show for each condition and space the median and quartiles of the $100$ trials.}
+		\label{res_explo}
+	\end{figure*}
+
 	We perform $100$ simulations per condition. 
@@
 	An example of exploration of the $2$D space of the object is also provided in Fig. \ref{res_interests}(b) for the same condition.
-
-	\begin{figure}[ht]
-		\centering
-		\hspace{-0.7cm}	
-		\vspace{0pt}
-		\includegraphics[width=4.4cm]{./include/H-RGB-P-AMB-log9-interests-100000.png}
-		\hspace{-0.1cm}	
-		%\vspace{-0.2cm}
-		\vspace{0pt}
-		\includegraphics[width=4.26cm]{./include/obj-explo.pdf}
-		\caption{Condition H-P-AMB. Left: Interests of each model. Right: Exploration of the object space: each dot is one point reached with the object at the end of a movement.}
-		\label{res_interests}
-	\end{figure}
 
@@
 
-		\begin{table}[!ht]
+		\begin{table}[h]
 			\small
@@
 
-		\begin{figure*}[ht]
-			\centering
-			\includegraphics[width=5.5cm]{./include/F-RGB-log53-events-100000.pdf}
-			\includegraphics[width=5.5cm]{./include/H-RGB-GR-AMB-log13-events-100000.pdf}
-			\includegraphics[width=5.5cm]{./include/H-RGB-P-AMB-log38-events-100000.pdf}
-			\caption{Behavioural phases typical examples.
-Left: F-RGB.
-Middle: H-GR-AMB, Right: H-P-AMB.
-Only hierarchical active condition H-P-AMB shows overlapping phases of behaviour similar to infant development.}
-			\label{res_ow}
-		\end{figure*}
-
 	%
@@
 
-		\begin{figure*}[ht]
-			\centering
-			\includegraphics[width=14cm]{./include/xp1-explo-legend.pdf}\\
-			\vspace{-0.4cm}
-			\subfloat[$Hand$]{\includegraphics[height=5.5cm]{./include/xp1-explo-hand.pdf}}
-			\subfloat[$Stick_1$]{\includegraphics[height=5.5cm]{./include/xp1-explo-stick_1.pdf}}
-			\subfloat[$Stick_2$]{\includegraphics[height=5.5cm]{./include/xp1-explo-stick_2.pdf}}
-			\subfloat[$Object$]{\includegraphics[height=5.5cm]{./include/xp1-explo-obj.pdf}}
-			\subfloat[$Boxes$]{\includegraphics[height=5.5cm]{./include/xp1-explo-box.pdf}}
-			\caption{Exploration of sensory spaces. Box plots show for each condition and space the median and quartiles of the $100$ trials.}
-			\label{res_explo}
-		\end{figure*}
-
 	%
@@
 
-		\begin{figure}[ht]
+		\begin{figure}[!]
 			\centering
